---
title: "MINA_TB README"
format: gfm
---

This code base `MINA_TB` aims to estimate the required size of Tuberculosis vaccine trials under different assumptions. Note: this README file renders to README.md.

## Conventions

### Folders

Code and data are stored in the respective `code/` / `data/` folders. Model outputs are saved in `outputs/`, usually as .csv files, and figures in `figures/`. See `notes/` folder for details on how the model code has developed over time.

### Code

`code/trialsim_rote.R` was Stephen's main code for running the analysis. This has been copied to `run_analysis.qmd` in the parent folder for ease of editing (02/19/2026), with new clearer naming conventions. 

All helper functions are stored in `code/utils.R`. If a piece of code is re-used more than twice, it should ideally be written up as a function and added to `utils.R`. Naming conventions for functions are as follows:

`sim_` = run the code

`plot_` = make a plot

`_analytic` = analytical approach, using probability expressions derived in `documentation/MINA-TB.pdf` (formerly called 'theory')

`_stoch` = stochastic simulation-based approach, also described in `documentation/MINA-TB.pdf` (formerly called 'trials')

The probability expressions derived in `documentation/MINA-TB.pdf` are also saved as the following functions: `p_inf_and_type_and_asymp_given_age`, `p_asymp_given_age`, and `p_inf_and_type_given_asymp_and_age`.

Lastly, naming of parameter sets uses the following conventions:

`_lit` = parameter values are taken from the literature

`_m72IIb` = parameter values are backcalculated from the M72 phase 2b trial (Van Der Meeren et al., 2018) (formerly called 'nejm')

## Example workflow

The file `code/trialsim_rote.R` has been preserved as an example workflow. Key steps are as follows:

1. import functions
```{r}
#| label: eg_workflow_1
library(tidyverse)
library(readxl)
source('code/utils.R')
```

2. define parameter values
```{r}
#| label: eg_workflow_2
pars_m72IIb_igra <- list(
	minage=18,
	maxage=49,
	rho=rep(0.0275,80),
	p_slow=0.5,
	mu_slow=0.0001,
	mu_fast=1.5,
	sigma=100,
	ve=0.55,
	trial_length=3)
pars_m72IIb_tasa <- pars_m72IIb_igra
pars_m72IIb_tasa$sigma <- 2

pars_lit_igra <- list(
	minage=18,
	maxage=49,
	rho=rep(0.0025,80),
	p_slow=0.95,
	mu_slow=0.0001,
	mu_fast=1.5,
	sigma=100,
	ve=0.55,
	trial_length=3)
pars_lit_tasa <- pars_lit_igra 
pars_lit_tasa$sigma <- 2
```

3. define an age distribution e.g. uniform
```{r}
#| label: eg_workflow_3
agedist <- rep(1, 80)
names(agedist) <- 1:80
agedist <- agedist/sum(agedist)
```

4. simulate trials under m72IIb conditions (analytical and stochastic approaches)
```{r}
#| label: eg_workflow_4
#' Simulate the stochastic approach with m72IIb params, over the duration of positivity sigma OR pre-load saved csv file
# stochastic_df_m72IIb <- sim_stoch_over_sigma(pars=pars_m72IIb_igra, sigmavec=1:80, reps=25)
stochastic_df_m72IIb <- read_csv("output/stochastic_df_m72IIb_uniform.csv")

#' Simulate the analytical approach with m72IIb params, over the duration of positivity sigma
analytical_df_m72IIb <- sim_analytic_over_sigma(pars=pars_m72IIb_igra, sigmavec=seq(from=.5, to=80, by=0.01), agedist=agedist)
analytical_df_m72IIb %>% filter(sigma %in% c(0.5, 1, 1.5, 2, 5))

#' Plot all results
fig_stochastic_analytic_m72IIb <- plot_stochastic_analytic(stochastic_df_m72IIb, analytical_df_m72IIb, 
                                           cols=c("n_tested","n_recruited","n_fast","n_overall")) + 
	labs(title="M72/AS01E trial emulation")
fig_stochastic_analytic_m72IIb
ggsave(fig_stochastic_analytic_m72IIb, file="figures/stochastic_analytic_m72IIb.pdf", width=5, height=5/1.6)

fig_stochastic_analytic_log_m72IIb <- fig_stochastic_analytic_m72IIb + scale_y_continuous(trans="log10")
fig_stochastic_analytic_log_m72IIb
ggsave(fig_stochastic_analytic_log_m72IIb, file="figures/stochastic_analytic_log_m72IIb.pdf", width=5, height=5/1.6)

fig_screenslope_m72IIb <- plot_screenslope(analytical_df_m72IIb)
fig_screenslope_m72IIb


fig_stochastic_analytic_m72IIb_r21 <- plot_stochastic_analytic(stochastic_df_m72IIb, analytical_df_m72IIb, cols=c("n_tested","n_recruited")) + 
	labs(title="M72/AS01E trial emulation")
fig_stochastic_analytic_m72IIb_r21
ggsave(fig_stochastic_analytic_m72IIb_r21, file="figures/stochastic_analytic_m72IIb_r21.pdf", width=5, height=5/1.6)

fig_stochastic_analytic_m72IIb_r21_log <- plot_stochastic_analytic(stochastic_df_m72IIb, analytical_df_m72IIb, 
                                                   cols=c("n_tested","n_recruited")) + 
	labs(title="M72/AS01E trial emulation") + 
	scale_y_continuous(trans="log10")
fig_stochastic_analytic_m72IIb_r21_log
ggsave(fig_stochastic_analytic_m72IIb_r21_log, file="figures/stochastic_analytic_m72IIb_r21_log.pdf", width=5, height=5/1.6)
```

5. simulate trials under literature conditions (analytical and stochastic approaches)
```{r}
#| label: eg_workflow_5
#' Simulate the stochastic approach with lit params, over the duration of positivity sigma OR pre-load saved csv file
# stochastic_df_lit <- sim_stoch_over_sigma(pars=pars_lit_igra, sigmavec=1:80, reps=25)
stochastic_df_lit <- read_csv("output/stochastic_df_lit_uniform.csv")

#' Simulate the analytical approach with lit params, over the duration of positivity sigma
analytical_df_lit <- sim_analytic_over_sigma(pars=pars_lit_igra, sigmavec=seq(from=.5, to=80, by=0.01), agedist=agedist)
analytical_df_lit %>% filter(sigma %in% c(0.5, 1, 1.5, 2, 5))

#' Plot all results
fig_stochastic_analytic_lit <- plot_stochastic_analytic(stochastic_df_lit, analytical_df_lit, cols=c("n_tested","n_recruited","n_fast","n_overall")) + 
	labs(title="Literature parameters")
fig_stochastic_analytic_lit
ggsave(fig_stochastic_analytic_lit, file="figures/stochastic_analytic_lit.pdf", width=5, height=5/1.6)

fig_stochastic_analytic_log_lit <- fig_stochastic_analytic_lit + scale_y_continuous(trans="log10")
fig_stochastic_analytic_log_lit
ggsave(fig_stochastic_analytic_log_lit, file="figures/stochastic_analytic_log_lit.pdf", width=5, height=5/1.6)

fig_screenslope_lit <- plot_screenslope(analytical_df_lit)
fig_screenslope_lit
```

Possible extensions to the above basic workflow are to include custom age distribution in `sim_stoch` and custom fast targets for `sim_stoch_over_sigma` and `sim_analytic_over_sigma`.