---
title: "run_analysis"
format: html
---

This Quarto Markdown file outlines a workflow for running all analysis steps. It is based on the example workflow in `code/trailsim_rote.R` and has been copied to a .qmd for ease of editing and commenting.

## 1. import functions and load packages
```{r}
#| label: setup
source('code/utils.R')
```

## 2. define parameter values
```{r}
#| label: define_params

pars_nejm_igra <- list(
	minage=18,
	maxage=49,
	rho=0.0275,
	p_slow=0.5,
	mu_slow=0.0001,
	mu_fast=1.5,
	sigma=100,
	ve=0.55,
	trial_length=3)
pars_nejm_tasa <- pars_nejm_igra
pars_nejm_tasa$sigma <- 2

pars_lit_igra <- list(
	minage=18,
	maxage=49,
	rho=0.0025,
	p_slow=0.95,
	mu_slow=0.0001,
	mu_fast=1.5,
	sigma=100,
	ve=0.55,
	trial_length=3)
pars_lit_tasa <- pars_lit_igra 
pars_lit_tasa$sigma <- 2
```

## 3. define an age distribution e.g. uniform
```{r}
#| label: define_age_dist

agedist <- rep(1, 80)
names(agedist) <- 1:80
agedist <- agedist/sum(agedist)
```

## 4. simulate trials under NEJM conditions (theoretical and stochastic approaches)
```{r}
#| label: simulate_with_NEJM

#' Simulate the trials approach with NEJM params, over the duration of positivity sigma OR pre-load saved csv file
# trial_df_nejm <- sim_trials_over_sigma(pars=pars_nejm_igra, sigmavec=1:80, reps=25)
trial_df_nejm <- read_csv("output/trial_df_nejm.csv")

#' Simulate the analytical approach with NEJM params, over the duration of positivity sigma
theoretical_df_nejm <- sim_theory_over_sigma(pars=pars_nejm_igra, sigmavec=seq(from=.5, to=80, by=0.01), agedist=agedist)
theoretical_df_nejm %>% filter(sigma %in% c(0.5, 1, 1.5, 2, 5))

#' Plot all results
fig_trial_theory_nejm <- plot_trial_theory(trial_df_nejm, theoretical_df_nejm, 
                                           cols=c("n_tested","n_recruited","n_fast","n_overall")) + 
	labs(title="M72/AS01E trial emulation")
fig_trial_theory_nejm
ggsave(fig_trial_theory_nejm, file="figures/trial_theory_nejm.pdf", width=5, height=5/1.6)

fig_trial_theory_log_nejm <- fig_trial_theory_nejm + scale_y_continuous(trans="log10")
fig_trial_theory_log_nejm
ggsave(fig_trial_theory_log_nejm, file="figures/trial_theory_log_nejm.pdf", width=5, height=5/1.6)

fig_screenslope_nejm <- plot_screenslope(theoretical_df_nejm)
fig_screenslope_nejm


fig_trial_theory_nejm_r21 <- plot_trial_theory(trial_df_nejm, theoretical_df_nejm, cols=c("n_tested","n_recruited")) + 
	labs(title="M72/AS01E trial emulation")
fig_trial_theory_nejm_r21
ggsave(fig_trial_theory_nejm_r21, file="figures/trial_theory_nejm_r21.pdf", width=5, height=5/1.6)

fig_trial_theory_nejm_r21_log <- plot_trial_theory(trial_df_nejm, theoretical_df_nejm, 
                                                   cols=c("n_tested","n_recruited")) + 
	labs(title="M72/AS01E trial emulation") + 
	scale_y_continuous(trans="log10")
fig_trial_theory_nejm_r21_log
ggsave(fig_trial_theory_nejm_r21_log, file="figures/trial_theory_nejm_r21_log.pdf", width=5, height=5/1.6)
```

## 5. simulate trials under literature conditions (theoretical and stochastic approaches)
```{r}
#| label: simulate_with_lit

#' Simulate the trials approach with lit params, over the duration of positivity sigma OR pre-load saved csv file
# trial_df_lit <- sim_trials_over_sigma(pars=pars_lit_igra, sigmavec=1:80, reps=25)
trial_df_lit <- read_csv("output/trial_df_lit.csv")

#' Simulate the analytical approach with lit params, over the duration of positivity sigma
theoretical_df_lit <- sim_theory_over_sigma(pars=pars_lit_igra, sigmavec=seq(from=.5, to=80, by=0.01), agedist=agedist)
theoretical_df_lit %>% filter(sigma %in% c(0.5, 1, 1.5, 2, 5))

#' Plot all results
fig_trial_theory_lit <- plot_trial_theory(trial_df_lit, theoretical_df_lit, cols=c("n_tested","n_recruited","n_fast","n_overall")) + 
	labs(title="Literature parameters")
fig_trial_theory_lit
ggsave(fig_trial_theory_lit, file="figures/trial_theory_lit.pdf", width=5, height=5/1.6)

fig_trial_theory_log_lit <- fig_trial_theory_lit + scale_y_continuous(trans="log10")
fig_trial_theory_log_lit
ggsave(fig_trial_theory_log_lit, file="figures/trial_theory_log_lit.pdf", width=5, height=5/1.6)

fig_screenslope_lit <- plot_screenslope(theoretical_df_lit)
fig_screenslope_lit
```

Possible extensions to the above basic workflow are to include custom age distribution in `sim_trial` and custom fast targets for `sim_trials_over_sigma` and `sim_theory_over_sigma`.