---
title: "run_analysis"
format: html
---

This Quarto Markdown file outlines a workflow for running all steps of the analysis. It is based on the example workflow in `code/trialsim_rote.R` and has been copied to a .qmd for ease of editing and commenting.

## 1. load packages, functions, data
```{r}
#| label: setup

library(tidyverse)
library(readxl)
library(future.apply)
library(progressr)
library(countrycode)
library(zoo)
source('code/utils.R')
plan(multisession, workers=8)  # use multiple cores for speed

unwpp <- read_excel("data/WPP2024_POP_F01_1_POPULATION_SINGLE_AGE_BOTH_SEXES.xlsx", skip = 16) %>%  # populations from UNWPP
  filter(Year == 2023 & Type == "Country/Area") %>% rename(country="Region, subregion, country or area *") %>%
  mutate(across(all_of(as.character(0:99)), ~ as.numeric(.x) * 1000)) %>% select(country, all_of(as.character(0:99))) %>% arrange(country)
global_TB_inc_report <- read.csv(file = "data/TB_burden_age_sex_2026-02-20.csv") %>%  # number of cases per year, 2024 from WHO
  filter(sex=="a" & risk_factor=="all") %>% select(country, year, age_group, best, lo, hi) %>% rename(cases=best, cases_lo=lo, cases_hi=hi) %>%
  filter(age_group %in% c("0-4","5-9","10-14","15-19","20-24","25-34","35-44","45-54","55-64","65plus")) %>%  # filter duplicate age groups
  mutate(pop = unlist(unname(mapply(get_pop, age_group, country, MoreArgs = list(unwpp = unwpp))))) %>%  # append population
  mutate(inc = cases/pop, inc_lo=cases_lo/pop, inc_hi=cases_hi/pop) %>%  # compute incidence
  select(country, year, age_group, inc, inc_lo, inc_hi) %>% numericize(age_group) %>% arrange(country, age_group)  # expand to single-year ages
#ARTI_by_age_studies <- read.csv(file="data/ARTI-by-age-estimates-from-literature_2010-2026.csv") %>% select(-notes) %>% numericize(age) %>% impute_ARTI_by_age()
progressor_type_by_age_studies <- read.csv(file="data/progressor-type-by-age-estimates-from-literature.csv") %>%
  numericize(age) %>% impute_probability_of_being_slow()
```

## 2. define age structure for the model e.g. uniform
```{r}
#| label: define_age_structure

age_structure <- "South Africa"  # works for "uniform" or any UN-recognised country, e.g. "South Africa"
foi_structure <- "base"  # works for "uniform4", "uniform6", ...
progression_structure <- "Vynnycky-1997"  # works for "uniform" or "Vynnycky-1997"
slow_structure <- "base"

agedist <- extract_age_distribution(unwpp, age_structure)  # population age distribution
rho_lit <- define_foi_by_age(foi_structure)  # force of infection by age
p_slow_lit <- extract_probability_of_being_slow(progressor_type_by_age_studies, progression_structure)  # prob of being a slow progressor, by age
mu_slow_lit <- define_mu_slow(slow_structure)

#' shorthand names for plots
iso3_agestructure <- if (age_structure!="uniform") countrycode(age_structure, origin="country.name.en", destination="iso3c") else "unif"
shorthand_progstructure <- if (progression_structure=="Vynnycky-1997") "Vynn" else if (progression_structure=="uniform") "unif"
fig_name <- paste0(iso3_agestructure,"_",foi_structure,"_",shorthand_progstructure, "_", slow_structure)  # pattern is agedist method _ foi _ p_slow method _ mu_slow
fig_labels <- paste0("pop agedist = ",iso3_agestructure,"; foi = ",foi_structure,"; p_slow = ",shorthand_progstructure)
```

## 3. define parameter values
`pars_m72IIb` currently uses values such that model outputs emulate the M72 Van Der Meeren trial outputs of # enrolled, # recruited etc. Note this is different to some of the values of the trial population itself (e.g. p_slow).

`pars_lit` takes best-known parameter values from the literature. 
```{r}
#| label: define_params

rho_m72IIb <- rep(0.0275,100)  # *uniform in pars_m72 for now*
p_slow_m72IIb <- rep(0.5,100)  # *uniform probability of being a slow progressor in pars_m72 for now*

pars_m72IIb_igra <- list(
	minage=18,  # from trial
	maxage=49,  # from trial (up to 50.0y)
	rho=rho_m72IIb,  #0.0275  # modelled value (range considered thus far: ~0.002-0.03 e.g. up to an order of mag greater than old lit)
	p_slow=p_slow_m72IIb,  # modelled value (range considered: ...)
	mu_slow=mu_slow_lit,  # assumed, informed by lit - could play around with this
	mu_fast=1.5,  # from lit
	sigma=100,  # IGRA test is essentially lifelong
	ve=0.55,  # from trial (technically 54% VE)
	trial_length=3)  # from trial (technically 2.3 years in Van Der Meeren)
pars_m72IIb_tasa <- pars_m72IIb_igra
pars_m72IIb_tasa$sigma <- 2

pars_lit_igra <- list(
	minage=18, # taken from above
	maxage=49, # taken from above
	rho=rho_lit,  # from lit, with choice of tinf method (foi_structure)
	p_slow=p_slow_lit,  # from lit
	mu_slow=mu_slow_lit,  # from lit
	mu_fast=1.5,  # for most fast progressors progressing within two years, assuming exponential distribution
	sigma=100,  # IGRA test is essentially lifelong
	ve=0.55, # taken from above, currently unused
	trial_length=3) # taken from above
#pars_lit_tasa <- pars_lit_igra 
#pars_lit_tasa$sigma <- 2
```

## 4. simulate trials under m72IIb conditions (analytical and stochastic approaches)
```{r}
#| label: simulate_with_m72IIb
#| eval: FALSE

#' Simulate the stochastic approach with m72IIb params, over the duration of positivity sigma OR pre-load saved csv file
with_progress({
  stochastic_df_m72IIb <- sim_stoch_over_sigma(pars=pars_m72IIb_igra, sigmavec=1:80, fasttarget=50, agedist=agedist, reps=25)
})
#stochastic_df_m72IIb <- read_csv("output/stochastic_df_m72IIb_uniform.csv")  # uniform agedist

#' Simulate the analytical approach with m72IIb params, over the duration of positivity sigma
analytical_df_m72IIb <- sim_analytic_over_sigma(pars=pars_m72IIb_igra, sigmavec=seq(from=.5, to=80, by=0.01), fasttarget=50, agedist=agedist)
analytical_df_m72IIb %>% filter(sigma %in% c(0.5, 1, 1.5, 2, 5))

#' Plot all results
fig_stochastic_analytic_m72IIb <- plot_stochastic_analytic(stochastic_df_m72IIb, analytical_df_m72IIb, 
                                           cols=c("n_tested","n_recruited","n_fast","n_overall")) + 
	labs(title="M72/AS01E trial emulation", subtitle=fig_labels)
fig_stochastic_analytic_m72IIb
ggsave(fig_stochastic_analytic_m72IIb, file=paste0("figures/stochastic_analytic_m72IIb_",fig_name,".pdf"), width=5, height=5/1.6)

#' Optional: estimate case incidence per 100k from model 
estimate_case_incidence_from_model(stochastic_df_m72IIb, pars=pars_m72IIb_igra, sig=80)
estimate_case_incidence_from_model(analytical_df_m72IIb, pars=pars_m72IIb_igra, sig=80)
```

## 5. simulate trials under literature conditions (analytical and stochastic approaches)
```{r}
#| label: simulate_with_lit
#| eval: FALSE

#' Simulate the stochastic approach with lit params, over the duration of positivity sigma OR pre-load saved csv file
with_progress({
  stochastic_df_lit <- sim_stoch_over_sigma(pars=pars_lit_igra, sigmavec=1:80, fasttarget=50, agedist=agedist, reps=2)
})
#stochastic_df_lit <- read_csv("output/stochastic_df_lit_uniform.csv")  # uniform agedist

#' Simulate the analytical approach with lit params, over the duration of positivity sigma
analytical_df_lit <- sim_analytic_over_sigma(pars=pars_lit_igra, sigmavec=seq(from=0.5, to=80, by=0.1), fasttarget=50, agedist=agedist)
analytical_df_lit %>% filter(sigma %in% c(0.5, 1, 1.5, 2, 5))

#' Plot all results
fig_stochastic_analytic_lit <- plot_stochastic_analytic(stochastic_df_lit, analytical_df_lit, cols=c("n_tested","n_recruited","n_fast","n_overall")) + 
	labs(title="Literature parameters", subtitle=fig_labels)
fig_stochastic_analytic_lit
ggsave(fig_stochastic_analytic_lit, file=paste0("figures/stochastic_analytic_lit_",fig_name,".pdf"), width=5, height=5/1.6)

#' Optional: estimate case incidence per 100k, infection prevalence, and ARTI from model (sigma=80)
from_model <- tibble()
for (i in 1:2) {
  cases <- estimate_case_incidence_from_model(stochastic_df_lit, pars=pars_lit_igra, my_rep=i, sig=80)
  ARTI_and_prev <- estimate_ARTI_from_model(stochastic_df_lit, pars=pars_lit_igra, my_rep=i, sig=80)
  #estimate_ARTI_from_model(analytical_df_lit, pars=pars_lit_igra, my_rep=i, sig=80)
  from_model <- bind_rows(from_model, tibble(i = i, infection_prevalence = ARTI_and_prev["infection_prevalence"], ARTI = ARTI_and_prev["ARTI"], cases= cases))
}
#summary_table <- tibble()
summary_table <- bind_rows(summary_table, tibble(foi_structure=foi_structure, infection_prevalence=median(from_model$infection_prevalence), 
                                                 ARTI=median(from_model$ARTI), cases=median(from_model$cases)))
```

# 6. (Optional) Parameter fitting: simulate trials under literature conditions, for different foi's
Note: run code snippets 1-3 first.
```{r}
#| label: parameter_fit

foi_structures <- c("base", "min", "max", "incr", "decr")
progression_structures <- c("uniform", "Vynnycky-1997")
slow_structures <- c("base", "min", "max") #, "Vynnycky" )
summary_table <- tibble()
reps <- 1

for (progression_structure in progression_structures) {
  # Redefine parameter which is looped
  prog <- extract_probability_of_being_slow(progressor_type_by_age_studies, progression_structure)  # prob of being slow
  pars_lit_igra$p_slow <- prog
  
  for (slow_structure in slow_structures) {
    # Redefine parameter which is looped
    mu_slow <- define_mu_slow(slow_structure)  # rate of progression to disease for slow progressors
    pars_lit_igra$mu_slow <- mu_slow
    
    for (foi_structure in foi_structures) {
    # Redefine parameter which is looped
    foi <- define_foi_by_age(foi_structure)  # force of infection by age
    pars_lit_igra$rho <- foi
  
    # Simulate stochastic and analytic approaches
    with_progress({stochastic_df_lit <- sim_stoch_over_sigma(pars=pars_lit_igra, sigmavec=c(80), fasttarget=50, agedist=agedist, reps=reps)})
    analytical_df_lit <- sim_analytic_over_sigma(pars=pars_lit_igra, sigmavec=seq(from=80, to=80, by=0.1), fasttarget=50, agedist=agedist)
  
    # Estimate case incidence per 100k, infection prevalence, and ARTI from model (sigma=80)
    from_model <- tibble()
    cases2 <- estimate_case_incidence_from_model(analytical_df_lit, pars=pars_lit_igra, sig=80)  # 1=stochastic, 2=analytic
    ARTI2 <- estimate_ARTI_from_model(analytical_df_lit, pars=pars_lit_igra, sig=80)
    infection_prevalence1 <- estimate_inf_prev_from_model(foi)
    for (i in 1:reps) {
      cases1 <- estimate_case_incidence_from_model(stochastic_df_lit, pars=pars_lit_igra, my_rep=i, sig=80)
      ARTI1 <- estimate_ARTI_from_model(stochastic_df_lit, pars=pars_lit_igra, my_rep=i, sig=80)
      from_model <- bind_rows(from_model, tibble(i = i, ARTI1 = ARTI1["ARTI"], cases1= cases1))
    }
    summary_table <- bind_rows(summary_table, tibble(progression_structure=progression_structure, slow_structure=slow_structure, foi_structure=foi_structure, 
                                                     as_tibble_row(infection_prevalence1), ARTI1=median(from_model$ARTI1),
                                                     cases_min1=min(from_model$cases1), cases_max1=max(from_model$cases1), ARTI2=ARTI2["ARTI"], cases2=cases2))
    }
  }
}
summary_table <- summary_table %>% mutate(conditions_met = (between(inf_prev_age20, 0.57, 0.77) & between(inf_prev_age30, 0.67, 0.92) &
                                             between(inf_prev_age40, 0.59, 0.95) & between(ARTI1, 0.035, 0.065) & cases_max1 > 200))  # NB: our model has no recovery
#write.csv(summary_table, file="output/parameter_fit_results.csv", row.names=FALSE)
```