---
title: "run_analysis"
format: html
---

This Quarto Markdown file outlines a workflow for running all steps of the analysis. It is based on the example workflow in `code/trailsim_rote.R` and has been copied to a .qmd for ease of editing and commenting.

## 1. load packages, functions, data
```{r}
#| label: setup

library(tidyverse)
library(readxl)
source('code/utils.R')
unwpp <- read_excel("data/WPP2024_POP_F01_1_POPULATION_SINGLE_AGE_BOTH_SEXES.xlsx", skip = 16) %>%  # populations from UNWPP
  filter(Year == 2023 & Type == "Country/Area") %>% rename(country="Region, subregion, country or area *") %>%
  mutate(across(all_of(as.character(0:99)), ~ as.numeric(.x) * 1000)) %>% select(country, all_of(as.character(0:99))) %>% arrange(country)
global_TB_report <- read.csv(file = "data/TB_burden_age_sex_2026-02-20.csv") %>%  # number of cases per year, 2024 from WHO
  filter(sex=="a" & risk_factor=="all") %>% select(country, year, age_group, best, lo, hi) %>% rename(cases=best, cases_lo=lo, cases_hi=hi) %>%
  filter(age_group %in% c("0-4","5-9","10-14","15-19","20-24","25-34","35-44","45-54","55-64","65plus")) %>%  # filter duplicate age groups
  mutate(pop = unlist(unname(mapply(get_pop, age_group, country, MoreArgs = list(unwpp = unwpp))))) %>%  # append population
  mutate(inc = cases/pop, inc_lo=cases_lo/pop, inc_hi=cases_hi/pop) %>%  # compute incidence
  select(country, year, age_group, inc, inc_lo, inc_hi) %>% numericize(age_group) %>% arrange(country, age_group)  # expand to single-year ages
```

## 2. define age structure for the model e.g. uniform
```{r}
#| label: define_age_structure

age_structure <- "South Africa"  # works for "uniform" or any UN-recognised country, e.g. "South Africa"
agedist <- extract_age_distribution(unwpp, age_structure)  # population age distribution
inc_by_age <- extract_incidence_by_age(global_TB_report, age_structure)  # incidence by age
```

## 3. define parameter values
```{r}
#| label: define_params

rho_m72IIb <- rep(0.0275,100)  # *uniform for now*
rho_lit <- inc_by_age  # incidence by age from above
  
pars_m72IIb_igra <- list(
	minage=18,
	maxage=49,
	rho=rho_m72IIb,
	p_slow=0.5,
	mu_slow=0.0001,
	mu_fast=1.5,
	sigma=100,
	ve=0.55,
	trial_length=3)
pars_m72IIb_tasa <- pars_m72IIb_igra
pars_m72IIb_tasa$sigma <- 2

pars_lit_igra <- list(
	minage=18,
	maxage=49,
	rho=rho_lit,
	p_slow=0.95,
	mu_slow=0.0001,
	mu_fast=1.5,
	sigma=100,
	ve=0.55,
	trial_length=3)
pars_lit_tasa <- pars_lit_igra 
pars_lit_tasa$sigma <- 2
```

## 4. simulate trials under m72IIb conditions (analytical and stochastic approaches)
```{r}
#| label: simulate_with_m72IIb

#' Simulate the stochastic approach with m72IIb params, over the duration of positivity sigma OR pre-load saved csv file
stochastic_df_m72IIb <- sim_stoch_over_sigma(pars=pars_m72IIb_igra, sigmavec=1:80, fasttarget=50, agedist=agedist, reps=1)
#stochastic_df_m72IIb <- read_csv("output/stochastic_df_m72IIb_uniform.csv")  # uniform agedist

#' Simulate the analytical approach with m72IIb params, over the duration of positivity sigma
analytical_df_m72IIb <- sim_analytic_over_sigma(pars=pars_m72IIb_igra, sigmavec=seq(from=.5, to=80, by=0.01), agedist=agedist)
analytical_df_m72IIb %>% filter(sigma %in% c(0.5, 1, 1.5, 2, 5))

#' Plot all results
fig_stochastic_analytic_m72IIb <- plot_stochastic_analytic(stochastic_df_m72IIb, analytical_df_m72IIb, 
                                           cols=c("n_tested","n_recruited","n_fast","n_overall")) + 
	labs(title="M72/AS01E trial emulation", subtitle=paste0("age_structure = ", age_structure))
fig_stochastic_analytic_m72IIb
ggsave(fig_stochastic_analytic_m72IIb, file=paste0("figures/stochastic_analytic_m72IIb_",age_structure,".pdf"), width=5, height=5/1.6)

# fig_stochastic_analytic_log_m72IIb <- fig_stochastic_analytic_m72IIb + scale_y_continuous(trans="log10")
# fig_stochastic_analytic_log_m72IIb
# ggsave(fig_stochastic_analytic_log_m72IIb, file="figures/stochastic_analytic_log_m72IIb.pdf", width=5, height=5/1.6)
# 
# fig_screenslope_m72IIb <- plot_screenslope(analytical_df_m72IIb)
# fig_screenslope_m72IIb


fig_stochastic_analytic_m72IIb_r21 <- plot_stochastic_analytic(stochastic_df_m72IIb, analytical_df_m72IIb, cols=c("n_tested","n_recruited")) + 
	labs(title="M72/AS01E trial emulation", subtitle=paste0("age_structure = ", age_structure))
fig_stochastic_analytic_m72IIb_r21
ggsave(fig_stochastic_analytic_m72IIb_r21, file=paste0("figures/stochastic_analytic_m72IIb_r21_",age_structure,".pdf"), width=5, height=5/1.6)

# fig_stochastic_analytic_m72IIb_r21_log <- plot_stochastic_analytic(stochastic_df_m72IIb, analytical_df_m72IIb, 
#                                                    cols=c("n_tested","n_recruited")) + 
# 	labs(title="M72/AS01E trial emulation") + 
# 	scale_y_continuous(trans="log10")
# fig_stochastic_analytic_m72IIb_r21_log
# ggsave(fig_stochastic_analytic_m72IIb_r21_log, file="figures/stochastic_analytic_m72IIb_r21_log.pdf", width=5, height=5/1.6)
```

## 5. simulate trials under literature conditions (analytical and stochastic approaches)
```{r}
#| label: simulate_with_lit

#' Simulate the stochastic approach with lit params, over the duration of positivity sigma OR pre-load saved csv file
stochastic_df_lit <- sim_stoch_over_sigma(pars=pars_lit_igra, sigmavec=1:80, fasttarget=50, agedist=agedist, reps=1)
#stochastic_df_lit <- read_csv("output/stochastic_df_lit_uniform.csv")  # uniform agedist

#' Simulate the analytical approach with lit params, over the duration of positivity sigma
analytical_df_lit <- sim_analytic_over_sigma(pars=pars_lit_igra, sigmavec=seq(from=.5, to=80, by=0.01), agedist=agedist)
analytical_df_lit %>% filter(sigma %in% c(0.5, 1, 1.5, 2, 5))

#' Plot all results
fig_stochastic_analytic_lit <- plot_stochastic_analytic(stochastic_df_lit, analytical_df_lit, cols=c("n_tested","n_recruited","n_fast","n_overall")) + 
	labs(title="Literature parameters", subtitle=paste0("age_structure = ", age_structure))
fig_stochastic_analytic_lit
ggsave(fig_stochastic_analytic_lit, file=paste0("figures/stochastic_analytic_lit_",age_structure,".pdf"), width=5, height=5/1.6)

# fig_stochastic_analytic_log_lit <- fig_stochastic_analytic_lit + scale_y_continuous(trans="log10")
# fig_stochastic_analytic_log_lit
# ggsave(fig_stochastic_analytic_log_lit, file="figures/stochastic_analytic_log_lit.pdf", width=5, height=5/1.6)
# 
# fig_screenslope_lit <- plot_screenslope(analytical_df_lit)
# fig_screenslope_lit
```

Possible extensions to the above workflow are to include custom fast targets for `sim_stoch_over_sigma` and `sim_analytic_over_sigma`.