---
title: "run_analysis"
format: html
---

This Quarto Markdown file outlines a workflow for running all steps of the analysis. It is based on the example workflow in `code/trialsim_rote.R` and has been copied to a .qmd for ease of editing and commenting.

## 1. load packages, functions, data
```{r}
#| label: setup

library(tidyverse)
library(readxl)
library(future.apply)
library(progressr)
library(countrycode)
library(zoo)
source('code/utils.R')
plan(multisession, workers=1)  # use multiple cores for speed

unwpp <- read_excel("data/WPP2024_POP_F01_1_POPULATION_SINGLE_AGE_BOTH_SEXES.xlsx", skip = 16) %>%  # populations from UNWPP
  filter(Year == 2023 & Type == "Country/Area") %>% rename(country="Region, subregion, country or area *") %>%
  mutate(across(all_of(as.character(0:99)), ~ as.numeric(.x) * 1000)) %>% select(country, all_of(as.character(0:99))) %>% arrange(country)
global_TB_inc_report <- read.csv(file = "data/TB_burden_age_sex_2026-02-20.csv") %>%  # number of cases per year, 2024 from WHO
  filter(sex=="a" & risk_factor=="all") %>% select(country, year, age_group, best, lo, hi) %>% rename(cases=best, cases_lo=lo, cases_hi=hi) %>%
  filter(age_group %in% c("0-4","5-9","10-14","15-19","20-24","25-34","35-44","45-54","55-64","65plus")) %>%  # filter duplicate age groups
  mutate(pop = unlist(unname(mapply(get_pop, age_group, country, MoreArgs = list(unwpp = unwpp))))) %>%  # append population
  mutate(inc = cases/pop, inc_lo=cases_lo/pop, inc_hi=cases_hi/pop) %>%  # compute incidence
  select(country, year, age_group, inc, inc_lo, inc_hi) %>% numericize(age_group) %>% arrange(country, age_group)  # expand to single-year ages
# ARTI_by_age_studies <- read.csv(file="data/ARTI-by-age-estimates-from-literature_2010-2026.csv") %>%
#   select(-notes) %>% numericize(age) %>% impute_ARTI_by_age()
progressor_type_by_age_studies <- read.csv(file="data/progressor-type-by-age-estimates-from-literature.csv") %>%
  numericize(age) %>% impute_probability_of_being_slow()
```

## 2. define age structure for the model e.g. uniform
```{r}
#| label: define_age_structure

age_structure <- "South Africa"  # works for "uniform" or any UN-recognised country, e.g. "South Africa"
# unique(ARTI_by_age_studies$country)  # countries for which ARTI-by-age data exists
# arti_structure <- "South Africa"  # works for "uniform" or the above countries
foi_structure <- "test"
progression_structure <- "Vynnycky-1997"  # works for "uniform" or "Vynnycky-1997"

agedist <- extract_age_distribution(unwpp, age_structure)  # population age distribution
#ARTI <- extract_ARTI_by_age(ARTI_by_age_studies, arti_structure, lo=F)  # annual risk of infection by age
foi <- rep(0.04,100) # force of infection by age
prog <- extract_probability_of_being_slow(progressor_type_by_age_studies, progression_structure)  # prob of being a slow progressor, by age

#' shorthand names for plots
iso3_agestructure <- if (age_structure!="uniform") countrycode(age_structure, origin="country.name.en", destination="iso3c") else "unif"
iso3_foistructure <- if (foi_structure!="test") countrycode(foi_structure, origin="country.name.en", destination="iso3c") else "test"
shorthand_progstructure <- if (progression_structure=="Vynnycky-1997") "Vynn" else if (progression_structure=="uniform") "unif"
fig_name <- paste0(iso3_agestructure,"_",iso3_foistructure,"_",shorthand_progstructure)  # pattern is agedist method _ tinf method _ p_slow method
fig_labels <- paste0("pop agedist = ",iso3_agestructure,"; foi = ",iso3_foistructure,"; p_slow = ",shorthand_progstructure)
```

## 3. define parameter values
`pars_m72IIb` currently uses values such that model outputs emulate the M72 Van Der Meeren trial outputs of # enrolled, # recruited etc. Note this is different to some of the values of the trial population itself (e.g. p_slow).

`pars_lit` takes best-known parameter values from the literature. 
```{r}
#| label: define_params

rho_m72IIb <- rep(0.0275,100)  # *uniform in pars_m72 for now*
#ARTI[20:40] <- ARTI[20:40]*5  # test
rho_lit <- foi  #ARTI
p_slow_m72IIb <- rep(0.5,100)  # *uniform probability of being a slow progressor in pars_m72 for now*
p_slow_lit <- prog

pars_m72IIb_igra <- list(
	minage=18,  # from trial
	maxage=49,  # from trial (up to 50.0y)
	rho=rho_m72IIb,  #0.0275  # modelled value (range considered thus far: ~0.002-0.03 e.g. up to an order of mag greater than old lit)
	p_slow=p_slow_m72IIb,  # modelled value (range considered: ...)
	mu_slow=0.0001,  # assumed, informed by lit - could play around with this
	mu_fast=1.5,  # from lit
	sigma=100,  # IGRA test is essentially lifelong
	ve=0.55,  # from trial (technically 54% VE)
	trial_length=3)  # from trial (technically 2.3 years in Van Der Meeren)
pars_m72IIb_tasa <- pars_m72IIb_igra
pars_m72IIb_tasa$sigma <- 2

pars_lit_igra <- list(
	minage=18, # taken from above
	maxage=49, # taken from above
	rho=rho_lit,  # from lit, with choice of tinf method (arti_structure)
	p_slow=p_slow_lit,  # from lit
	mu_slow=0.0001,  # from lit
	mu_fast=1.5,  # for most fast progressors progressing within two years, assuming exponential distribution
	sigma=100,  # IGRA test is essentially lifelong
	ve=0.55, # taken from above, currently unused
	trial_length=3) # taken from above
pars_lit_tasa <- pars_lit_igra 
pars_lit_tasa$sigma <- 2
```

## 4. simulate trials under m72IIb conditions (analytical and stochastic approaches)
```{r}
#| label: simulate_with_m72IIb
#| eval: FALSE

#' Simulate the stochastic approach with m72IIb params, over the duration of positivity sigma OR pre-load saved csv file
with_progress({
  stochastic_df_m72IIb <- sim_stoch_over_sigma(pars=pars_m72IIb_igra, sigmavec=1:80, fasttarget=50, agedist=agedist, reps=1)
})
#stochastic_df_m72IIb <- read_csv("output/stochastic_df_m72IIb_uniform.csv")  # uniform agedist

#' Simulate the analytical approach with m72IIb params, over the duration of positivity sigma
analytical_df_m72IIb <- sim_analytic_over_sigma(pars=pars_m72IIb_igra, sigmavec=seq(from=.5, to=80, by=0.01), fasttarget=50, agedist=agedist)
analytical_df_m72IIb %>% filter(sigma %in% c(0.5, 1, 1.5, 2, 5))

#' Plot all results
fig_stochastic_analytic_m72IIb <- plot_stochastic_analytic(stochastic_df_m72IIb, analytical_df_m72IIb, 
                                           cols=c("n_tested","n_recruited","n_fast","n_overall")) + 
	labs(title="M72/AS01E trial emulation", subtitle=fig_labels)
fig_stochastic_analytic_m72IIb
ggsave(fig_stochastic_analytic_m72IIb, file=paste0("figures/stochastic_analytic_m72IIb_",fig_name,".pdf"), width=5, height=5/1.6)

#' Optional: estimate case incidence per 100k from model 
estimate_case_incidence_from_model(stochastic_df_m72IIb, pars=pars_m72IIb_igra, sig=80)
estimate_case_incidence_from_model(analytical_df_m72IIb, pars=pars_m72IIb_igra, sig=80)
```

## 5. simulate trials under literature conditions (analytical and stochastic approaches)
```{r}
#| label: simulate_with_lit

#' Simulate the stochastic approach with lit params, over the duration of positivity sigma OR pre-load saved csv file
with_progress({
  stochastic_df_lit <- sim_stoch_over_sigma(pars=pars_lit_igra, sigmavec=c(80), fasttarget=50, agedist=agedist, reps=1)
})
#stochastic_df_lit <- read_csv("output/stochastic_df_lit_uniform.csv")  # uniform agedist

#' Simulate the analytical approach with lit params, over the duration of positivity sigma
analytical_df_lit <- sim_analytic_over_sigma(pars=pars_lit_igra, sigmavec=seq(from=80, to=80, by=0.01), fasttarget=50, agedist=agedist)
analytical_df_lit %>% filter(sigma %in% c(0.5, 1, 1.5, 2, 5))

#' Plot all results
fig_stochastic_analytic_lit <- plot_stochastic_analytic(stochastic_df_lit, analytical_df_lit, cols=c("n_tested","n_recruited","n_fast","n_overall")) + 
	labs(title="Literature parameters", subtitle=fig_labels)
fig_stochastic_analytic_lit
ggsave(fig_stochastic_analytic_lit, file=paste0("figures/stochastic_analytic_lit_",fig_name,".pdf"), width=5, height=5/1.6)

#' Optional: estimate case incidence per 100k from model 
cases <- vector()
for (i in 1:1) {
  cases[i] <- estimate_case_incidence_from_model(stochastic_df_lit, pars=pars_lit_igra, my_rep=i, sig=80)
  #estimate_case_incidence_from_model(analytical_df_lit, pars=pars_lit_igra, my_rep=i, sig=80)
}
min(cases)
max(cases)
median(cases)
```
