---
title: "run_analysis"
format: html
---

This Quarto Markdown file outlines a workflow for running all steps of the analysis. It is based on the example workflow in `code/trialsim_rote.R`.

## 1. load packages, functions, data

```{r}
#| label: setup

library(tidyverse)
library(readxl)
library(future.apply)
library(progressr)
library(countrycode)
library(zoo)
source('code/utils.R')
plan(multisession, workers=10)  # use multiple cores for speed

# Extract and pre-process data sets
unwpp <- read_excel("data/WPP2024_POP_F01_1_POPULATION_SINGLE_AGE_BOTH_SEXES.xlsx", skip = 16) %>%  # populations from UNWPP
  filter(Year == 2023 & Type == "Country/Area") %>% rename(country="Region, subregion, country or area *") %>%
  mutate(across(all_of(as.character(0:99)), ~ as.numeric(.x) * 1000)) %>% select(country, all_of(as.character(0:99))) %>% arrange(country)
global_TB_inc_report <- read.csv(file = "data/TB_burden_age_sex_2026-02-20.csv") %>%  # number of cases per year, 2024 from WHO
  filter(sex=="a" & risk_factor=="all") %>% select(country, year, age_group, best, lo, hi) %>% rename(cases=best, cases_lo=lo, cases_hi=hi) %>%
  filter(age_group %in% c("0-4","5-9","10-14","15-19","20-24","25-34","35-44","45-54","55-64","65plus")) %>%  # filter duplicate age groups
  mutate(pop = unlist(unname(mapply(get_pop, age_group, country, MoreArgs = list(unwpp = unwpp))))) %>%  # append population
  mutate(inc = cases/pop, inc_lo=cases_lo/pop, inc_hi=cases_hi/pop) %>%  # compute incidence
  select(country, year, age_group, inc, inc_lo, inc_hi) %>% numericize(age_group) %>% arrange(country, age_group)  # expand to single-year ages
#ARTI_by_age_studies <- read.csv(file="data/ARTI-by-age-estimates-from-literature_2010-2026.csv") %>% select(-notes) %>% numericize(age) %>% impute_ARTI_by_age()
progressor_type_by_age_studies <- read.csv(file="data/progressor-type-by-age-estimates-from-literature.csv") %>%
  numericize(age) %>% impute_probability_of_being_slow()

# Estimate reversion rate
Dagnew_reversion_data <- left_join(read.csv("data/Dagnew_2026_IGRA_status_at_day_1_table_s4.csv"), read.csv("data/Dagnew_2026_IGRA_reversion_conversion_table_s6.csv"), by = c("country", "site_no" = "site_number")) %>%  # reversion data from Dagnew et al.
  select(country, site_no, N_D1, n_positive_D1, N_M12, reversion_n) %>%
  group_by(country) %>% summarise(across(c(N_D1, n_positive_D1, N_M12, reversion_n), sum)) %>%  # summing across sites
  mutate(prob_of_reversion_once_infected = reversion_n / (n_positive_D1*N_M12/N_D1))  # probability of reverting once infected = no of reversions / approx no of initial positives who completed the study
```

## 2. define age structure for the model e.g. uniform

```{r}
#| label: define_age_structure

age_structure <- "South Africa"  # works for "uniform" or any UN-recognised country, e.g. "South Africa"
#foi_structure <- "uniform_4"  # works for "uniform4", "uniform6", ... with define_foi_by_age()
progression_structure <- "Vynnycky-high"  # works for "uniform" or "Vynnycky-1997" or "Vynnycky-high"
slow_structure <- "0.003"

agedist <- extract_age_distribution(unwpp, age_structure)  # population age distribution
rho_lit <- make_foi(3,6,7,6,5)  # force of infection by age
p_slow_lit <- extract_probability_of_being_slow(progressor_type_by_age_studies, progression_structure)  # prob of being a slow progressor, by age
mu_slow_lit <- define_mu_slow(slow_structure)
p_revert_lit <- Dagnew_reversion_data %>% filter(country=="South Africa") %>% pull(prob_of_reversion_once_infected)

#' shorthand names for plots
foi_name <- "36765"
iso3_agestructure <- if (age_structure!="uniform") countrycode(age_structure, origin="country.name.en", destination="iso3c") else "unif"
shorthand_progstructure <- if (progression_structure=="Vynnycky-1997") "Vynn" else if (progression_structure=="uniform") "unif"
fig_name <- paste0(iso3_agestructure,"_",foi_name,"_",shorthand_progstructure, "_", slow_structure)  # pattern is agedist method _ foi _ p_slow method _ mu_slow
fig_labels <- paste0("pop agedist = ",iso3_agestructure,"; foi = ",foi_name,"; p_slow = ",shorthand_progstructure)
```

## 3. define parameter values

`pars_m72IIb` currently uses values such that model outputs emulate the M72 Van Der Meeren trial outputs of \# enrolled etc. Note this is different to some of the values of the trial population itself (e.g. p_slow).

`pars_lit` takes best-known parameter values from the literature.

```{r}
#| label: define_params

rho_m72IIb <- rho_lit
names(rho_m72IIb) <- 0:99
p_slow_m72IIb <- rep(0.5,100)  # *uniform probability of being a slow progressor in pars_m72 for now*
names(p_slow_m72IIb) <- 0:99

pars_m72IIb_igra <- list(
	minage=18,  # from trial
	maxage=49,  # from trial (up to 50.0y)
	rho=rho_m72IIb,  # modelled value
	p_slow=p_slow_m72IIb,  # modelled value
	mu_slow=mu_slow_lit,  # assumed, informed by lit - could play around with this
	mu_fast=1.5,  # from lit
	p_revert=p_revert_lit, # tbd
	mu_revert=0.75, # tbd
	sigma=100,  # IGRA test is essentially lifelong
	trial_length=3)  # from trial (technically 2.3 years in Van Der Meeren)
# pars_m72IIb_tasa <- pars_m72IIb_igra
# pars_m72IIb_tasa$sigma <- 2

pars_lit_igra <- list(
	minage=15, # taken from above
	maxage=49, # taken from above
	rho=rho_lit,  # from lit, with choice of tinf method (foi_structure)
	p_slow=p_slow_lit,  # from lit
	mu_slow=mu_slow_lit,  # from lit
	mu_fast=1.5,  # for most fast progressors progressing within two years, assuming exponential distribution
	p_revert=p_revert_lit,  # from lit
	mu_revert=0.75, # for most reverters reverting within two years, assuming exponential dist
	sigma=100,  # IGRA test is essentially lifelong
	trial_length=3) # taken from above
```

## 4. simulate trials under m72IIb conditions (analytic and stochastic approaches)

```{r}
#| label: simulate_with_m72IIb
#| eval: FALSE

#' Simulate the stochastic approach with m72IIb params, over the duration of positivity sigma OR pre-load saved csv file
with_progress({
  stochastic_df_m72IIb <- sim_stoch_over_sigma(pars=pars_m72IIb_igra, sigmavec=1:80, casetarget=50, agedist=agedist, reps=1)  ## NB: THIS JUST USES sim_stoch() NOT sim_stoch_trial() - MIGHT WANT TO CHANGE
})
#stochastic_df_m72IIb <- read_csv("output/stochastic_df_m72IIb_uniform.csv")  # uniform agedist

#' Simulate the analytical approach with m72IIb params, over the duration of positivity sigma
analytical_df_m72IIb <- sim_analytic_over_sigma(pars=pars_m72IIb_igra, sigmavec=seq(from=.5, to=80, by=0.1), casetarget=50, agedist=agedist)

#' Plot all results
fig_stochastic_analytic_m72IIb <- plot_stochastic_analytic(stochastic_df_m72IIb, analytical_df_m72IIb, 
                                           cols=c("n_tested","n_enrolled","n_overall")) + 
	labs(title="M72/AS01E trial emulation", subtitle=fig_labels)
fig_stochastic_analytic_m72IIb
ggsave(fig_stochastic_analytic_m72IIb, file=paste0("figures/stochastic_analytic_m72IIb_",fig_name,".png"), width=7.29, height=4.51)
```

## 4b. parameter fitting: m72IIb trial

Rather than stopping at casetarget=50 and scaling up, `sim_stoch_trial` recruits until enrol_target is reached.

```{r}
#| label: simulate_with_m72IIb_fit
#| eval: FALSE

target_enrolled <- 3289
target_cases    <- 52

foi_m72IIb  <- make_foi(3,6,7,6,5)
slow_structures_m72IIb <- c("base", "min", "max", "0.003")
p_slow_m72IIb_vals     <- seq(0.5, 1.0, by=0.05)
p_slow_lit <- extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-1997")
reps <- 25

# Build a flat grid of all parameter combinations x reps
uniform_grid <- expand.grid(
  slow_structure = slow_structures_m72IIb,
  p_slow_label   = paste0("uniform_", seq(0.5, 0.95, by=0.05)),
  rep            = 1:reps,
  stringsAsFactors = FALSE
)
vynnycky_grid <- expand.grid(
  slow_structure = slow_structures_m72IIb,
  p_slow_label   = c("Vynnycky-1997", "Vynnycky-high"),
  rep            = 1:reps,
  stringsAsFactors = FALSE
)
param_grid <- bind_rows(uniform_grid, vynnycky_grid)

with_progress({
  p <- progressr::progressor(steps=nrow(param_grid))
  trial_results_list <- future.apply::future_lapply(1:nrow(param_grid), function(i) {
    pars_fit         <- pars_m72IIb_igra
    pars_fit$mu_slow <- define_mu_slow(param_grid$slow_structure[i])
    pars_fit$rho     <- foi_m72IIb
    pars_fit$p_slow <- if (param_grid$p_slow_label[i] == "Vynnycky-1997") {
      p_slow_lit 
      } else if (param_grid$p_slow_label[i] == "Vynnycky-high") {
        extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-high")
      } else {
        val <- as.numeric(sub("uniform_", "", param_grid$p_slow_label[i]))
        setNames(rep(val, 100), 0:99)
      }
    out <- sim_stoch_trial(pars_fit, enrol_target=target_enrolled, agedist=agedist)
    p()
    tibble(
      p_slow_structure= param_grid$p_slow_label[i],
      mu_slow        = pars_fit$mu_slow,
      foi_structure  = param_grid$foi_structure[i],
      rep            = param_grid$rep[i],
      n_overall      = out$n_overall,
      n_tested       = out$n_tested,
      n_enrolled     = out$n_enrolled,
      n_trial_cases  = out$n_trial_cases  
    )
  }, future.seed=TRUE)
})

trial_results <- bind_rows(trial_results_list)

#' Summarise over reps
m72IIb_fit_trial <- trial_results %>%
  group_by(p_slow_structure, mu_slow) %>%
  summarise(
    n_overall_med = round(median(n_overall)),
    n_enrolled_med = round(median(n_enrolled)),
    n_trial_cases_med = round(median(n_trial_cases), 1),
    n_trial_cases_lo  = round(quantile(n_trial_cases, 0.1), 1),
    n_trial_cases_hi  = round(quantile(n_trial_cases, 0.9), 1),
    .groups       = "drop"
  ) %>%
  mutate(case_target_met = between(n_trial_cases_med, target_cases * 0.8, target_cases * 1.2))

head(m72IIb_fit_trial)
write.csv(m72IIb_fit_trial, file="output/m72IIb_fit_results.csv", row.names=FALSE)
```

## 5. simulate trials under literature conditions (analytic and stochastic approaches)

```{r}
#| label: simulate_with_lit
#| eval: FALSE

pars_lit_igra$rho <- make_foi(3,6,7,6,5)
#' Simulate the stochastic approach with lit params, over the duration of positivity sigma OR pre-load saved csv file
with_progress({
  stochastic_df_lit <- sim_stoch_over_sigma(pars=pars_lit_igra, sigmavec=c(0.5,1:80), casetarget=50, agedist=agedist, reps=100)
})
#stochastic_df_lit <- read_csv("output/stochastic_df_lit_uniform.csv")  # uniform agedist

#' Simulate the analytical approach with lit params, over the duration of positivity sigma
analytical_df_lit <- sim_analytic_over_sigma(pars=pars_lit_igra, sigmavec=seq(from=0.5, to=80, by=0.2), casetarget=50, agedist=agedist)

#' Plot all results (per 1)
fig_stochastic_analytic_lit <- plot_stochastic_analytic(stochastic_df_lit, analytical_df_lit, ylimit=1000)
fig_stochastic_analytic_lit
ggsave(fig_stochastic_analytic_lit, file=paste0("figures/stochastic_analytic_lit_",fig_name,".png"), width=7.29, height=4.51)

#' Optional: estimate case incidence per 100k, infection prevalence, and ARTI from model (sigma=80)
from_model <- tibble()
for (i in 1:25) {
  cases <- calculate_case_incidence_at_time_of_recruitment_from_model(stochastic_df_lit, pars=pars_lit_igra, my_rep=i, sig=80)
  ARTI_and_prev <- estimate_ARTI_from_model(stochastic_df_lit, pars=pars_lit_igra, my_rep=i, sig=80)
  from_model <- bind_rows(from_model, tibble(i = i, inf_prev_15to24 = ARTI_and_prev["inf_prev_15to24"], 
                                             inf_prev_25to34 = ARTI_and_prev["inf_prev_25to34"], 
                                             ARTI = ARTI_and_prev["ARTI"], cases= cases))
}
```

## 6. (Optional) Parameter fitting: simulate trials under literature conditions (stochastic approach), for different parameter values

Note: run code snippets 1-3 first.

```{r}
#| label: parameter_fit
#| eval: FALSE

start.time <- Sys.time()
# define parameter search space
foi_grid_1 <- tibble(a0_4=1:10, a5_24=1:10, a25_34=1:10, a35_49=1:10, a50plus=1:10)  # initial uniform fits
foi_grid_2 <- expand.grid(a0_4=3:7, a5_24=3:7, a25_34=3:7, a35_49=3:7, a50plus=3:7)  # closer inspection of 3-7% as this looked promising from initial fits
foi_grid <- bind_rows(foi_grid_1, foi_grid_2) %>% distinct()
foi_structures <- make_foi(foi_grid)  # named list of 3125 vectors
progression_structures <- c("Vynnycky-1997", "Vynnycky-high")
slow_structures <- c("base", "min")  #c("base", "min", "max", "0.003")
summary_table <- tibble()
reps <- 5

# run sims
for (progression_structure in progression_structures) {
  # Redefine parameter which is looped
  prog <- extract_probability_of_being_slow(progressor_type_by_age_studies, progression_structure)  # prob of being slow
  pars_lit_igra$p_slow <- prog
  
  for (slow_structure in slow_structures) {
    # Redefine parameter which is looped
    mu_slow <- define_mu_slow(slow_structure)  # rate of progression to disease for slow progressors
    pars_lit_igra$mu_slow <- mu_slow
    
    for (foi_structure in names(foi_structures)) {
    # Redefine parameter which is looped
    foi <- foi_structures[[foi_structure]] # force of infection by age
    pars_lit_igra$rho <- foi
  
    # Simulate stochastic approach (sigma=80)
    with_progress({stochastic_df_lit <- sim_stoch_over_sigma(pars=pars_lit_igra, sigmavec=c(80), casetarget=50, agedist=agedist, reps=reps)})
    
    # Estimate case incidence per 100k, infection prevalence, and ARTI from model (sigma=80)
    from_model <- tibble()
    for (i in 1:reps) {
      cases <- calculate_case_incidence_at_time_of_recruitment_from_model(stochastic_df_lit, pars=pars_lit_igra, my_rep=i, sig=80)
      ARTI_and_prev <- estimate_ARTI_from_model(stochastic_df_lit, pars=pars_lit_igra, my_rep=i, sig=80)
      from_model <- bind_rows(from_model, tibble(i = i, inf_prev_15to24 = ARTI_and_prev["inf_prev_15to24"], 
                                             inf_prev_25to34 = ARTI_and_prev["inf_prev_25to34"], 
                                             ARTI = ARTI_and_prev["ARTI"], cases= cases))
    }
    summary_table <- bind_rows(summary_table, tibble(progression_structure=progression_structure, slow_structure=slow_structure, 
                                                     foi_structure=foi_structure, 
                                                     inf_prev_15to24=median(stochastic_df_lit$inf_prev_15to24),  # assuming sigmavec=c(80)
                                                     inf_prev_25to34=median(stochastic_df_lit$inf_prev_25to34),  # assuming sigmavec=c(80)
                                                     ARTI=median(from_model$ARTI), cases=median(from_model$cases)))
    }
  }
}

# extract infection prevalence data from Dagnew et al. for fitting
Dagnew_positivity_data <- read.csv("data/Dagnew_2026_IGRA_positivity_by_age_table_s5.csv") %>%
  select(country, site_no, age_group, pct_positive, ci_lo_positive, ci_hi_positive) %>%
  mutate(across(c(pct_positive, ci_lo_positive, ci_hi_positive), ~ .x / 100)) %>%  # convert % to proportion
  group_by(country, age_group) %>% summarise(min_positivity = min(ci_lo_positive), max_positivity = max(ci_hi_positive)) %>%
  ungroup()
dagnew_age20_min <- Dagnew_positivity_data %>% filter(country=="South Africa" & age_group=="15-24") %>% pull(min_positivity)
dagnew_age20_max <- Dagnew_positivity_data %>% filter(country=="South Africa" & age_group=="15-24") %>% pull(max_positivity)
dagnew_age30_min <- Dagnew_positivity_data %>% filter(country=="South Africa" & age_group=="25-34") %>% pull(min_positivity)
dagnew_age30_max <- Dagnew_positivity_data %>% filter(country=="South Africa" & age_group=="25-34") %>% pull(max_positivity)

# compute summary table and save
summary_table <- summary_table %>% mutate(conditions_met = between(inf_prev_15to24, dagnew_age20_min, dagnew_age20_max) & between(inf_prev_25to34, dagnew_age30_min, dagnew_age30_max) & between(ARTI, 0.04, 0.06) & between(cases, 242, 571))
write.csv(summary_table, file="output/parameter_fit_results.csv", row.names=FALSE) 
end.time <- Sys.time()
```

```{r}
#| eval: FALSE
# plot parameter fitting results
slow_labels <- c(
  "min"   = "μ_s = 0.0001",
  "base"  = "μ_s = 0.001",
  "0.003" = "μ_s = 0.003",
  "max"   = "μ_s = 0.00527"
)

prog_labels <- c(
  "Vynnycky-1997" = "4–14% age-varying",
  "Vynnycky-high" = "4–19% age-varying"
)

fig_6 <- summary_table %>%
  ggplot(aes(x=inf_prev_15to24, y=ARTI, shape=progression_structure, col=conditions_met)) +
  annotate("rect", xmin=dagnew_age20_min, xmax=dagnew_age20_max,
           ymin=0.04, ymax=0.06, alpha=0.1, fill="steelblue") +
  geom_vline(xintercept=c(dagnew_age20_min, dagnew_age20_max),
             linetype="dashed", col="steelblue", linewidth=0.4) +
  geom_hline(yintercept=c(0.04, 0.06),
             linetype="dashed", col="steelblue", linewidth=0.4) +
  geom_point(data=~filter(.x, !conditions_met), size=2, alpha=0.8) +
  geom_point(data=~filter(.x, conditions_met), size=2, alpha=0.8) +
  scale_colour_manual(values=c("FALSE"="grey80", "TRUE"="forestgreen")) +
  scale_shape_manual(values=c(16, 17), labels=prog_labels) +
  facet_wrap(~slow_structure, labeller=as_labeller(slow_labels)) +
  theme_classic() +
  theme(strip.background=element_blank()) +
  labs(x="Infection prevalence, age 15-24", y="ARTI",
       col="All conditions met", shape="p_f")

fig_6
ggsave(fig_6, file="figures/6_parameter_fit.png", width=7.29, height=4.51)

# summary table
library(flextable)
summary_table %>%
  filter(conditions_met) %>%
  select(foi_structure, progression_structure, slow_structure,
         inf_prev_15to24, inf_prev_25to34, ARTI, cases) %>%
  mutate(across(c(inf_prev_15to24, inf_prev_25to34), ~ round(.x, 2)),
         across(c(ARTI), ~ round(.x, 3)),
         across(c(cases), ~ round(.x, 0))) %>%
  arrange(slow_structure, progression_structure) %>%
  flextable() %>%
  autofit() %>%
  save_as_docx(path="output/parameter_fit_passing.docx")
```


## 7. (Scenarios)

Note: run code snippets 1-3 first.

## 7a. Varied vaccine trial sites

Compare trial recruitment requirements across three country populations (South Africa, India, Kenya) under a range of FOI structures and p_slow values. Parameters held constant: minage, maxage, sigma range, trial_length, mu_fast, mu_slow (0.003). Age distribution, FOI, and p_slow vary by scenario.

```{r}
#| label: 7a_varied_sites
#| eval: FALSE

plan(multisession, workers=8)  # reset worker pool in case of stale state from previous run

countries_7a      <- c("South Africa", "India", "Kenya")
foi_structures_7a <- c("uniform_1", "uniform_2", "uniform_3", "uniform_4", "uniform_5", "uniform_6", "uniform_7", "uniform_8", "uniform_9", "uniform_10")
p_slow_structures_7a <- list(
  "uniform_95"     = extract_probability_of_being_slow(progressor_type_by_age_studies, "uniform"),
  "Vynnycky-1997"  = extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-1997"),
  "Vynnycky-high"  = extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-high"))

# Pre-compute age distributions — keeps unwpp out of the future_lapply workers
agedists_7a <- setNames(lapply(countries_7a, function(c) extract_age_distribution(unwpp, c)), countries_7a)

# Build base parameter list (shared across all scenarios)
pars_7a <- pars_lit_igra
p_revert_7a <- list(
  "South Africa" = Dagnew_reversion_data %>% filter(country=="South Africa") %>% pull(prob_of_reversion_once_infected),
  "Kenya"        = Dagnew_reversion_data %>% filter(country=="Kenya") %>% pull(prob_of_reversion_once_infected),
  "India"        = Dagnew_reversion_data %>% filter(country=="Bangladesh") %>% pull(prob_of_reversion_once_infected))  # Bangladesh used as proxy for India

# Flat grid over all combinations: country x FOI x sigma x rep
sim_grid_7a <- bind_rows(tibble(country="India",        foi_structure=c("uniform_1","uniform_2")),
                         tibble(country="Kenya",        foi_structure=c("uniform_3","uniform_4")),
                         tibble(country="South Africa", foi_structure=c("uniform_5","uniform_6","uniform_7"))) %>%
  crossing(slow_structure = names(p_slow_structures_7a),
           sigma          = c(1:10, seq(15, 80, by=5)),
           rep            = 1:25)

# Single flat future_lapply — avoids nested parallelism and memory spikes
with_progress({
  p <- progressr::progressor(steps=nrow(sim_grid_7a))
  stoch_list_7a <- future.apply::future_lapply(1:nrow(sim_grid_7a), function(i) {
    pars_i        <- pars_7a
    pars_i$rho    <- define_foi_by_age(sim_grid_7a$foi_structure[i])
    pars_i$p_slow <- p_slow_structures_7a[[sim_grid_7a$slow_structure[i]]]
    pars_i$p_revert <- p_revert_7a[[sim_grid_7a$country[i]]]
    pars_i$sigma  <- sim_grid_7a$sigma[i]
    agedist_i     <- agedists_7a[[sim_grid_7a$country[i]]]
    out           <- sim_stoch(pars_i, casetarget=50, agedist=agedist_i)
    p()
    tibble(country=sim_grid_7a$country[i], foi_structure=sim_grid_7a$foi_structure[i],
       slow_structure=sim_grid_7a$slow_structure[i], sigma=sim_grid_7a$sigma[i], rep=sim_grid_7a$rep[i],
       n_tested=out$n_tested, n_enrolled=out$n_enrolled, n_overall=out$n_overall,
       n_trial_cases=out$n_trial_cases,
       inf_prev_15to24=out$inf_prev_15to24, inf_prev_25to34=out$inf_prev_25to34)
  }, future.seed=TRUE)
})

stoch_df_7a <- bind_rows(stoch_list_7a)

#' 3x2 panel plot: rows = n_enrolled_1 / n_tested_1, columns = country, colour = FOI structure
stoch_df_7a_long <- stoch_df_7a %>%
  mutate(country = factor(country, levels=countries_7a),
         n_enrolled_1 = n_enrolled / n_trial_cases,
         n_tested_1   = n_tested   / n_trial_cases) %>%
  select(country, foi_structure, slow_structure, sigma, rep, n_enrolled_1, n_tested_1) %>%
  pivot_longer(cols=c(n_enrolled_1, n_tested_1), names_to="metric", values_to="value") %>%
  mutate(metric = case_when(metric=="n_enrolled_1"~"Enrolled", metric=="n_tested_1"~"Tested"),
         metric = factor(metric, levels=c("Enrolled","Tested"))) %>%
  filter(!(country=="Kenya" & foi_structure %in% c("uniform_4"))) %>%  # filter out foi's that do not give plausible outputs
  filter(!(country=="India" & foi_structure %in% c("uniform_1"))) %>%  # filter out foi's that do not give plausible outputs
  filter(!(country=="South Africa" & foi_structure %in% c("uniform_5", "uniform_7")))  # filter out foi's that do not give plausible outputs

median_df_7a <- stoch_df_7a_long %>%
  group_by(country, foi_structure, slow_structure, sigma, metric) %>%
  summarise(value = median(value), .groups="drop")
#write.csv(median_df_7a, file="output/variedsite_results_full.csv", row.names=FALSE)

fig_7a <- ggplot(stoch_df_7a_long, aes(x=sigma, y=value, col=foi_structure, linetype=slow_structure)) +
  geom_point(size=0.4, alpha=0.1) +
  geom_line(data=median_df_7a, linewidth=0.7) +
  facet_grid(metric ~ country, scales="free_y") +
  scale_colour_brewer(palette="Set1") +
  theme_classic() +
  theme(strip.background=element_blank()) +
  labs(x="Test span (years)", y="Number (for 1 case)", col="Force of infection", linetype="p_f")
fig_7a
ggsave(fig_7a, file="figures/7a_varied_sites.pdf", width=7.29, height=4.51)

#' Summary table: infection prevalence at ages 20/30, ARTI, case incidence
#' Computed from stochastic output at sigma=80 (infection prevs, ARTI, cases)
summary_table_7a <- stoch_df_7a %>%
  filter(sigma == 80) %>%
  mutate(inf_prev_all = (n_overall - n_tested + n_enrolled) / n_overall,
    meanage      = ((pars_7a$maxage - pars_7a$minage) / 2) + pars_7a$minage,
    ARTI         = 1 - (1 - inf_prev_all)^(1 / meanage),
    cases_per100k = n_trial_cases / (n_overall * pars_7a$trial_length) * 100000) %>%
  group_by(country, foi_structure, slow_structure) %>%
  summarise(inf_prev_15to24 = median(inf_prev_15to24),
    inf_prev_25to34 = median(inf_prev_25to34),
    ARTI            = median(ARTI),
    cases_per100k   = median(cases_per100k),
    .groups = "drop")

# Literature for criteria
Dagnew_positivity_data <- read.csv("data/Dagnew_2026_IGRA_positivity_by_age_table_s5.csv") %>%
  select(country, site_no, age_group, pct_positive, ci_lo_positive, ci_hi_positive) %>%
  mutate(across(c(pct_positive, ci_lo_positive, ci_hi_positive), ~ .x / 100)) %>%  # convert % to proportion
  group_by(country, age_group) %>% summarise(min_positivity = min(ci_lo_positive), max_positivity = max(ci_hi_positive)) %>% ungroup()

dagnew_bounds_15to24 <- Dagnew_positivity_data %>%
  filter(country %in% countries_7a, age_group == "15-24") %>%
  select(country, min_positivity, max_positivity) %>%
  rename(min_15to24 = min_positivity, max_15to24 = max_positivity) %>%
  rows_update(tibble(country="India", min_15to24 = 0.098, max_15to24 = 0.158), by="country")  # adding india data from Selvaraju et al 2023

dagnew_bounds_25to34 <- Dagnew_positivity_data %>%
  filter(country %in% countries_7a, age_group == "25-34") %>%
  select(country, min_positivity, max_positivity) %>%
  rename(min_25to34 = min_positivity, max_25to34 = max_positivity) %>%
  rows_update(tibble(country="India", min_25to34 = 0.171, max_25to34 = 0.252), by="country")  # adding india data from Selvaraju et al 2023

country_thresholds_7a <- tibble(
  country       = c("South Africa", "Kenya",   "India"),
  arti_lo       = c(0.04,           0.016,      0.00),
  arti_hi       = c(0.06,           0.036,      0.02),
  cases_lo      = c(242,            109,        160),
  cases_hi      = c(571,            339,        218)
)

summary_table_7a <- summary_table_7a %>%
  left_join(dagnew_bounds_15to24, by="country") %>%
  left_join(dagnew_bounds_25to34, by="country") %>%
  left_join(country_thresholds_7a, by="country") %>%
  mutate(conditions_met =
    between(inf_prev_15to24, min_15to24, max_15to24) &  # might want to change India inf prev conditions to Selvaraju study
    between(inf_prev_25to34, min_25to34, max_25to34) &
    between(ARTI, arti_lo, arti_hi) &
    between(cases_per100k, cases_lo, cases_hi)) #%>%
  #select(country, foi_structure, slow_structure, inf_prev_15to24, inf_prev_25to34, ARTI, cases_per100k, conditions_met)

write.csv(summary_table_7a, file="output/variedsite_results.csv", row.names=FALSE)
```

## 7b. Non-test enrolment scenarios

Three scenarios using `sim_stoch_notest`: standard ages (15-49), younger ages (12-34), and household contacts (6-99, high instantaneous FOI if not already infected). No sigma dimension — one output per (scenario, country, FOI, rep).

```{r}
#| label: 7b_notest_scenarios
#| eval: FALSE

plan(multisession, workers=8)

countries_7b      <- c("South Africa", "India", "Kenya")
foi_structures_7b <- c("uniform_1", "uniform_2", "uniform_3", "uniform_4", "uniform_5")
p_slow_7b         <- extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-1997")
mu_slow_7b        <- define_mu_slow("0.003")
agedists_7b       <- setNames(lapply(countries_7b, function(c) extract_age_distribution(unwpp, c)), countries_7b)

# Build base parameter list
pars_7b <- pars_lit_igra
pars_7b$p_slow  <- p_slow_7b
pars_7b$mu_slow <- mu_slow_7b

# Flat grid: scenario x country x FOI x rep
scenarios_7b <- tibble(scenario = c("no test standard", "no test young", "no test household"),
                       minage   = c(15, 12, 6),
                       maxage   = c(49, 34, 99))

sim_grid_7b <- scenarios_7b %>%
  expand_grid(country = countries_7b, foi_structure = foi_structures_7b, rep = 1:25)

with_progress({
  p <- progressr::progressor(steps=nrow(sim_grid_7b))
  notest_list_7b <- future.apply::future_lapply(1:nrow(sim_grid_7b), function(i) {
    pars_i        <- pars_7b
    pars_i$rho    <- define_foi_by_age(sim_grid_7b$foi_structure[i])
    pars_i$minage <- sim_grid_7b$minage[i]
    pars_i$maxage <- sim_grid_7b$maxage[i]
    agedist_i     <- agedists_7b[[sim_grid_7b$country[i]]]
    out           <- sim_stoch_notest(pars_i, casetarget=50, agedist=agedist_i, 
                                      households = (sim_grid_7b$scenario[i] == "no test household"))
    p()
    tibble(
      scenario      = sim_grid_7b$scenario[i],
      country       = sim_grid_7b$country[i],
      foi_structure = sim_grid_7b$foi_structure[i],
      rep           = sim_grid_7b$rep[i],
      n_enrolled   = out$n_enrolled,
      n_fast        = out$n_fast,
      n_cases        = out$n_cases,
      n_overall     = out$n_overall,
      n_infected    = out$n_infected
    )
  }, future.seed=TRUE)
})

notest_df_7b <- bind_rows(notest_list_7b)

#' Summarise over reps: median + 10th/90th percentile
notest_summary_7b <- notest_df_7b %>%
  group_by(scenario, country, foi_structure) %>%
  summarise(
    n_enrolled_med = median(n_enrolled),
    n_enrolled_lo  = quantile(n_enrolled, 0.1),
    n_enrolled_hi  = quantile(n_enrolled, 0.9),
    n_overall_med   = median(n_overall),
    n_overall_lo    = quantile(n_overall, 0.1),
    n_overall_hi    = quantile(n_overall, 0.9),
    .groups = "drop"
  )
write.csv(notest_summary_7b, file="output/notest_results.csv", row.names=FALSE)

#' Plot: x = scenario, facet = country, line = foi
fig_7b <- notest_df_7b %>% 
  mutate(country  = factor(country, levels=countries_7b),
         scenario = factor(scenario, levels=c("no test standard", "no test young", "no test household")),
         foi_structure = factor(foi_structure, levels=foi_structures_7b)) %>%
  filter(!(country=="Kenya" & foi_structure %in% c("uniform_1", "uniform_5"))) %>%  # filter out foi's that do not give plausible outputs
  filter(!(country=="India" & foi_structure %in% c("uniform_4", "uniform_5"))) %>%  # filter out foi's that do not give plausible outputs
  filter(!(country=="South Africa" & foi_structure %in% c("uniform_1", "uniform_2", "uniform_3"))) %>% # filter out foi's that do not give plausible outputs
  ggplot(aes(x=scenario, y=n_enrolled, fill=foi_structure)) +
  geom_boxplot(coef=Inf) +
  scale_fill_brewer(palette = "Set1") +
  facet_wrap(~country, nrow=1) +
  theme_classic() +
  theme(strip.background=element_blank(), axis.text.x=element_text(angle=25, hjust=1)) +
  labs(x=NULL, y="Enrolled (for 50 cases)", fill="Force of infection")
fig_7b
ggsave(fig_7b, file="figures/7b_notest_scenarios.pdf", width=7.29, height=4.51)

# #' Epidemiological benchmarks
# combos_7b    <- sim_grid_7b %>% distinct(scenario, country, foi_structure, minage, maxage) 
# benchmarks_7b <- tibble()
# for (i in 1:nrow(combos_7b)) {
#   pars_i        <- pars_7b
#   pars_i$rho    <- define_foi_by_age(combos_7b$foi_structure[i])
#   pars_i$minage <- combos_7b$minage[i]
#   pars_i$maxage <- combos_7b$maxage[i]
# 
#   stoch_i  <- notest_df_7b %>%
#     filter(scenario==combos_7b$scenario[i], country==combos_7b$country[i], foi_structure==combos_7b$foi_structure[i]) %>%
#     select(rep, n_fast, n_cases, n_overall, n_infected)
# 
#   reps_i     <- unique(stoch_i$rep)
#   cases_vec  <- sapply(reps_i, function(r) calculate_case_incidence_at_time_of_recruitment_from_model(stoch_i, pars=pars_i, my_rep=r))
#   inf_vec1  <- sapply(reps_i, function(r) estimate_ARTI_from_model(stoch_i, pars=pars_i, my_rep=r, sig=80)["inf_prev_15to24"])
#   inf_vec2  <- sapply(reps_i, function(r) estimate_ARTI_from_model(stoch_i, pars=pars_i, my_rep=r, sig=80)["inf_prev_25to34"])
#   ARTI_vec   <- sapply(reps_i, function(r) estimate_ARTI_from_model(stoch_i, pars=pars_i, my_rep=r))
# 
#   benchmarks_7b <- bind_rows(benchmarks_7b, tibble(
#     scenario      = combos_7b$scenario[i],
#     country       = combos_7b$country[i],
#     foi_structure = combos_7b$foi_structure[i],
#     inf_prev_15to24 = median(inf_vec1),
#     inf_prev_25to34 = median(inf_vec2),
#     ARTI          = median(ARTI_vec),
#     cases_per100k = median(cases_vec)
#   ))
# }
# 
# benchmarks_7b <- benchmarks_7b %>%
#   mutate(conditions_met = TRUE)  # TODO: fill in conditions per scenario/country
# 
# write.csv(benchmarks_7b, file="output/notest_benchmarks.csv", row.names=FALSE)
```

## 8 Match analytic & stochastic (on non-age-varying params)
```{r}
#| label: match_approaches
#| eval: FALSE

# Set non-age-varying params TODO
pars_lit_uniform <- list(
	minage=15, # taken from above
	maxage=49, # taken from above
	rho=make_foi(6,6,6,6,6),
	p_slow=extract_probability_of_being_slow(progressor_type_by_age_studies, "uniform"),
	mu_slow=mu_slow_lit,  # from lit
	mu_fast=1.5,  # for most fast progressors progressing within two years, assuming exponential distribution
	p_revert=0,  # no reversion for analytic match
	mu_revert=0, # no reversion for analytic match
	sigma=100,  # IGRA test is essentially lifelong
	trial_length=3)

# Simulate the stochastic approach with lit params, over the duration of positivity sigma OR pre-load saved csv file
with_progress({
  stochastic_df_match <- sim_stoch_over_sigma(pars=pars_lit_uniform, sigmavec=c(0.5,1:80), casetarget=50, agedist=agedist, reps=25)
})

#' Simulate the analytical approach with lit params, over the duration of positivity sigma
analytical_df_match <- sim_analytic_over_sigma(pars=pars_lit_uniform, sigmavec=seq(from=0.5, to=80, by=0.1), casetarget=50, agedist=agedist)

#' Plot all results
fig_stochastic_analytic_match <- plot_stochastic_analytic(stochastic_df_match, analytical_df_match)
fig_stochastic_analytic_match
ggsave(fig_stochastic_analytic_match, file=paste0("figures/stochastic_analytic_match_",fig_name,".png"), width=7.29, height=4.51)
```