---
title: "run_analysis"
format: html
---

This Quarto Markdown file outlines a workflow for running all steps of the analysis. It is based on the example workflow in `code/trailsim_rote.R` and has been copied to a .qmd for ease of editing and commenting.

## 1. import functions and load packages
```{r}
#| label: setup
source('code/utils.R')
```

## 2. define parameter values
```{r}
#| label: define_params

pars_m72IIb_igra <- list(
	minage=18,
	maxage=49,
	rho=0.0275,
	p_slow=0.5,
	mu_slow=0.0001,
	mu_fast=1.5,
	sigma=100,
	ve=0.55,
	trial_length=3)
pars_m72IIb_tasa <- pars_m72IIb_igra
pars_m72IIb_tasa$sigma <- 2

pars_lit_igra <- list(
	minage=18,
	maxage=49,
	rho=0.0025,
	p_slow=0.95,
	mu_slow=0.0001,
	mu_fast=1.5,
	sigma=100,
	ve=0.55,
	trial_length=3)
pars_lit_tasa <- pars_lit_igra 
pars_lit_tasa$sigma <- 2
```

## 3. define an age distribution e.g. uniform
```{r}
#| label: define_age_dist

agedist <- rep(1, 80)
names(agedist) <- 1:80
agedist <- agedist/sum(agedist)
```

## 4. simulate trials under m72IIb conditions (analytical and stochastic approaches)
```{r}
#| label: simulate_with_m72IIb

#' Simulate the stochastic approach with m72IIb params, over the duration of positivity sigma OR pre-load saved csv file
# stochastic_df_m72IIb <- sim_stoch_over_sigma(pars=pars_m72IIb_igra, sigmavec=1:80, reps=25)
stochastic_df_m72IIb <- read_csv("output/stochastic_df_m72IIb.csv")

#' Simulate the analytical approach with m72IIb params, over the duration of positivity sigma
analytical_df_m72IIb <- sim_analytic_over_sigma(pars=pars_m72IIb_igra, sigmavec=seq(from=.5, to=80, by=0.01), agedist=agedist)
analytical_df_m72IIb %>% filter(sigma %in% c(0.5, 1, 1.5, 2, 5))

#' Plot all results
fig_stochastic_analytic_m72IIb <- plot_stochastic_analytic(stochastic_df_m72IIb, analytical_df_m72IIb, 
                                           cols=c("n_tested","n_recruited","n_fast","n_overall")) + 
	labs(title="M72/AS01E trial emulation")
fig_stochastic_analytic_m72IIb
ggsave(fig_stochastic_analytic_m72IIb, file="figures/stochastic_analytic_m72IIb.pdf", width=5, height=5/1.6)

fig_stochastic_analytic_log_m72IIb <- fig_stochastic_analytic_m72IIb + scale_y_continuous(trans="log10")
fig_stochastic_analytic_log_m72IIb
ggsave(fig_stochastic_analytic_log_m72IIb, file="figures/stochastic_analytic_log_m72IIb.pdf", width=5, height=5/1.6)

fig_screenslope_m72IIb <- plot_screenslope(analytical_df_m72IIb)
fig_screenslope_m72IIb


fig_stochastic_analytic_m72IIb_r21 <- plot_stochastic_analytic(stochastic_df_m72IIb, analytical_df_m72IIb, cols=c("n_tested","n_recruited")) + 
	labs(title="M72/AS01E trial emulation")
fig_stochastic_analytic_m72IIb_r21
ggsave(fig_stochastic_analytic_m72IIb_r21, file="figures/stochastic_analytic_m72IIb_r21.pdf", width=5, height=5/1.6)

fig_stochastic_analytic_m72IIb_r21_log <- plot_stochastic_analytic(stochastic_df_m72IIb, analytical_df_m72IIb, 
                                                   cols=c("n_tested","n_recruited")) + 
	labs(title="M72/AS01E trial emulation") + 
	scale_y_continuous(trans="log10")
fig_stochastic_analytic_m72IIb_r21_log
ggsave(fig_stochastic_analytic_m72IIb_r21_log, file="figures/stochastic_analytic_m72IIb_r21_log.pdf", width=5, height=5/1.6)
```

## 5. simulate trials under literature conditions (analytical and stochastic approaches)
```{r}
#| label: simulate_with_lit

#' Simulate the stochastic approach with lit params, over the duration of positivity sigma OR pre-load saved csv file
# stochastic_df_lit <- sim_stoch_over_sigma(pars=pars_lit_igra, sigmavec=1:80, reps=25)
stochastic_df_lit <- read_csv("output/stochastic_df_lit.csv")

#' Simulate the analytical approach with lit params, over the duration of positivity sigma
analytical_df_lit <- sim_analytic_over_sigma(pars=pars_lit_igra, sigmavec=seq(from=.5, to=80, by=0.01), agedist=agedist)
analytical_df_lit %>% filter(sigma %in% c(0.5, 1, 1.5, 2, 5))

#' Plot all results
fig_stochastic_analytic_lit <- plot_stochastic_analytic(stochastic_df_lit, analytical_df_lit, cols=c("n_tested","n_recruited","n_fast","n_overall")) + 
	labs(title="Literature parameters")
fig_stochastic_analytic_lit
ggsave(fig_stochastic_analytic_lit, file="figures/stochastic_analytic_lit.pdf", width=5, height=5/1.6)

fig_stochastic_analytic_log_lit <- fig_stochastic_analytic_lit + scale_y_continuous(trans="log10")
fig_stochastic_analytic_log_lit
ggsave(fig_stochastic_analytic_log_lit, file="figures/stochastic_analytic_log_lit.pdf", width=5, height=5/1.6)

fig_screenslope_lit <- plot_screenslope(analytical_df_lit)
fig_screenslope_lit
```

Possible extensions to the above basic workflow are to include custom age distribution in `sim_trial`(?) and custom fast targets for `sim_stoch_over_sigma` and `sim_analytic_over_sigma`.