---
title: "Age-structure diagnostics"
format: html
editor: 
  markdown: 
    wrap: 72
---

Six diagnostics to investigate why model case incidence (30--80/100k)
falls short of the 100--250/100k South Africa target, and to understand
the contribution of each age-structure addition made in February--March
2026. Written by Claude and checked by human.

**Note on analytic vs stochastic:** The analytic functions
(`sim_analytic_over_sigma`) use `rho[age]` as a per-age scalar
approximation, so they do not correctly propagate age-varying FOI
through a person's full infection history. The stochastic approach
(`sim_stoch`) handles this correctly via the survival PMF. Each
diagnostic therefore includes both: analytical (fast; always runs) and
stochastic (slower; `eval: FALSE` by default — set to `TRUE` to run).

## 0. Setup

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(readxl)
library(future.apply)
library(progressr)
library(zoo)
source('code/utils.R')
plan(multisession, workers=8)

unwpp <- read_excel("data/WPP2024_POP_F01_1_POPULATION_SINGLE_AGE_BOTH_SEXES.xlsx", skip = 16) %>%
  filter(Year == 2023 & Type == "Country/Area") %>% rename(country="Region, subregion, country or area *") %>%
  mutate(across(all_of(as.character(0:99)), ~ as.numeric(.x) * 1000)) %>%
  select(country, all_of(as.character(0:99))) %>% arrange(country)

progressor_type_by_age_studies <- read.csv(file="data/progressor-type-by-age-estimates-from-literature.csv") %>%
  numericize(age) %>% impute_probability_of_being_slow()

agedist_uniform <- extract_age_distribution(unwpp, "uniform")
agedist_ZAF     <- extract_age_distribution(unwpp, "South Africa")
prog_uniform     <- extract_probability_of_being_slow(progressor_type_by_age_studies, "uniform")
prog_vynn        <- extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-1997")

foi_names <- c("uniform4", "uniform6", "uniform10", "5888", "5102030", "5204050", "5255070", "33510", "151015")
foi_list  <- setNames(lapply(foi_names, define_foi_by_age), foi_names)
```

------------------------------------------------------------------------

## Diagnostic 1: FOI inputs and infection timing

**Question:** Where are infections being drawn relative to the eligible
age window? If the FOI is high, most infections occur in childhood —
meaning 18--49 year olds at trial entry mostly have *old* infections
(slow progressors), not recent ones (fast progressors). This would
suppress both recruitment efficiency and case incidence.

*No simulation required: these are direct properties of the FOI inputs.*

```{r}
#| label: diag1_survival

surv_df <- map_dfr(names(foi_list), function(nm) {
  sv <- compute_survival_fn(foi_list[[nm]])
  bind_rows(
    tibble(foi_structure=nm, type="survival_fn",  age=1:100,  value=sv$survival_fn),
    tibble(foi_structure=nm, type="survival_pmf", age=0:99,   value=sv$survival_pmf[1:100])
  )
})

lit_d1a <- tibble(
  source = c(rep("Wood", 3), 
             rep("Ncayiyana (latent)", 3), 
             rep("Houben (AFRO)", 4)),
  age = c(24, 34, 44,
          20, 30, 40,
          20, 40, 80, 90),
  survival = 1 - c(0.26, 0.31, 0.45,
                   0.67, 0.77, 0.69,
                   0.15, 0.35, 0.65, 0.70))
fig_d1a <- surv_df %>%
  filter(type=="survival_fn") %>%
  ggplot(aes(x=age, y=value, col=foi_structure)) +
  geom_line() +
  geom_point(data=lit_d1a, aes(x=age, y=survival, shape=source), color="black", size=3, inherit.aes=FALSE) +
  scale_shape_manual(values=c("Wood"=16, "Ncayiyana (latent)"=17, "Houben (AFRO)"=15)) +
  annotate("rect", xmin=18, xmax=49, ymin=-Inf, ymax=Inf, alpha=0.1, fill="steelblue") +
  theme_classic() +
  labs(x="Age", y="P(not yet infected by age a)",
       title="Diagnostic 1a: Survival function by FOI scenario",
       subtitle="Blue band = trial-eligible ages 18–49",
       col="FOI scenario", shape="Literature (prevalence by age)")
fig_d1a

fig_d1b <- surv_df %>%
  filter(type=="survival_pmf") %>%
  ggplot(aes(x=age, y=value, col=foi_structure)) +
  geom_line() +
  annotate("rect", xmin=18, xmax=49, ymin=-Inf, ymax=Inf, alpha=0.1, fill="steelblue") +
  theme_classic() +
  labs(x="Age at first infection", y="Probability",
       title="Diagnostic 1b: Age distribution of first infection",
       subtitle="Blue band = trial-eligible ages 18–49", col="FOI scenario")
fig_d1b

map_dfr(names(foi_list), function(nm) {
  sv <- compute_survival_fn(foi_list[[nm]])
  pmf <- sv$survival_pmf
  tibble(
    foi_structure = nm,
    pct_before_18 = round(sum(pmf[1:18])  * 100, 1),
    pct_eligible  = round(sum(pmf[19:50]) * 100, 1),
    pct_after_49  = round(sum(pmf[51:100])* 100, 1),
    pct_never     = round(pmf[101]        * 100, 1)
  )
}) %>% knitr::kable(
  col.names = c("FOI scenario", "% infected <18y", "% infected 18–49y", "% infected 50+y", "% never infected"),
  caption   = "Diagnostic 1c: Where in the life-course do infections land?")
```

**Interpretation guide:** A high `pct_before_18` means most people
entering the trial window already have old LTBI and are nearly all slow
progressors. `n_fast/n_overall` will be tiny and case incidence
estimates will be low.

------------------------------------------------------------------------

## Diagnostic 2: Population composition at trial entry

**Question:** Of everyone drawn from the population (ages 18--49), what
fraction falls into each category — uninfected, LTBI (old/TASA-), LTBI
(recent/TASA+), symptomatic? Only the *LTBI (recent)* group are
recruited by a TASA-type test (sigma=2).

### 2a. Analytical — per-age composition (uniform FOI)

*Analytical functions use rho\[age\] as a scalar; valid for uniform FOI
only.*

```{r}
#| label: diag2a_analytic

uniform_foi_names <- c("uniform4", "uniform6", "uniform10")
minage_d2 <- 18; maxage_d2 <- 49

comp_df <- map_dfr(uniform_foi_names, function(nm) {
  foi <- foi_list[[nm]]
  map_dfr(minage_d2:maxage_d2, function(a) {
    p_asymp     <- p_asymp_given_age(age=a, p_slow=prog_uniform, foi=foi,
                                     prograte_slow=0.0001, prograte_fast=1.5)
    p_uninf     <- exp(-foi[[as.character(a)]] * a)
    p_inf_asymp <- p_asymp - p_uninf
    p_symp      <- 1 - p_asymp
    p_tasa      <- p_inf_and_type_and_asymp_given_age(
                     "slow", a, sigma=2, p_slow=prog_uniform, foi=foi,
                     prograte_slow=0.0001, prograte_fast=1.5) +
                   p_inf_and_type_and_asymp_given_age(
                     "fast", a, sigma=2, p_slow=prog_uniform, foi=foi,
                     prograte_slow=0.0001, prograte_fast=1.5)
    p_ltbi_old  <- p_inf_asymp - p_tasa
    tibble(foi_structure=nm, age=a,
           Symptomatic=p_symp, `LTBI (old, TASA-)`=p_ltbi_old,
           `LTBI (recent, TASA+)`=p_tasa, Uninfected=p_uninf)
  })
})

comp_df %>%
  pivot_longer(c(Symptomatic, `LTBI (old, TASA-)`, `LTBI (recent, TASA+)`, Uninfected),
               names_to="category") %>%
  mutate(category = factor(category,
    levels=c("Uninfected","LTBI (old, TASA-)","LTBI (recent, TASA+)","Symptomatic"))) %>%
  ggplot(aes(x=age, y=value, fill=category)) +
  geom_area() +
  facet_wrap(~foi_structure) +
  scale_fill_manual(values=c("Uninfected"="lightgrey","LTBI (old, TASA-)"="steelblue",
                              "LTBI (recent, TASA+)"="orange","Symptomatic"="red")) +
  theme_classic() +
  labs(x="Age", y="Probability", fill=NULL,
       title="Diagnostic 2a: Population composition at trial entry (analytical, uniform FOI, uniform p_slow)")
```

### 2b. Stochastic — aggregate composition (any FOI)

From a stochastic run the fractions can be recovered as:

\- P(symptomatic) ≈ `(n_overall - n_tested) / n_overall` *(symptomatics
fail the pre-test symptom screen and are never IGRA-tested)*

\- P(asymptomatic, IGRA+) ≈ `n_recruited / n_overall` at sigma=80
*(note: symptomatics would also be IGRA+ but are excluded before
testing)*

\- P(asymptomatic, TASA+) ≈ `n_recruited / n_overall` at sigma=2

\- P(LTBI old, asymptomatic) ≈ P(asymptomatic IGRA+) − P(asymptomatic
TASA+)

\- P(uninfected, asymptomatic) ≈ `(n_tested - n_recruited) / n_overall`
at sigma=80

These are aggregate figures across ages 18--49, not per-age. Running
this stochastically for all FOI scenarios (including age-varying) is the
main value of 2b — the analytical in 2a is only valid for uniform FOI,
so the stochastic runs for "5888", "5102030" etc. are the only way to
get composition estimates for those scenarios.

```{r}
#| label: diag2b_stoch
#| eval: TRUE  # set to TRUE to run (~2 minutes)

pars_base_d2 <- list(minage=18, maxage=49, mu_slow=0.0001, mu_fast=1.5, p_slow=prog_uniform)

# Run at sigma=2 and sigma=80 for ALL FOI scenarios (including age-varying)
stoch_comp_df <- map_dfr(foi_names, function(nm) {
  map_dfr(c(2, 80), function(sig) {
    pars <- c(pars_base_d2, list(rho=foi_list[[nm]], sigma=sig))
    run  <- sim_stoch(pars=pars, fasttarget=50, agedist=agedist_ZAF)
    tibble(foi_structure=nm, sigma=sig,
           sym_frac     = (run$n_overall - run$n_tested)   / run$n_overall,
           test_neg_frac= (run$n_tested  - run$n_recruited) / run$n_overall,
           # NB: test_neg_frac = P(uninfected) at sigma=80, but
           #     test_neg_frac = P(uninfected) + P(old LTBI) at sigma=2 —
           #     only the sigma=80 value is used as "Uninfected" below.
           test_pos_frac= run$n_recruited                  / run$n_overall)
           # NB: test_pos_frac = P(any LTBI, asymptomatic) at sigma=80, but
           #     test_pos_frac = P(recent LTBI, asymptomatic) at sigma=2 —
           #     both values are used below (as ltbi_sigma80 and ltbi_sigma2).
  })
})

# Derive per-scenario composition (TASA+ from sigma=2 run; rest from sigma=80 run)
stoch_comp_wide <- stoch_comp_df %>%
  select(foi_structure, sigma, test_pos_frac) %>%
  pivot_wider(names_from=sigma, values_from=test_pos_frac, names_prefix="test_pos_sigma") %>%
  left_join(stoch_comp_df %>% filter(sigma==80) %>%
              select(foi_structure, sym_frac, test_neg_frac), by="foi_structure") %>%
  mutate(`LTBI (recent, TASA+)` = test_pos_sigma2,
         `LTBI (old, TASA-)`    = test_pos_sigma80 - test_pos_sigma2,
         Uninfected              = test_neg_frac,  # valid only at sigma=80
         Symptomatic             = sym_frac,
         approach                = "Stochastic") %>%
  select(foi_structure, approach, Symptomatic, `LTBI (old, TASA-)`, `LTBI (recent, TASA+)`, Uninfected)

# Analytical aggregates for uniform scenarios only (weighted by agedist over eligible ages)
analytic_comp_wide <- comp_df %>%
  mutate(wt = agedist_ZAF[as.character(age)]) %>%
  group_by(foi_structure) %>%
  summarise(across(c(Symptomatic, `LTBI (old, TASA-)`, `LTBI (recent, TASA+)`, Uninfected),
                   ~weighted.mean(.x, wt))) %>%
  mutate(approach="Analytic")

# Combined plot: stochastic for all scenarios; analytical overlay for uniform scenarios only
bind_rows(
  stoch_comp_wide,
  analytic_comp_wide  # only covers uniform_foi_names, so won't appear for age-varying rows
) %>%
  pivot_longer(c(Symptomatic, `LTBI (old, TASA-)`, `LTBI (recent, TASA+)`, Uninfected),
               names_to="category") %>%
  mutate(category = factor(category,
    levels=c("Uninfected","LTBI (old, TASA-)","LTBI (recent, TASA+)","Symptomatic"))) %>%
  ggplot(aes(x=approach, y=value, fill=category)) +
  geom_col() +
  facet_wrap(~foi_structure) +
  scale_fill_manual(values=c("Uninfected"="lightgrey","LTBI (old, TASA-)"="steelblue",
                              "LTBI (recent, TASA+)"="orange","Symptomatic"="red")) +
  theme_classic() +
  theme(axis.text.x=element_text(angle=20, hjust=1)) +
  labs(x=NULL, y="Proportion of population", fill=NULL,
       title="Diagnostic 2b: Population composition — stochastic + analytical")
```

------------------------------------------------------------------------

## Diagnostic 3: Stepwise age-structure effects

**Question:** Which of the three age-structure additions — (B) South
Africa population, (C) Vynnycky age-varying p_slow, (D) age-varying FOI
— changed model outputs the most?

Four scenarios are built up one element at a time from the uniform
baseline. The stochastic results are most important here: scenario D
uses age-varying FOI which the analytical method only approximates.

```{r}
#| label: diag3_setup

scenarios_d3 <- list(
  `A: uniform all`    = list(agedist=agedist_uniform, foi=define_foi_by_age("uniform4"), p_slow=prog_uniform),
  `B: +SA pop`        = list(agedist=agedist_ZAF,     foi=define_foi_by_age("uniform4"), p_slow=prog_uniform),
  `C: +Vynnycky slow` = list(agedist=agedist_ZAF,     foi=define_foi_by_age("uniform4"), p_slow=prog_vynn),
  `D: +age-vary FOI`  = list(agedist=agedist_ZAF,     foi=define_foi_by_age("5102030"),  p_slow=prog_vynn)
)
pars_base_d3 <- list(minage=18, maxage=49, mu_slow=0.0001, mu_fast=1.5, ve=0.55, trial_length=3)
stoch_d3_df  <- NULL  # populated by stochastic chunk below if run
```

### 3a. Analytical

```{r}
#| label: diag3a_analytic

analytic_d3_df <- map_dfr(names(scenarios_d3), function(nm) {
  sc   <- scenarios_d3[[nm]]
  pars <- c(pars_base_d3, list(rho=sc$foi, p_slow=sc$p_slow))
  sim_analytic_over_sigma(pars=pars, sigmavec=seq(0.5, 80, by=0.5),
                          fasttarget=50, agedist=sc$agedist) %>%
    mutate(scenario=nm, approach="Analytic")
})
```

### 3b. Stochastic

```{r}
#| label: diag3b_stoch
#| eval: TRUE  # set to TRUE to run (~5 minutes with 8 cores)

sigmavec_d3 <- c(1, 2, 5, 10, 20, 40, 80)
with_progress({
  stoch_d3_df <- map_dfr(names(scenarios_d3), function(nm) {
    sc   <- scenarios_d3[[nm]]
    pars <- c(pars_base_d3, list(rho=sc$foi, p_slow=sc$p_slow))
    sim_stoch_over_sigma(pars=pars, sigmavec=sigmavec_d3,
                         fasttarget=50, agedist=sc$agedist, reps=10) %>%
      mutate(scenario=nm, approach="Stochastic")
  })
})
```

### 3c. Combined plots

```{r}
#| label: diag3c_plots

# n_recruited vs sigma
fig_d3_recruited <- ggplot() +
  geom_line(data=analytic_d3_df, aes(x=sigma, y=n_recruited, col=scenario)) +
  { if (!is.null(stoch_d3_df))
      geom_point(data=stoch_d3_df, aes(x=sigma, y=n_recruited, col=scenario),
                 size=0.8, alpha=0.4) } +
  geom_vline(xintercept=c(2, 80), linetype="dashed", alpha=0.4) +
  theme_classic() +
  labs(x="Test span sigma (years)", y="N recruited (to achieve 50 fasts)",
       title="Diagnostic 3: Stepwise age-structure effects on recruitment curve",
       subtitle="Lines = analytical; points = stochastic (where run)", col=NULL)
fig_d3_recruited

# n_overall vs sigma
fig_d3_overall <- ggplot() +
  geom_line(data=analytic_d3_df, aes(x=sigma, y=n_overall, col=scenario)) +
  { if (!is.null(stoch_d3_df))
      geom_point(data=stoch_d3_df, aes(x=sigma, y=n_overall, col=scenario),
                 size=0.8, alpha=0.4) } +
  geom_vline(xintercept=c(2, 80), linetype="dashed", alpha=0.4) +
  theme_classic() +
  labs(x="Test span sigma (years)", y="N overall",
       title="Diagnostic 3: Effect of age structure on total population drawn",
       subtitle="Lines = analytical; points = stochastic (where run)", col=NULL)
fig_d3_overall

# Summary table at sigma=2 and sigma=80 (analytical)
analytic_d3_df %>%
  filter(sigma %in% c(2, 80)) %>%
  mutate(pct_fast           = round(100 * n_fast / n_recruited, 1),
         screens_per_recruit = round(n_tested / n_recruited, 1)) %>%
  select(scenario, sigma, n_overall, n_tested, n_recruited, pct_fast, screens_per_recruit) %>%
  arrange(sigma, scenario) %>%
  knitr::kable(
    col.names = c("Scenario", "sigma", "N overall", "N screened", "N recruited",
                  "% fast among recruited", "Screens per recruit"),
    caption   = "Diagnostic 3: Analytical outputs at sigma=2 (TASA) and sigma=80 (IGRA)")

# Summary table at sigma=2 and sigma=80 (stochastic, if run)
if (!is.null(stoch_d3_df)) {
  stoch_d3_df %>%
    filter(sigma %in% c(2, 80)) %>%
    mutate(pct_fast           = round(100 * n_fast / n_recruited, 1),
           screens_per_recruit = round(n_tested / n_recruited, 1)) %>%
    select(scenario, sigma, n_overall, n_tested, n_recruited, pct_fast, screens_per_recruit) %>%
    arrange(sigma, scenario) %>%
    knitr::kable(
      col.names = c("Scenario", "sigma", "N overall", "N screened", "N recruited",
                    "% fast among recruited", "Screens per recruit"),
      caption   = "Diagnostic 3: Stochastic outputs at sigma=2 (TASA) and sigma=80 (IGRA)")
}
```

**Interpretation guide:** Compare rows within the same sigma to isolate
each addition. A→B is population age structure; B→C is p_slow by age;
C→D is FOI by age. Stochastic estimates for scenario D are the more
reliable figures.

------------------------------------------------------------------------

## Diagnostic 4: Case incidence decomposition — fast vs slow contribution

**Question:** Is the gap with the 100--250/100k target driven by (a) too
few fast progressors, (b) too low a reactivation rate (mu_slow), or (c)
both?

The case incidence formula is:
`incidence = (n_fast + n_slow * mu_slow * trial_length) / (n_overall * trial_length)`

The analytical result uses the rho\[age\] approximation for age-varying
FOI; the stochastic result is correct for all scenarios.

```{r}
#| label: diag4_setup

pars_base_d4 <- list(minage=18, maxage=49, mu_slow=0.0001, mu_fast=1.5,
                     ve=0.55, trial_length=3, p_slow=prog_vynn)
stoch_d4_df  <- NULL  # populated by stochastic chunk below if run
```

### 4a. Analytical

```{r}
#| label: diag4a_analytic

analytic_d4_df <- map_dfr(names(foi_list), function(nm) {
  pars <- c(pars_base_d4, list(rho=foi_list[[nm]]))
  res  <- sim_analytic_over_sigma(pars=pars, sigmavec=80, fasttarget=50, agedist=agedist_ZAF)
  tibble(foi_structure  = nm,
         n_overall      = round(res$n_overall),
         n_fast         = round(res$n_fast),
         n_slow         = round(res$n_slow),
         fast_per_100k  = round((res$n_fast / res$n_overall) / pars$trial_length * 1e5, 2),
         slow_per_100k  = round(res$n_slow * pars$mu_slow / res$n_overall * 1e5, 2),
         total_per_100k = round(((res$n_fast / res$n_overall) / pars$trial_length +
                                  res$n_slow * pars$mu_slow / res$n_overall) * 1e5, 2),
         approach       = "Analytic")
})

analytic_d4_df %>%
  select(-approach) %>%
  mutate(pct_fast = round(100 * fast_per_100k / total_per_100k, 1)) %>%
  knitr::kable(
    col.names = c("FOI", "N overall", "N fast", "N slow",
                  "Fast (/100k/y)", "Slow (/100k/y)", "Total (/100k/y)", "% from fast"),
    caption   = "Diagnostic 4a: Analytic case incidence decomposition (sigma=80, Vynn p_slow, SA pop)")
```

### 4b. Stochastic

```{r}
#| label: diag4b_stoch
#| eval: FALSE  # set to TRUE to run (~3 minutes)

with_progress({
  stoch_d4_df <- map_dfr(names(foi_list), function(nm) {
    pars <- c(pars_base_d4, list(rho=foi_list[[nm]], sigma=80))
    sim_stoch_over_sigma(pars=pars, sigmavec=80, fasttarget=50,
                         agedist=agedist_ZAF, reps=10) %>%
      mutate(foi_structure = nm,
             fast_per_100k = (n_fast / n_overall) / pars$trial_length * 1e5,
             slow_per_100k = n_slow * pars$mu_slow / n_overall * 1e5,
             total_per_100k= fast_per_100k + slow_per_100k,
             approach      = "Stochastic")
  })
})
```

### 4c. Combined plot

```{r}
#| label: diag4c_plot

# Build a long-format dataset for the stacked bars (analytical)
analytic_d4_long <- analytic_d4_df %>%
  select(foi_structure, fast_per_100k, slow_per_100k) %>%
  pivot_longer(-foi_structure, names_to="source", values_to="cases_per_100k") %>%
  mutate(source = case_match(source,
    "fast_per_100k" ~ "Fast progressors",
    "slow_per_100k" ~ "Slow progressors"))

fig_d4 <- ggplot() +
  geom_col(data=analytic_d4_long,
           aes(x=foi_structure, y=cases_per_100k, fill=source), alpha=0.85) +
  { if (!is.null(stoch_d4_df))
      geom_point(data=stoch_d4_df,
                 aes(x=foi_structure, y=total_per_100k), shape=4, size=2,
                 colour="black", position=position_jitter(width=0.1)) } +
  geom_hline(yintercept=c(100, 250), linetype="dashed", col="darkred", linewidth=0.8) +
  annotate("rect", xmin=-Inf, xmax=Inf, ymin=100, ymax=250, alpha=0.07, fill="darkred") +
  annotate("text", x=0.6, y=100, label=" 100/100k", hjust=0, vjust=-0.4, size=3, col="darkred") +
  annotate("text", x=0.6, y=250, label=" 250/100k", hjust=0, vjust=-0.4, size=3, col="darkred") +
  theme_classic() +
  theme(axis.text.x=element_text(angle=30, hjust=1)) +
  labs(x="FOI scenario", y="Cases per 100k per year",
       title="Diagnostic 4: Case incidence — fast vs slow (bars=analytic, x=stochastic)",
       fill=NULL)
fig_d4
```

**Interpretation guide:** If fast progressors dominate and total is
still far from target, the bottleneck is the rarity of recent infections
(see Diagnostic 1). If slow progressors are negligible, Diagnostic 5
explores whether mu_slow is the missing lever.

------------------------------------------------------------------------

## Diagnostic 5: Sensitivity to mu_slow — what reactivation rate closes the gap?

**Question:** mu_slow is currently 0.0001/year. How large would it need
to be to reach 100--250 cases/100k? This reveals whether mu_slow alone
could close the gap.

```{r}
#| label: diag5_setup

mu_slow_vec  <- c(0.0001, 0.0003, 0.001, 0.003, 0.01, 0.03, 0.1)
foi_for_d5   <- c("uniform4", "uniform6", "5102030")
stoch_d5_df  <- NULL  # populated by stochastic chunk below if run
```

### 5a. Analytical

```{r}
#| label: diag5a_analytic

analytic_d5_df <- map_dfr(foi_for_d5, function(nm) {
  map_dfr(mu_slow_vec, function(mu_s) {
    pars <- list(minage=18, maxage=49, rho=foi_list[[nm]], p_slow=prog_vynn,
                 mu_slow=mu_s, mu_fast=1.5, ve=0.55, trial_length=3)
    res  <- sim_analytic_over_sigma(pars=pars, sigmavec=80, fasttarget=50, agedist=agedist_ZAF)
    tibble(foi_structure=nm, mu_slow=mu_s, approach="Analytical",
           fast = (res$n_fast  / res$n_overall) / pars$trial_length * 1e5,
           slow = res$n_slow * mu_s / res$n_overall * 1e5,
           total= ((res$n_fast / res$n_overall) / pars$trial_length +
                    res$n_slow * mu_s / res$n_overall) * 1e5)
  })
})
```

### 5b. Stochastic

```{r}
#| label: diag5b_stoch
#| eval: FALSE  # set to TRUE to run (~4 minutes)

with_progress({
  stoch_d5_df <- map_dfr(foi_for_d5, function(nm) {
    map_dfr(mu_slow_vec, function(mu_s) {
      pars <- list(minage=18, maxage=49, rho=foi_list[[nm]], p_slow=prog_vynn,
                   mu_slow=mu_s, mu_fast=1.5, ve=0.55, trial_length=3, sigma=80)
      sim_stoch_over_sigma(pars=pars, sigmavec=80, fasttarget=50,
                           agedist=agedist_ZAF, reps=5) %>%
        mutate(foi_structure=nm, mu_slow=mu_s, approach="Stochastic",
               fast = (n_fast / n_overall) / pars$trial_length * 1e5,
               slow = n_slow * mu_s / n_overall * 1e5,
               total= fast + slow)
    })
  })
})
```

### 5c. Combined plot

```{r}
#| label: diag5c_plot

fig_d5 <- ggplot() +
  geom_line(data=analytic_d5_df,
            aes(x=mu_slow, y=total, col=foi_structure)) +
  { if (!is.null(stoch_d5_df))
      geom_point(data=stoch_d5_df,
                 aes(x=mu_slow, y=total, col=foi_structure), size=1, alpha=0.5) } +
  geom_hline(yintercept=c(100, 250), linetype="dashed", col="darkred") +
  annotate("rect", xmin=-Inf, xmax=Inf, ymin=100, ymax=250, alpha=0.07, fill="darkred") +
  geom_vline(xintercept=0.0001, linetype="dotted", col="grey40") +
  annotate("text", x=0.00012, y=5, label="current mu_slow", hjust=0, size=3, col="grey40") +
  scale_x_log10(labels=scales::label_scientific()) +
  theme_classic() +
  labs(x="mu_slow — annual reactivation rate (log scale)", y="Cases per 100k per year",
       title="Diagnostic 5: How high must mu_slow be to reach target case incidence?",
       subtitle="Lines = analytic; points = stochastic (where run)",
       col="FOI scenario")
fig_d5

# Required mu_slow to hit targets (analytical)
analytic_d5_df %>%
  group_by(foi_structure) %>%
  summarise(
    mu_slow_for_100k = approx(total, mu_slow, xout=100)$y,
    mu_slow_for_250k = approx(total, mu_slow, xout=250)$y
  ) %>%
  mutate(across(where(is.numeric), ~round(.x, 5))) %>%
  knitr::kable(
    col.names = c("FOI scenario", "mu_slow needed for 100/100k", "mu_slow needed for 250/100k"),
    caption   = "Diagnostic 5: Required reactivation rate to hit case incidence targets")
```

**Interpretation guide:** If the required mu_slow far exceeds published
LTBI reactivation estimates, the gap cannot be
closed by reactivation alone and points to missing components (e.g. HIV
co-infection, re-infection, or a more complex progression model).

------------------------------------------------------------------------

## Diagnostic 6: Time since infection at enrollment — who are the recruits?

**Question:** For a stochastic run (sigma=80), what is the distribution
of time-since-infection among recruited participants? If most recruits
were infected decades ago, this confirms why `n_fast/n_recruited` is
small and why modelled incidence is low.

*This diagnostic is entirely stochastic — no analytical version exists.*

```{r}
#| label: diag6_stoch

pars_d6 <- list(minage=18, maxage=49, rho=foi_list[["uniform4"]], p_slow=prog_vynn,
                mu_slow=0.0001, mu_fast=1.5, sigma=80, ve=0.55, trial_length=3)

set.seed(42)
stoch_d6  <- sim_stoch(pars=pars_d6, fasttarget=200, agedist=agedist_ZAF)
rec_d6    <- stoch_d6$recruited_df %>%
  mutate(time_since_inf = age - tinf)

cat(sprintf("N recruited: %d   N overall: %d   Fast: %d   Slow: %d\n",
            stoch_d6$n_recruited, stoch_d6$n_overall,
            stoch_d6$n_fast, stoch_d6$n_slow))
cat(sprintf("Fast fraction among recruited: %.1f%%\n",
            100 * stoch_d6$n_fast / stoch_d6$n_recruited))

fig_d6a <- rec_d6 %>%
  ggplot(aes(x=time_since_inf, fill=progressor_type)) +
  geom_histogram(bins=40, position="stack") +
  scale_fill_manual(values=c("fast"="tomato","slow"="steelblue")) +
  geom_vline(xintercept=2, linetype="dashed") +
  annotate("text", x=2.3, y=Inf, label="TASA\nwindow", vjust=1.5, hjust=0, size=3) +
  theme_classic() +
  labs(x="Time since infection at enrollment (years)", y="Count",
       title="Diagnostic 6a: Time since infection at enrollment (sigma=80, uniform4 FOI, Vynnycky p_slow)",
       subtitle="Left of dashed line = would be TASA-recruited; right = IGRA-only",
       fill="Progressor type")
fig_d6a

fig_d6b <- rec_d6 %>%
  ggplot(aes(x=tinf, fill=progressor_type)) +
  geom_histogram(bins=40, position="stack") +
  scale_fill_manual(values=c("fast"="tomato","slow"="steelblue")) +
  annotate("rect", xmin=18, xmax=49, ymin=-Inf, ymax=Inf, alpha=0.15, fill="orange") +
  annotate("text", x=33, y=Inf, label="Infected during\neligible ages", vjust=1.5, size=3) +
  theme_classic() +
  labs(x="Age at infection (tinf)", y="Count",
       title="Diagnostic 6b: Age at first infection for recruited participants",
       subtitle="Orange = infected during eligible window 18–49. Most infections are pre-18.",
       fill="Progressor type")
fig_d6b

rec_d6 %>%
  mutate(recency = if_else(time_since_inf <= 2, "Recent (<= 2y, TASA+)", "Old (> 2y, TASA-)")) %>%
  count(progressor_type, recency) %>%
  mutate(pct = round(100 * n / sum(n), 1)) %>%
  knitr::kable(caption="Diagnostic 6c: Composition of recruited cohort by recency and progressor type")
```

**Interpretation guide:** Fast progressors cluster near zero
time-since-infection (they progress quickly so must have been infected
very recently to still be asymptomatic). Slow progressors span a wide
range of old infections. The ratio of fast-to-total directly determines
`n_fast/n_overall` and hence the ceiling on modelled case incidence.