---
title: "run_analysis"
format: html
---
This Quarto Markdown file outlines a workflow for running all steps of the analysis. It is based on the example workflow in `code/trialsim_rote.R`.

## 1. Setup

```{r}
#| label: setup

library(tidyverse)
library(readxl)
library(future.apply)
library(progressr)
library(countrycode)
library(zoo)
source('code/utils.R')
n_workers <- 8  # shared worker count for all plan(multisession, ...) calls below
plan(multisession, workers=n_workers)  # use multiple cores for speed

# Extract and pre-process data sets
unwpp <- read_excel("data/WPP2024_POP_F01_1_POPULATION_SINGLE_AGE_BOTH_SEXES.xlsx", skip = 16) %>%  # populations from UNWPP
  filter(Year == 2023 & Type == "Country/Area") %>% rename(country="Region, subregion, country or area *") %>%
  mutate(across(all_of(as.character(0:99)), ~ as.numeric(.x) * 1000)) %>% select(country, all_of(as.character(0:99))) %>% arrange(country)
global_TB_inc_report <- read.csv(file = "data/TB_burden_age_sex_2026-02-20.csv") %>%  # number of cases per year, 2024 from WHO
  filter(sex=="a" & risk_factor=="all") %>% select(country, year, age_group, best, lo, hi) %>% rename(cases=best, cases_lo=lo, cases_hi=hi) %>%
  filter(age_group %in% c("0-4","5-9","10-14","15-19","20-24","25-34","35-44","45-54","55-64","65plus")) %>%  # filter duplicate age groups
  mutate(pop = unlist(unname(mapply(get_pop, age_group, country, MoreArgs = list(unwpp = unwpp))))) %>%  # append population
  mutate(inc = cases/pop, inc_lo=cases_lo/pop, inc_hi=cases_hi/pop) %>%  # compute incidence
  select(country, year, age_group, inc, inc_lo, inc_hi) %>% numericize(age_group) %>% arrange(country, age_group)  # expand to single-year ages
progressor_type_by_age_studies <- read.csv(file="data/progressor-type-by-age-estimates-from-literature.csv") %>%
  numericize(age) %>% impute_probability_of_being_slow()

# Estimate reversion rate
Dagnew_reversion_data <- left_join(read.csv("data/Dagnew_2026_IGRA_status_at_day_1_table_s4.csv"), read.csv("data/Dagnew_2026_IGRA_reversion_conversion_table_s6.csv"), by = c("country", "site_no" = "site_number")) %>%  # reversion data from Dagnew et al.
  select(country, site_no, N_D1, n_positive_D1, N_M12, reversion_n) %>%
  group_by(country) %>% summarise(across(c(N_D1, n_positive_D1, N_M12, reversion_n), sum)) %>%  # summing across sites
  mutate(prob_of_reversion_once_infected = reversion_n / (n_positive_D1*N_M12/N_D1))  # probability of reverting once infected = no of reversions / approx no of initial positives who completed the study

# Infection prevalence by age, for fitting/benchmarking (used in chunks 6, 6a)
Dagnew_positivity_data <- read.csv("data/Dagnew_2026_IGRA_positivity_by_age_table_s5.csv") %>%
  select(country, site_no, age_group, pct_positive, ci_lo_positive, ci_hi_positive) %>%
  mutate(across(c(pct_positive, ci_lo_positive, ci_hi_positive), ~ .x / 100)) %>%  # convert % to proportion
  group_by(country, age_group) %>% summarise(min_positivity = min(ci_lo_positive), max_positivity = max(ci_hi_positive)) %>%
  ungroup()
```

## 2. Define age structure

```{r}
#| label: define_age_structure

age_structure <- "South Africa"  # works for "uniform" or any UN-recognised country, e.g. "South Africa"
agedist <- extract_age_distribution(unwpp, age_structure)  # population age distribution
```

## 3. Define parameter values
`pars_lit` takes best-known parameter values from the literature.

```{r}
#| label: define_params

# Edit here as desired
rho_lit <- make_foi(6,5,7,7,5)  # South Africa best fit; ideally use with Vynnycky-high/mu_s=0.003
p_slow_lit <- extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-high")  # works for "uniform", "Vynnycky-1997", "Vynnycky-high"
mu_slow_lit <- define_mu_slow("0.003")  # works for "min", "base", "0.003", "max"
p_revert_lit <- Dagnew_reversion_data %>% filter(country==age_structure) %>% pull(prob_of_reversion_once_infected)

pars_lit <- list(
	minage=15, # taken from above
	maxage=49, # taken from above
	rho=rho_lit,  # from fitting
	p_slow=p_slow_lit,  # from lit
	mu_slow=mu_slow_lit,  # from lit
	mu_fast=1.5,  # for most fast progressors progressing within two years, assuming exponential dist
	p_revert=p_revert_lit,  # from lit
	mu_revert=0.75, # for most reverters reverting within two years, assuming exponential dist
	sigma=100,  # IGRA test is essentially lifelong
	trial_length=3) # taken from above
```

## 4. South Africa parameter fitting

Note: run code snippets 1-3 first.
Note: full fitting is now done in separate code.
```{r}
#| label: SA_parameter_fit_plot
#| eval: FALSE

# Full fitting is now done in separate code. Read in results:
summary_table <- read.csv("output/parameter_fit_results.csv")

# plot parameter fitting results
slow_labels <- c("min"   = "μ_s = 0.0001",
  "base"  = "μ_s = 0.001",
  "0.003" = "μ_s = 0.003",
  "max"   = "μ_s = 0.00527")

prog_labels <- c("Vynnycky-1997" = "4–14% age-varying",
  "Vynnycky-high" = "4–19% age-varying")

# thresholds for plot
dagnew_age20_min <- Dagnew_positivity_data %>% filter(country=="South Africa" & age_group=="15-24") %>% pull(min_positivity)
dagnew_age20_max <- Dagnew_positivity_data %>% filter(country=="South Africa" & age_group=="15-24") %>% pull(max_positivity)

fig_4 <- summary_table %>%
  ggplot(aes(x=inf_prev_15to24, y=ARTI, shape=progression_structure, col=conditions_met)) +
  annotate("rect", xmin=dagnew_age20_min, xmax=dagnew_age20_max,
           ymin=0.04, ymax=0.06, alpha=0.1, fill="steelblue") +
  geom_vline(xintercept=c(dagnew_age20_min, dagnew_age20_max),
             linetype="dashed", col="steelblue", linewidth=0.4) +
  geom_hline(yintercept=c(0.04, 0.06),
             linetype="dashed", col="steelblue", linewidth=0.4) +
  geom_point(data=~filter(.x, !conditions_met), size=2, alpha=0.8) +
  geom_point(data=~filter(.x, conditions_met), size=2, alpha=0.8) +
  scale_colour_manual(values=c("FALSE"="grey80", "TRUE"="forestgreen")) +
  scale_shape_manual(values=c(16, 17), labels=prog_labels) +
  facet_wrap(~slow_structure, labeller=as_labeller(slow_labels)) +
  theme_classic() +
  theme(strip.background=element_blank()) +
  labs(x="Infection prevalence, age 15-24", y="ARTI",
       col="All conditions met", shape="p_f")

fig_4
ggsave(fig_4, file="figures/4_parameter_fit.png", width=7.29, height=4.51)

# summary table
library(flextable)
summary_table %>%
  filter(conditions_met) %>%
  select(foi_structure, progression_structure, slow_structure,
         inf_prev_15to24, inf_prev_25to34, ARTI, cases) %>%
  mutate(across(c(inf_prev_15to24, inf_prev_25to34), ~ round(.x, 2)),
         across(c(ARTI), ~ round(.x, 3)),
         across(c(cases), ~ round(.x, 0))) %>%
  arrange(slow_structure, progression_structure) %>%
  flextable() %>%
  autofit() %>%
  save_as_docx(path="output/parameter_fit_passing.docx")
```

## 5. South Africa literature simulation

```{r}
#| label: simulate_with_lit
#| eval: FALSE

# Simulate the stochastic approach with lit params, over the duration of positivity sigma OR pre-load saved csv file
with_progress({
  stochastic_df_lit <- sim_stoch_over_sigma(pars=pars_lit, sigmavec=c(0.5, 1:10, seq(12, 50, by=2)), casetarget=50, agedist=agedist, reps=100)
})

# Simulate the analytical approach with lit params, over the duration of positivity sigma
analytical_df_lit <- sim_analytic_over_sigma(pars=pars_lit, sigmavec=seq(from=0.5, to=50, by=0.2), casetarget=50, agedist=agedist)

# Plot all results (per 1)
fig_stochastic_analytic_lit <- plot_stochastic_analytic(stochastic_df_lit, analytical_df_lit, ylimit=1000)
fig_stochastic_analytic_lit
ggsave(fig_stochastic_analytic_lit, file=paste0("figures/stochastic_analytic_lit.png"), width=7.29, height=4.51)

fig_stochastic_analytic_lit_zoom <- plot_stochastic_analytic(stochastic_df_lit %>% filter(sigma <= 15), analytical_df_lit %>% filter(sigma <= 15))
fig_stochastic_analytic_lit_zoom
ggsave(fig_stochastic_analytic_lit_zoom, file=paste0("figures/stochastic_analytic_lit_zoom.png"), width=7.29, height=4.51)

# Save full (per-rep, per-sigma) South Africa results for reuse in chunk 6c, instead of re-simulating
# South Africa there. n_enrolled_1/n_tested_1 pre-computed to match the schema used by chunk 6a/6b.
stochastic_df_lit_full <- stochastic_df_lit %>%
  mutate(country = "South Africa", p_slow = "Vynnycky-high",
         n_enrolled_1 = n_enrolled / n_trial_cases, n_tested_1 = n_tested / n_trial_cases)
write.csv(stochastic_df_lit_full, file="output/southafrica_stochoutput.csv", row.names=FALSE)

#' Summary table: infection prevalence at ages 20/30, ARTI, case incidence
#' Computed from stochastic output at sigma=50 (infection prevs, ARTI, cases). Saved for reuse in
#' chunk 6a (combined into summary_table_6a) instead of re-simulating South Africa there.
summary_table_5 <- stochastic_df_lit_full %>%
  filter(sigma == 50) %>%
  mutate(inf_prev_all = (n_overall - n_tested + n_enrolled) / n_overall,
    meanage      = ((pars_lit$maxage - pars_lit$minage) / 2) + pars_lit$minage,
    ARTI         = 1 - (1 - inf_prev_all)^(1 / meanage),
    cases_per100k = n_trial_cases / (n_overall * pars_lit$trial_length) * 100000) %>%
  group_by(country, p_slow) %>%
  summarise(inf_prev_15to24 = median(inf_prev_15to24),
    inf_prev_25to34 = median(inf_prev_25to34),
    ARTI            = median(ARTI),
    cases_per100k   = median(cases_per100k),
    .groups = "drop")

write.csv(summary_table_5, file="output/southafrica_results.csv", row.names=FALSE)
```

## 6. Scenarios (shared setup)

Note: run code snippets 1-3 first.

Shared setup for the country-scenario chunks below (6a-6c): country list, age distributions, p_revert by country, and the three p_slow structures used by 6a/6b. Run this once before 6a, 6b, or 6c.

```{r}
#| label: 6_scenarios_setup
#| eval: FALSE

countries_scenarios <- c("South Africa", "Kenya", "India")

# Pre-compute age distributions — keeps unwpp out of the future_lapply workers
agedists_scenarios <- setNames(lapply(countries_scenarios, function(c) extract_age_distribution(unwpp, c)), countries_scenarios)

p_revert_by_country <- list(
  "South Africa" = Dagnew_reversion_data %>% filter(country=="South Africa") %>% pull(prob_of_reversion_once_infected),
  "Kenya"        = Dagnew_reversion_data %>% filter(country=="Kenya")        %>% pull(prob_of_reversion_once_infected),
  "India"        = Dagnew_reversion_data %>% filter(country=="Bangladesh")   %>% pull(prob_of_reversion_once_infected))  # Bangladesh used as proxy for India

# Shared p_slow structures for 6a/6b (6c uses a single fixed p_slow per country instead)
p_slow_structures_scenarios <- list(
  "uniform_95"    = extract_probability_of_being_slow(progressor_type_by_age_studies, "uniform"),
  "Vynnycky-1997" = extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-1997"),
  "Vynnycky-high" = extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-high"))

# Shared benchmark thresholds by country, used for conditions_met checks in 6a (uniform sweep) and the
# Kenya/India age-varying parameter fitting
country_thresholds_scenarios <- tibble(
  country       = c("South Africa", "Kenya",   "India"),
  arti_lo       = c(0.04,           0.016,      0.00),
  arti_hi       = c(0.06,           0.036,      0.02),
  cases_lo      = c(242,            109,        160),
  cases_hi      = c(571,            339,        218)
)
```

## 6a. Varied vaccine trial sites

A full age-varying FOI model fitting for Kenya and India, mirroring the South Africa fitting, was run in a separate code (`code/foi_overnight_run.R`). FOI search range for each country was informed by an initial uniform sweep (Kenya: 2-5%, India: 1-4%). Best-choice foi for each country is used for model simulations here.

```{r}
#| label: 6a_varied_site_results
#| eval: FALSE

# Full fitting is done in separate code. View summary results here:
summary_table <- read.csv("output/kenya_india_parameter_fit_results.csv")

# Plot varied site results, using one best-choice FOI informed by results of the model fitting chunks.
# Kenya and India are simulated here and South Africa results (chunk 5) are read in for the plot.
pars_6a     <- pars_lit
p_revert_6a <- p_revert_by_country

countries_6a_sim  <- c("Kenya", "India")               # simulated in this chunk
countries_6a_plot <- c("South Africa", "Kenya", "India")  

foi_by_country <- list(
  "Kenya" = make_foi(5,2,5,4,2),   # use with Vynnycky-1997/mu_s=0.003
  "India" = make_foi(2,1,3,1,1))  # use with Vynnycky-1997/mu_s=0.003

p_slow_lookup_6a <- list(
  "Vynnycky-1997" = extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-1997"),
  "uniform"       = extract_probability_of_being_slow(progressor_type_by_age_studies, "uniform"))

sim_grid_6a <- tibble(country=countries_6a_sim) %>%
  crossing(p_slow=c("Vynnycky-1997","uniform")) %>%
  crossing(sigma = c(0.5, 1:10, seq(12, 50, by=2)), rep = 1:100)

# Single flat future_lapply — avoids nested parallelism and memory spikes
with_progress({
  p <- progressr::progressor(steps=nrow(sim_grid_6a))
  stoch_list_6a <- future.apply::future_lapply(1:nrow(sim_grid_6a), function(i) {
    pars_i        <- pars_6a
    pars_i$rho    <- foi_by_country[[sim_grid_6a$country[i]]]
    pars_i$p_slow <- p_slow_lookup_6a[[sim_grid_6a$p_slow[i]]]
    pars_i$mu_slow <- define_mu_slow("0.003")
    pars_i$p_revert <- p_revert_6a[[sim_grid_6a$country[i]]]
    pars_i$sigma  <- sim_grid_6a$sigma[i]
    agedist_i     <- agedists_scenarios[[sim_grid_6a$country[i]]]
    out           <- sim_stoch(pars_i, casetarget=50, agedist=agedist_i)
    p()
    tibble(country=sim_grid_6a$country[i], p_slow=sim_grid_6a$p_slow[i],
       sigma=sim_grid_6a$sigma[i], rep=sim_grid_6a$rep[i],
       n_tested=out$n_tested, n_enrolled=out$n_enrolled, n_overall=out$n_overall,
       n_trial_cases=out$n_trial_cases, inf_prev_15to24=out$inf_prev_15to24, inf_prev_25to34=out$inf_prev_25to34)
  }, future.seed=TRUE)
})

stoch_df_6a <- bind_rows(stoch_list_6a)

# Save full (raw counts, per-rep) Kenya/India results for reuse in chunk 6c, instead of re-simulating there
write.csv(stoch_df_6a, file="output/variedsite_results_stochoutput.csv", row.names=FALSE)

#' 2x3 panel plot: rows = n_enrolled_1 / n_tested_1, columns = country (South Africa, Kenya, India),
#' colour = p_slow. South Africa's raw sigma-sweep data comes from chunk 5's saved output (not
#' re-simulated here) and is bound onto Kenya/India's freshly-simulated data before plotting.
stoch_df_sa_6a <- read.csv("output/southafrica_stochoutput.csv") %>%
  select(country, p_slow, sigma, rep, n_tested, n_enrolled, n_overall, n_trial_cases, inf_prev_15to24, inf_prev_25to34)

stoch_df_6a_all <- bind_rows(stoch_df_6a, stoch_df_sa_6a)

stoch_df_6a_long <- stoch_df_6a_all %>%
  mutate(country = factor(country, levels=countries_6a_plot),
         n_enrolled_1 = n_enrolled / n_trial_cases,
         n_tested_1   = n_tested   / n_trial_cases) %>%
  select(country, p_slow, sigma, rep, n_enrolled_1, n_tested_1) %>%
  pivot_longer(cols=c(n_enrolled_1, n_tested_1), names_to="metric", values_to="value") %>%
  mutate(metric = case_when(metric=="n_enrolled_1"~"Enrolled", metric=="n_tested_1"~"Tested"),
         metric = factor(metric, levels=c("Enrolled","Tested")))

median_df_6a <- stoch_df_6a_long %>%
  group_by(country, p_slow, sigma, metric) %>%
  summarise(value = median(value), .groups="drop")
iqr_6a <- stoch_df_6a_long %>%
  group_by(country, p_slow, sigma, metric) %>%
  summarise(iqr_lo = quantile(value, 0.25),
            iqr_hi = quantile(value, 0.75), .groups = "drop")
median_df_6a <- median_df_6a %>% left_join(iqr_6a, by = c("country", "p_slow", "sigma", "metric"))
write.csv(median_df_6a, file="output/variedsite_results_medians.csv", row.names=FALSE)

p_slow_labels_6a  <- c("uniform"="5%","Vynnycky-1997"="4-14%","Vynnycky-high"="4-19%")

fig_6a <- ggplot(stoch_df_6a_long, aes(x=sigma, y=value, col=p_slow)) +
  geom_point(size=0.4, alpha=0.1) +
  geom_line(data=median_df_6a, linewidth=0.7) +
  facet_grid(metric ~ country, scales="free_y") +
  scale_colour_brewer(palette="Set1", labels=p_slow_labels_6a) +
  theme_classic() +
  theme(strip.background=element_blank()) +
  labs(x="Test span (years)", y="Number (for 1 case)", col="p_f")
fig_6a
ggsave(fig_6a, file="figures/6a_varied_sites.png", width=7.29, height=4.51)

fig_6a_zoom <- ggplot(stoch_df_6a_long %>% filter(sigma <= 15),
                      aes(x=sigma, y=value, col=p_slow)) +
  geom_point(size=0.4, alpha=0.1) +
  geom_line(data=median_df_6a %>% filter(sigma <= 15), linewidth=0.7) +
  facet_grid(metric ~ country, scales="free_y") +
  scale_colour_brewer(palette="Set1", labels=p_slow_labels_6a) +
  theme_classic() +
  theme(strip.background=element_blank()) +
  labs(x="Test span (years)", y="Number (for 1 case)", col="p_f")
fig_6a_zoom
ggsave(fig_6a_zoom, file="figures/6a_varied_sites_zoom.png", width=7.29, height=4.51)

#' Summary table: infection prevalence at ages 20/30, ARTI, case incidence, for Kenya/India
#' Computed from stochastic output at sigma=50 (infection prevs, ARTI, cases)
summary_table_6a_ki <- stoch_df_6a %>%
  filter(sigma == 50) %>%
  mutate(inf_prev_all = (n_overall - n_tested + n_enrolled) / n_overall,
    meanage      = ((pars_6a$maxage - pars_6a$minage) / 2) + pars_6a$minage,
    ARTI         = 1 - (1 - inf_prev_all)^(1 / meanage),
    cases_per100k = n_trial_cases / (n_overall * pars_6a$trial_length) * 100000) %>%
  group_by(country, p_slow) %>%
  summarise(inf_prev_15to24 = median(inf_prev_15to24),
    inf_prev_25to34 = median(inf_prev_25to34),
    ARTI            = median(ARTI),
    cases_per100k   = median(cases_per100k),
    .groups = "drop")

# Combine with South Africa's pre-computed summary (chunk 5) instead of re-simulating it here
summary_table_sa <- read.csv("output/southafrica_results.csv")
summary_table_6a <- bind_rows(summary_table_sa, summary_table_6a_ki)

write.csv(summary_table_6a, file="output/variedsite_results.csv", row.names=FALSE)
```

```{r}
#| eval: FALSE
## Build a copy-paste-ready table for manuscript TABLE varied-trial-sites.
variedsite_results <- read.csv("output/variedsite_results.csv")

foi_by_country_label <- c("India"="2,1,3,1,1", "Kenya"="5,2,5,4,2", "South Africa"="6,5,7,7,5")
chosen_foi_structure <- c("India"="2_1_3_1_1", "Kenya"="5_2_5_4_2", "South Africa"="6_5_7_7_5")
p_slow_label <- c("Vynnycky-1997"="4-14%", "uniform"="5%", "Vynnycky-high"="4-19%")

sa_conditions <- read.csv("output/parameter_fit_results.csv") %>%
  filter(slow_structure=="0.003", foi_structure==chosen_foi_structure[["South Africa"]]) %>%
  select(country, p_slow=progression_structure, conditions_met)

ki_conditions <- read.csv("output/kenya_india_parameter_fit_results.csv") %>%
  filter(slow_structure=="0.003",
         (country=="Kenya" & foi_structure==chosen_foi_structure[["Kenya"]]) |
         (country=="India" & foi_structure==chosen_foi_structure[["India"]])) %>%
  select(country, p_slow=progression_structure, conditions_met)

conditions_lookup <- bind_rows(sa_conditions, ki_conditions)

table_varied_trial_sites <- variedsite_results %>%
  left_join(conditions_lookup, by=c("country","p_slow")) %>%
  mutate(rho = foi_by_country_label[country],
         p_f = p_slow_label[p_slow],
         country = factor(country, levels=c("India","Kenya","South Africa")),
         across(c(inf_prev_15to24, inf_prev_25to34, ARTI), ~round(.x, 3)),
         cases_per100k = round(cases_per100k, 0)) %>%
  arrange(country, p_f) %>%
  select(Country=country, rho, p_f,
         `Infection prevalence 15-24y`=inf_prev_15to24,
         `Infection prevalence 25-34y`=inf_prev_25to34,
         ARTI,
         `Case incidence per 100k per year`=cases_per100k,
         `All conditions met?`=conditions_met)

write.csv(table_varied_trial_sites, file="output/table_varied_trial_sites.csv", row.names=FALSE)
```

```{r}
#| eval: FALSE
## Build a copy-paste-ready table for manuscript TABLE economic-costs (No. needed to test/enrol columns).
medians_6a <- read.csv("output/variedsite_results_medians.csv")

foi_by_country_label <- c("India"="2,1,3,1,1", "Kenya"="5,2,5,4,2", "South Africa"="6,5,7,7,5")
p_slow_label <- c("Vynnycky-1997"="4-14%", "uniform"="5%", "Vynnycky-high"="4-19%")

table_economic_costs <- medians_6a %>%
  filter(sigma %in% c(2, 50), metric %in% c("Tested", "Enrolled")) %>%
  mutate(cell = sprintf("%.0f [%.0f-%.0f]", value, iqr_lo, iqr_hi),
         col  = paste0(metric, "_sigma", sigma)) %>%
  select(country, p_slow, col, cell) %>%
  pivot_wider(names_from = col, values_from = cell) %>%
  mutate(rho = foi_by_country_label[country],
         p_f = p_slow_label[p_slow],
         country = factor(country, levels = c("India", "Kenya", "South Africa"))) %>%
  arrange(country, p_f) %>%
  select(Country = country, rho, p_f,
         `No. needed to test (sigma=2y)`  = Tested_sigma2,
         `No. needed to test (sigma=50y)` = Tested_sigma50,
         `No. needed to enrol (sigma=2y)` = Enrolled_sigma2,
         `No. needed to enrol (sigma=50y)`= Enrolled_sigma50)

write.csv(table_economic_costs, file = "output/table_economic_costs.csv", row.names = FALSE)
```

## 6b. No-test enrolment scenarios

Three scenarios using `sim_stoch_notest`: standard ages (15-49), younger ages (12-34), and household contacts (6-99, high instantaneous FOI if not already infected). No sigma dimension — one output per (scenario, country, FOI, rep).

```{r}
#| label: 6b_notest_scenarios
#| eval: FALSE

plan(multisession, workers=n_workers)

countries_6b      <- countries_scenarios
p_slow_structures_6b <- p_slow_structures_scenarios
p_revert_6b       <- p_revert_by_country
mu_slow_6b        <- define_mu_slow("0.003")
agedists_6b       <- agedists_scenarios

# Build base parameter list
pars_6b <- pars_lit
pars_6b$mu_slow <- mu_slow_6b

# Flat grid: scenario x country x FOI x rep
scenarios_6b <- tibble(scenario = c("no test standard", "no test young", "no test household"),
                       minage   = c(15, 12, 6),
                       maxage   = c(49, 34, 99))

# Each country uses its single fitted FOI (Vynnycky-high for South Africa, Vynnycky-1997 for Kenya/India)
# regardless of which p_slow structure is being shown, matching the same approach used in 6a above
foi_by_country_6b <- list(
  "South Africa" = make_foi(6,5,7,7,5),
  "Kenya"        = make_foi(5,2,5,4,2),
  "India"        = make_foi(2,1,3,1,1))

sim_grid_6b <- crossing(
  bind_rows(tibble(country="South Africa", slow_structure="Vynnycky-high"),
    tibble(country="Kenya", slow_structure=c("uniform_95","Vynnycky-1997")),
    tibble(country="India", slow_structure=c("uniform_95","Vynnycky-1997"))),
  scenarios_6b,
  rep = 1:100)

with_progress({
  p <- progressr::progressor(steps=nrow(sim_grid_6b))
  notest_list_6b <- future.apply::future_lapply(1:nrow(sim_grid_6b), function(i) {
    pars_i        <- pars_6b
    pars_i$rho    <- foi_by_country_6b[[sim_grid_6b$country[i]]]
    pars_i$minage <- sim_grid_6b$minage[i]
    pars_i$maxage <- sim_grid_6b$maxage[i]
    pars_i$p_slow   <- p_slow_structures_6b[[sim_grid_6b$slow_structure[i]]]
    pars_i$p_revert <- p_revert_6b[[sim_grid_6b$country[i]]]
    agedist_i     <- agedists_6b[[sim_grid_6b$country[i]]]
    out           <- sim_stoch_notest(pars_i, casetarget=50, agedist=agedist_i,
                                      households = (sim_grid_6b$scenario[i] == "no test household"))
    p()
    tibble(
      scenario      = sim_grid_6b$scenario[i],
      country       = sim_grid_6b$country[i],
      slow_structure  = sim_grid_6b$slow_structure[i],
      rep           = sim_grid_6b$rep[i],
      n_enrolled   = out$n_enrolled,
      n_fast        = out$n_fast,
      n_trial_cases = out$n_trial_cases,
      n_overall     = out$n_overall,
      n_infected    = out$n_infected,
      inf_prev_15to24 = out$inf_prev_15to24,
      inf_prev_25to34 = out$inf_prev_25to34,
      minage = sim_grid_6b$minage[i],
      maxage = sim_grid_6b$maxage[i])
  }, future.seed=TRUE)
})

notest_df_6b <- bind_rows(notest_list_6b) %>%
  mutate(n_enrolled_1 = n_enrolled / n_trial_cases)

# Save full (per-rep) no-test results for reuse in chunk 6c, instead of re-simulating there
write.csv(notest_df_6b, file="output/notest_stochoutput.csv", row.names=FALSE)

#' Summarise over reps: median + 10th/90th percentile
notest_summary_6b <- notest_df_6b %>%
  group_by(scenario, country, slow_structure) %>%
  summarise(
    n_enrolled_med = median(n_enrolled),
    n_enrolled_lo  = quantile(n_enrolled, 0.1),
    n_enrolled_hi  = quantile(n_enrolled, 0.9),
    n_overall_med   = median(n_overall),
    n_overall_lo    = quantile(n_overall, 0.1),
    n_overall_hi    = quantile(n_overall, 0.9),
    .groups = "drop"
  )
write.csv(notest_summary_6b, file="output/notest_results.csv", row.names=FALSE)

#' Plot: x = scenario, facet = country, line = p_f
fig_6b <- notest_df_6b %>%
  mutate(country       = factor(country, levels=countries_6b),
         scenario      = factor(scenario, levels=c("no test standard","no test young","no test household")),
         slow_structure = factor(slow_structure, levels=names(p_slow_structures_6b)),
         n_enrolled_1  = n_enrolled / n_trial_cases) %>%
  ggplot(aes(x=scenario, y=n_enrolled_1, fill=slow_structure)) +
  geom_boxplot(coef=Inf) +
  scale_fill_brewer(palette="Set1",
                    labels=c("uniform_95"="5%","Vynnycky-1997"="4-14%","Vynnycky-high"="4-19%")) +
  facet_wrap(~country, nrow=1) +
  theme_classic() +
  theme(strip.background=element_blank(), axis.text.x=element_text(angle=25, hjust=1)) +
  labs(x=NULL, y="Number enrolled (for 1 case)", fill="p_f")
fig_6b
ggsave(fig_6b, file="figures/6b_notest_scenarios.png", width=7.29, height=4.51)

## Build a copy-paste-ready table for manuscript no-test-scenarios table (No. needed to
## contact/enrol, by country x p_f x scenario), with IQR in square brackets.
notest_raw <- read.csv("output/notest_stochoutput.csv") %>%
  mutate(n_overall_1 = n_overall / n_trial_cases,
         n_enrolled_1 = n_enrolled / n_trial_cases)

foi_by_country_label <- c("India"="2,1,3,1,1", "Kenya"="5,2,5,4,2", "South Africa"="6,5,7,7,5")
p_slow_label <- c("Vynnycky-1997"="4-14%", "uniform_95"="5%", "Vynnycky-high"="4-19%")
scenario_label <- c("no test standard"="standard", "no test young"="young", "no test household"="household")

notest_summary_iqr <- notest_raw %>%
  group_by(country, slow_structure, scenario) %>%
  summarise(
    contact_cell = sprintf("%.0f [%.0f-%.0f]", median(n_overall_1), quantile(n_overall_1, 0.25), quantile(n_overall_1, 0.75)),
    enrol_cell   = sprintf("%.0f [%.0f-%.0f]", median(n_enrolled_1), quantile(n_enrolled_1, 0.25), quantile(n_enrolled_1, 0.75)),
    .groups = "drop"
  ) %>%
  mutate(scenario = scenario_label[scenario]) %>%
  pivot_wider(names_from = scenario, values_from = c(contact_cell, enrol_cell))

table_notest <- notest_summary_iqr %>%
  mutate(rho = foi_by_country_label[country],
         p_f = p_slow_label[slow_structure],
         country = factor(country, levels = c("India", "Kenya", "South Africa"))) %>%
  arrange(country, p_f) %>%
  select(Country = country, rho, p_f,
         `No. needed to contact (standard)`   = contact_cell_standard,
         `No. needed to contact (young)`      = contact_cell_young,
         `No. needed to contact (household)`  = contact_cell_household,
         `No. needed to enrol (standard)`     = enrol_cell_standard,
         `No. needed to enrol (young)`        = enrol_cell_young,
         `No. needed to enrol (household)`    = enrol_cell_household)

write.csv(table_notest, file = "output/table_notest_results.csv", row.names = FALSE)
library(knitr)
kable(table_notest)
```

## 6c. Main figure: test-based vs no-test strategies combined

Combines two test-based strategies (sigma = 2 years, ~lifetime) with the three `sim_stoch_notest` scenarios from 6b, one fixed FOI and one fixed p_slow structure per country (Vynnycky-high for South Africa, Vynnycky-1997 for Kenya and India), fill = enrolment strategy. No new simulation here - reads the full per-rep results already saved by chunks 5 (South Africa), 6a (Kenya/India), and 6b (no-test scenarios).

```{r}
#| label: 6c_main_combined
#| eval: FALSE

countries_6c <- countries_scenarios

# Strategy definitions: 2 test-based (sigma = 2y / lifetime) + 3 no-test scenarios
strategy_levels_6c <- c("No test\nstandard", "No test\nyoung", "No test\nhousehold", "Test\nIGRA", "Test\nrecent infection")

# Test-based: South Africa from chunk 5's full output, Kenya/India from chunk 6a's full output.
# Each country only has one fitted p_slow shown here (Vynnycky-high for SA, Vynnycky-1997 for Kenya/India).
sa_test_6c <- read.csv("output/southafrica_stochoutput.csv") %>%
  filter(sigma %in% c(2, 50)) %>%
  mutate(strategy = ifelse(sigma == 50, "test_lifetime", "test_2y"))

ki_test_6c <- read.csv("output/variedsite_results_stochoutput.csv") %>%
  filter(p_slow == "Vynnycky-1997", sigma %in% c(2, 50)) %>%
  mutate(n_enrolled_1 = n_enrolled / n_trial_cases,
         strategy = ifelse(sigma == 50, "test_lifetime", "test_2y"))

test_6c <- bind_rows(
  sa_test_6c %>% select(country, strategy, rep, n_enrolled_1),
  ki_test_6c %>% select(country, strategy, rep, n_enrolled_1))

# No-test: from chunk 6b's full output. Each country only has one fitted p_slow shown here
# (Vynnycky-high for SA, Vynnycky-1997 for Kenya/India), matching the test-based strategies above.
notest_6c <- read.csv("output/notest_stochoutput.csv") %>%
  filter((country == "South Africa" & slow_structure == "Vynnycky-high") |
         (country %in% c("Kenya","India") & slow_structure == "Vynnycky-1997")) %>%
  mutate(strategy = scenario) %>%
  select(country, strategy, rep, n_enrolled_1)

stoch_df_6c <- bind_rows(test_6c, notest_6c) %>%
  mutate(strategy = case_when(
    strategy == "no test standard"  ~ "No test\nstandard",
    strategy == "no test young"     ~ "No test\nyoung",
    strategy == "no test household" ~ "No test\nhousehold",
    strategy == "test_lifetime"     ~ "Test\nIGRA",
    strategy == "test_2y"           ~ "Test\nrecent infection"))

# Plot: x = strategy (grouped, test-based then no-test), 3 dodged boxes per group = country, fill = country
country_colours_6c <- c("South Africa"="#4DAF4A", "Kenya"="#377EB8", "India"="#E41A1C")
fig_6c <- stoch_df_6c %>%
  mutate(country  = factor(country, levels=countries_6c),
         strategy = factor(strategy, levels=strategy_levels_6c)) %>%
  ggplot(aes(x=strategy, y=n_enrolled_1, fill=country)) +
  geom_boxplot(coef=Inf, position=position_dodge2(preserve="single")) +
  scale_fill_manual(values=country_colours_6c) +
  theme_classic() +
  theme(strip.background=element_blank(), axis.text.x=element_text(angle=25, hjust=1)) +
  labs(x=NULL, y="Number needed to enrol (for 1 case)", fill="Country")
fig_6c
ggsave(fig_6c, file="figures/6c_main_combined.png", width=7.29, height=4.51)

# Main plot alternative 1 (Test-based strategies only, with 6-month span)
sigma_to_strategy_6c_alt1 <- function(sigma) case_when(
  sigma == 0.5 ~ "Test\n6 months span",
  sigma == 2   ~ "Test\n2 years span",
  sigma == 50  ~ "Test\nIGRA")
strategy_levels_6c_alt1 <- c("Test\nIGRA", "Test\n2 years span", "Test\n6 months span")

sa_test_6c_alt1 <- read.csv("output/southafrica_stochoutput.csv") %>%
  filter(sigma %in% c(0.5, 2, 50)) %>%
  mutate(strategy = sigma_to_strategy_6c_alt1(sigma))

ki_test_6c_alt1 <- read.csv("output/variedsite_results_stochoutput.csv") %>%
  filter(p_slow == "Vynnycky-1997", sigma %in% c(0.5, 2, 50)) %>%
  mutate(n_enrolled_1 = n_enrolled / n_trial_cases,
         strategy = sigma_to_strategy_6c_alt1(sigma))

stoch_df_6c_alt1 <- bind_rows(
  sa_test_6c_alt1 %>% select(country, strategy, rep, n_enrolled_1),
  ki_test_6c_alt1 %>% select(country, strategy, rep, n_enrolled_1))

fig_6c_alt1 <- stoch_df_6c_alt1 %>%
  mutate(country  = factor(country, levels=countries_6c),
         strategy = factor(strategy, levels=strategy_levels_6c_alt1)) %>%
  ggplot(aes(x=strategy, y=n_enrolled_1, fill=country)) +
  geom_boxplot(coef=Inf, position=position_dodge2(preserve="single")) +
  scale_fill_manual(values=country_colours_6c) +
  theme_classic() +
  labs(x=NULL, y="Number needed to enrol (for 1 case)", fill="Country")
fig_6c_alt1
ggsave(fig_6c_alt1, file="figures/6c_alt1.png", width=7.29, height=4.51)

# Main plot alternative 2
dop_df_6c_alt2 <- bind_rows(
    read.csv("output/southafrica_stochoutput.csv") %>% select(country, sigma, rep, n_enrolled_1),
    read.csv("output/variedsite_results_stochoutput.csv") %>%
      filter(p_slow == "Vynnycky-1997") %>%  mutate(n_enrolled_1 = n_enrolled / n_trial_cases) %>% 
      select(country, sigma, rep, n_enrolled_1))

dop_median_6c_alt2 <- dop_df_6c_alt2 %>%
  group_by(country, sigma) %>%
  summarise(n_enrolled_1 = median(n_enrolled_1), .groups="drop")

household_thresh_6c_alt2 <- notest_6c %>%
  filter(strategy == "no test household") %>%
  group_by(country) %>%
  summarise(n_enrolled_1 = median(n_enrolled_1), .groups="drop")

fig_6c_alt2 <- dop_df_6c_alt2 %>%
  mutate(country = factor(country, levels=countries_6c)) %>%
  ggplot(aes(x=sigma, y=n_enrolled_1, col=country)) +
  geom_point(size=0.6, alpha=0.1) +
  geom_line(data=dop_median_6c_alt2 %>% mutate(country=factor(country, levels=countries_6c)), linewidth=0.8) +
  geom_hline(data=household_thresh_6c_alt2, aes(yintercept=n_enrolled_1, col=country),
             linetype="dashed", linewidth=0.5, alpha=0.7) +
  scale_colour_manual(values=country_colours_6c) +
  theme_classic() +
  labs(x="Duration of positivity, σ (years)", y="Number needed to enrol (for 1 case)",
       col="Country", subtitle="Dashed lines: median no-test household yield")
fig_6c_alt2
ggsave(fig_6c_alt2, file="figures/6c_alt2.png", width=7.29, height=4.51)
```

## 7. M72IIb emulation fitting

Rather than stopping at casetarget=50 and scaling up, `sim_stoch_trial` recruits until enrol_target is reached.
```{r}
#| label: simulate_with_m72IIb_fit
#| eval: FALSE

target_enrolled <- 3289
target_cases    <- 52

pars_m72IIb <- list(
	minage=18,  # from trial
	maxage=49,  # from trial (up to 50.0y)
	rho=make_foi(6,5,7,7,5),  # modelled value (South Africa; Vynnycky-high/mu_s=0.003, confirmed robust at reps=100, see chunk 3)
	p_slow=NA,  # modelled value
	mu_slow=NA,  # assumed, informed by lit
	mu_fast=1.5,  # from lit
	p_revert=p_revert_lit,  # from lit
	mu_revert=0.75, # from lit
	sigma=80,  # IGRA test is essentially lifelong
	trial_length=3)  # from trial
p_slow_m72IIb_vals     <- seq(0.5, 1.0, by=0.05)
slow_structures_m72IIb <- c("base", "min", "max", "0.003")
reps <- 100

# Build a flat grid of all parameter combinations x reps
uniform_grid <- expand.grid(
  slow_structure = slow_structures_m72IIb,
  p_slow_label   = paste0("uniform_", seq(0.5, 0.95, by=0.05)),
  rep            = 1:reps,
  stringsAsFactors = FALSE)
vynnycky_grid <- expand.grid(
  slow_structure = slow_structures_m72IIb,
  p_slow_label   = c("Vynnycky-1997", "Vynnycky-high"),
  rep            = 1:reps,
  stringsAsFactors = FALSE)
param_grid <- bind_rows(uniform_grid, vynnycky_grid)

with_progress({
  p <- progressr::progressor(steps=nrow(param_grid))
  trial_results_list <- future.apply::future_lapply(1:nrow(param_grid), function(i) {
    pars_fit         <- pars_m72IIb
    pars_fit$mu_slow <- define_mu_slow(param_grid$slow_structure[i])
    pars_fit$p_slow <- if (param_grid$p_slow_label[i] == "Vynnycky-1997") {
      extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-1997") 
      } else if (param_grid$p_slow_label[i] == "Vynnycky-high") {
        extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-high")
      } else {
        val <- as.numeric(sub("uniform_", "", param_grid$p_slow_label[i]))
        setNames(rep(val, 100), 0:99)
      }
    out <- sim_stoch_trial(pars_fit, enrol_target=target_enrolled, agedist=agedist)
    p()
    tibble(p_slow_structure= param_grid$p_slow_label[i],
      mu_slow        = pars_fit$mu_slow,
      foi_structure  = param_grid$foi_structure[i],
      rep            = param_grid$rep[i],
      n_overall      = out$n_overall,
      n_tested       = out$n_tested,
      n_enrolled     = out$n_enrolled,
      n_trial_cases  = out$n_trial_cases)
  }, future.seed=TRUE)
})

trial_results <- bind_rows(trial_results_list)

#' Summarise over reps
m72IIb_fit_trial <- trial_results %>%
  group_by(p_slow_structure, mu_slow) %>%
  summarise(
    n_overall_med = round(median(n_overall)),
    n_enrolled_med = round(median(n_enrolled)),
    n_trial_cases_med = round(median(n_trial_cases), 1),
    n_trial_cases_lo  = round(quantile(n_trial_cases, 0.1), 1),
    n_trial_cases_hi  = round(quantile(n_trial_cases, 0.9), 1),
    .groups       = "drop"
  ) %>%
  mutate(case_target_met = between(n_trial_cases_med, target_cases * 0.8, target_cases * 1.2))

write.csv(m72IIb_fit_trial, file="output/m72IIb_fit_results.csv", row.names=FALSE)
```

## 8. Stochastic & analytic match
```{r}
#| label: match_approaches
#| eval: FALSE

# Set non-age-varying params TODO
pars_lit_uniform <- list(
	minage=15, # taken from above
	maxage=49, # taken from above
	rho=make_foi(6,6,6,6,6),
	p_slow=extract_probability_of_being_slow(progressor_type_by_age_studies, "uniform"),
	mu_slow=mu_slow_lit,  # from lit
	mu_fast=1.5,  # for most fast progressors progressing within two years, assuming exponential distribution
	p_revert=0,  # no reversion for analytic match
	mu_revert=0, # no reversion for analytic match
	sigma=80,  # IGRA test is essentially lifelong
	trial_length=3)

# Simulate the stochastic approach with lit params, over the duration of positivity sigma OR pre-load saved csv file
with_progress({
  stochastic_df_match <- sim_stoch_over_sigma(pars=pars_lit_uniform, sigmavec=c(0.5,1:50), casetarget=50, agedist=agedist, reps=100)
})

#' Simulate the analytical approach with lit params, over the duration of positivity sigma
analytical_df_match <- sim_analytic_over_sigma(pars=pars_lit_uniform, sigmavec=seq(from=0.5, to=50, by=0.2), casetarget=50, agedist=agedist)

#' Plot all results
fig_stochastic_analytic_match <- plot_stochastic_analytic(stochastic_df_match, analytical_df_match)
fig_stochastic_analytic_match
ggsave(fig_stochastic_analytic_match, file=paste0("figures/stochastic_analytic_match.png"), width=7.29, height=4.51)
```

## 9. Size of trial

Explores the effect of varying trial size - continually enrolling until 5 vs 50 vs 500 cases are reached. How does this affect the level of uncertainty in model outputs? Does stochasticity scale with trial size as expected by a simple renewal-process/CLT argument.
```{r}
#| label: 9_size_of_trial_stochasticity
#| eval: FALSE

# Effect of trial size on observed stochasticity
plan(multisession, workers=n_workers)

casetargets_9 <- c(5, 50, 500)
sigmas_9      <- c(2, 50)  # consider two sigma values
reps_9        <- 100  # same rep count at every (sigma, casetarget) cell

pars_9 <- pars_lit  # South Africa's main fitted scenario, sigma overridden per grid row below (default sigma=100 otherwise)
sim_grid_9 <- crossing(sigma = sigmas_9, casetarget = casetargets_9, rep = 1:reps_9)

with_progress({
  p <- progressr::progressor(steps=nrow(sim_grid_9))
  trial_size_list_9 <- future.apply::future_lapply(1:nrow(sim_grid_9), function(i) {
    pars_i       <- pars_9
    pars_i$sigma <- sim_grid_9$sigma[i]
    out <- sim_stoch(pars_i, casetarget=sim_grid_9$casetarget[i], agedist=agedist)
    p()
    tibble(sigma=sim_grid_9$sigma[i], casetarget=sim_grid_9$casetarget[i], rep=sim_grid_9$rep[i],
           n_overall=out$n_overall, n_tested=out$n_tested, n_enrolled=out$n_enrolled,
           n_trial_cases=out$n_trial_cases)
  }, future.seed=TRUE)
})

trial_size_df_9 <- bind_rows(trial_size_list_9) %>%
  mutate(n_overall_1  = n_overall  / casetarget,
         n_tested_1   = n_tested   / casetarget,
         n_enrolled_1 = n_enrolled / casetarget)
write.csv(trial_size_df_9, file="output/size_of_trial_stochoutput.csv", row.names=FALSE)

# Panel A: raw spread by casetarget, sigma=2 vs 50 dodged within each metric facet - do the boxes
# visibly narrow as casetarget grows, at both sigma spans?
fig_9 <- trial_size_df_9 %>%
  pivot_longer(cols=c(n_overall_1, n_tested_1, n_enrolled_1), names_to="metric", values_to="value") %>%
  mutate(metric = case_when(metric=="n_overall_1"~"Contacted", metric=="n_tested_1"~"Tested", metric=="n_enrolled_1"~"Enrolled"),
         metric = factor(metric, levels=c("Contacted","Tested","Enrolled")),
         casetarget = factor(casetarget, levels=casetargets_9),
         sigma = factor(sigma, levels=sigmas_9)) %>%
  ggplot(aes(x=casetarget, y=value, fill=sigma)) +
  geom_boxplot(coef=Inf, position=position_dodge2(preserve="single")) +
  facet_wrap(~metric, scales="free_y") +
  scale_fill_brewer(palette="Set1") +
  theme_classic() +
  theme(strip.background=element_blank()) +
  labs(x="Trial size (case target)", y="Number (per case)", fill="σ (years)")
fig_9
ggsave(fig_9, file="figures/9_size_of_trial_spread.png", width=8.5, height=4.51)
```

## 10. Parameter sensitivity analysis

Explores which model parameters (rho, p_f, mu_fast, mu_slow, p_revert, mu_revert) shift trial outcomes the most, perturbing each +/-20% one at a time from South Africa's main fitted scenario (pars_lit). Uses the stochastic model. Three tornado plots: (a) raw per-case counts contacted/tested/enrolled, (b) funnel ratios (tested/contacted, enrolled/tested), (c) cross-sigma ratios (tested and enrolled at sigma=0.5y or 2y, relative to sigma=50y) - i.e. how sensitive the "recent-infection test" benefit itself is to each parameter.

```{r}
#| label: 10_sensitivity_analysis
#| eval: FALSE

plan(multisession, workers=n_workers)

reps_10   <- 100
sigmas_10 <- c(0.5, 2, 50)

# One perturbation function per parameter - multiplies the relevant field of pars_lit by `m`
# (0.8 or 1.2 for a -20%/+20% perturbation). rho/p_slow are age-varying vectors, scaled uniformly
# to preserve their age-shape rather than perturbing each of rho's 5 age bands separately.
# NB: p_slow (Vynnycky-high) sits close to 1 for most ages so p_fast is perturbed instead.
sensitivity_params_10 <- list(
  rho       = function(pars, m) { pars$rho <- pars$rho * m; pars },
  p_slow    = function(pars, m) { p_fast <- 1 - pars$p_slow; pars$p_slow <- 1 - (p_fast * m); pars },
  mu_fast   = function(pars, m) { pars$mu_fast <- pars$mu_fast * m; pars },
  mu_slow   = function(pars, m) { pars$mu_slow <- pars$mu_slow * m; pars },
  p_revert  = function(pars, m) { pars$p_revert <- pars$p_revert * m; pars },
  mu_revert = function(pars, m) { pars$mu_revert <- pars$mu_revert * m; pars }
)

# Flat grid: 1 baseline + (6 parameters x 2 directions) = 13 combinations, x 3 sigma x reps_10.
# Single future_lapply over the whole flat grid (not sim_stoch_over_sigma, which already
# parallelises internally over sigma x rep - nesting future_lapply inside future_lapply would be
# the mistake to avoid here, same reasoning as chunk 9's flat-grid comment).
sens_grid_10 <- crossing(
    parameter = c("baseline", names(sensitivity_params_10)),
    direction = c("low", "high")
  ) %>%
  filter(parameter != "baseline" | direction == "low") %>%
  mutate(direction = ifelse(parameter == "baseline", "baseline", direction)) %>%
  crossing(sigma = sigmas_10, rep = 1:reps_10)

with_progress({
  p <- progressr::progressor(steps = nrow(sens_grid_10))
  sens_list_10 <- future.apply::future_lapply(1:nrow(sens_grid_10), function(i) {
    pars_i      <- pars_lit
    parameter_i <- sens_grid_10$parameter[i]
    direction_i <- sens_grid_10$direction[i]
    if (parameter_i != "baseline") {
      multiplier <- if (direction_i == "low") 0.8 else 1.2
      pars_i <- sensitivity_params_10[[parameter_i]](pars_i, multiplier)
    }
    pars_i$sigma <- sens_grid_10$sigma[i]
    out <- sim_stoch(pars_i, casetarget = 50, agedist = agedist)
    p()
    tibble(parameter = parameter_i, direction = direction_i, sigma = sens_grid_10$sigma[i], rep = sens_grid_10$rep[i],
           n_overall = out$n_overall, n_tested = out$n_tested, n_enrolled = out$n_enrolled,
           n_trial_cases = out$n_trial_cases)
  }, future.seed = TRUE)
})

sens_df_10 <- bind_rows(sens_list_10)
write.csv(sens_df_10, file = "output/sensitivity_analysis_results.csv", row.names = FALSE)

sens_summary_10 <- sens_df_10 %>%
  group_by(parameter, direction, sigma) %>%
  summarise(n_overall = median(n_overall), n_tested = median(n_tested), n_enrolled = median(n_enrolled), .groups = "drop")
write.csv(sens_summary_10, file = "output/sensitivity_analysis_summary.csv", row.names = FALSE)

## Display labels: symbols matching the manuscript's own parameter notation. The "p_slow" row is
## labelled "pf" (not "ps") since it's p_fast that's actually perturbed under the hood (see the
## sensitivity_params_10 comment above) - flag if "ps" is what was actually wanted instead.
param_labels_10 <- c(rho = "ρ", p_slow = "pf", mu_fast = "μf", mu_slow = "μs",
                      p_revert = "pr", mu_revert = "μr")
sigma_symbol_10 <- "σ"

## (a) Raw per-case counts: % change in median n_overall/n_tested/n_enrolled from baseline, at
## matching sigma.
baseline_10 <- sens_summary_10 %>%
  filter(parameter == "baseline") %>%
  select(sigma, n_overall_base = n_overall, n_tested_base = n_tested, n_enrolled_base = n_enrolled)

counts_pct_10 <- sens_summary_10 %>%
  filter(parameter != "baseline") %>%
  left_join(baseline_10, by = "sigma") %>%
  mutate(
    pct_overall  = (n_overall  - n_overall_base)  / n_overall_base  * 100,
    pct_tested   = (n_tested   - n_tested_base)   / n_tested_base   * 100,
    pct_enrolled = (n_enrolled - n_enrolled_base) / n_enrolled_base * 100
  ) %>%
  select(parameter, direction, sigma, pct_overall, pct_tested, pct_enrolled) %>%
  pivot_longer(cols = c(pct_overall, pct_tested, pct_enrolled), names_to = "metric", values_to = "pct_change") %>%
  mutate(metric = case_when(metric == "pct_overall" ~ "Contacted", metric == "pct_tested" ~ "Tested", metric == "pct_enrolled" ~ "Enrolled"),
         metric = factor(metric, levels = c("Contacted", "Tested", "Enrolled")))

param_order_10a <- counts_pct_10 %>% group_by(parameter) %>% summarise(max_effect = max(abs(pct_change)), .groups = "drop") %>%
  arrange(max_effect) %>% pull(parameter)

## (b) Funnel ratios: what fraction of contacts get tested, and what fraction of those tested enrol.
funnel_10 <- sens_summary_10 %>%
  mutate(prop_tested = n_tested / n_overall, prop_enrolled_of_tested = n_enrolled / n_tested) %>%
  select(parameter, direction, sigma, prop_tested, prop_enrolled_of_tested)

funnel_base_10 <- funnel_10 %>%
  filter(parameter == "baseline") %>%
  select(sigma, prop_tested_base = prop_tested, prop_enrolled_of_tested_base = prop_enrolled_of_tested)

funnel_pct_10 <- funnel_10 %>%
  filter(parameter != "baseline") %>%
  left_join(funnel_base_10, by = "sigma") %>%
  mutate(
    pct_prop_tested             = (prop_tested             - prop_tested_base)             / prop_tested_base             * 100,
    pct_prop_enrolled_of_tested = (prop_enrolled_of_tested - prop_enrolled_of_tested_base) / prop_enrolled_of_tested_base * 100
  ) %>%
  select(parameter, direction, sigma, pct_prop_tested, pct_prop_enrolled_of_tested) %>%
  pivot_longer(cols = c(pct_prop_tested, pct_prop_enrolled_of_tested), names_to = "metric", values_to = "pct_change") %>%
  mutate(metric = case_when(metric == "pct_prop_tested" ~ "Tested / Contacted", metric == "pct_prop_enrolled_of_tested" ~ "Enrolled / Tested"),
         metric = factor(metric, levels = c("Tested / Contacted", "Enrolled / Tested")))

param_order_10b <- funnel_pct_10 %>% group_by(parameter) %>% summarise(max_effect = max(abs(pct_change)), .groups = "drop") %>%
  arrange(max_effect) %>% pull(parameter)

## (c) Cross-sigma ratios: tested/enrolled at sigma=0.5y or 2y, relative to sigma=50y (lifelong) -
## i.e. how much the "recent-infection test" reduction in trial size depends on each parameter.
sigma_wide_10 <- sens_summary_10 %>%
  select(parameter, direction, sigma, n_tested, n_enrolled) %>%
  pivot_wider(names_from = sigma, values_from = c(n_tested, n_enrolled))

sigma_ratio_10 <- sigma_wide_10 %>%
  mutate(ratio_tested_0.5to50   = n_tested_0.5   / n_tested_50,
         ratio_tested_2to50     = n_tested_2     / n_tested_50,
         ratio_enrolled_0.5to50 = n_enrolled_0.5 / n_enrolled_50,
         ratio_enrolled_2to50   = n_enrolled_2   / n_enrolled_50) %>%
  select(parameter, direction, starts_with("ratio_"))

base_ratio_tested_0.5to50   <- sigma_ratio_10 %>% filter(parameter == "baseline") %>% pull(ratio_tested_0.5to50)
base_ratio_tested_2to50     <- sigma_ratio_10 %>% filter(parameter == "baseline") %>% pull(ratio_tested_2to50)
base_ratio_enrolled_0.5to50 <- sigma_ratio_10 %>% filter(parameter == "baseline") %>% pull(ratio_enrolled_0.5to50)
base_ratio_enrolled_2to50   <- sigma_ratio_10 %>% filter(parameter == "baseline") %>% pull(ratio_enrolled_2to50)

sigma_ratio_pct_10 <- sigma_ratio_10 %>%
  filter(parameter != "baseline") %>%
  mutate(
    pct_tested_0.5to50   = (ratio_tested_0.5to50   - base_ratio_tested_0.5to50)   / base_ratio_tested_0.5to50   * 100,
    pct_tested_2to50     = (ratio_tested_2to50     - base_ratio_tested_2to50)     / base_ratio_tested_2to50     * 100,
    pct_enrolled_0.5to50 = (ratio_enrolled_0.5to50 - base_ratio_enrolled_0.5to50) / base_ratio_enrolled_0.5to50 * 100,
    pct_enrolled_2to50   = (ratio_enrolled_2to50   - base_ratio_enrolled_2to50)   / base_ratio_enrolled_2to50   * 100
  ) %>%
  select(parameter, direction, starts_with("pct_")) %>%
  pivot_longer(cols = starts_with("pct_"), names_to = "key", values_to = "pct_change") %>%
  mutate(comparison = case_when(grepl("tested", key) ~ "Tested", grepl("enrolled", key) ~ "Enrolled"),
         metric = case_when(grepl("0.5to50", key) ~ paste0(sigma_symbol_10, "=0.5 vs ", sigma_symbol_10, "=50"),
                                 grepl("2to50", key)   ~ paste0(sigma_symbol_10, "=2 vs ",   sigma_symbol_10, "=50"))) %>%
  select(-key)

param_order_10c <- sigma_ratio_pct_10 %>% group_by(parameter) %>% summarise(max_effect = max(abs(pct_change)), .groups = "drop") %>%
  arrange(max_effect) %>% pull(parameter)

## Shared, symmetric x-axis range across all three figures (all measure "% change from baseline",
## so a common scale makes them directly visually comparable) - fixed via coord_cartesian (zooms
## without dropping data) rather than each plot auto-scaling to its own data range.
shared_xlim_10 <- max(abs(c(counts_pct_10$pct_change, funnel_pct_10$pct_change, sigma_ratio_pct_10$pct_change)), na.rm = TRUE) * 1.05

## Colour each END of the bar by which way the PARAMETER itself was perturbed to get that point
## (-20% vs +20%) - the output direction is already visible from x-position, so the colour instead
## disambiguates which end is which perturbation. The connecting segment stays a neutral grey.
perturbation_colours_10 <- c("Parameter decreased (-20%)" = "darkgreen", "Parameter increased (+20%)" = "firebrick")

fig_10a <- counts_pct_10 %>%
  pivot_wider(names_from = direction, values_from = pct_change, names_prefix = "pct_") %>%
  mutate(parameter = factor(parameter, levels = param_order_10a, labels = param_labels_10[param_order_10a]),
         sigma = factor(sigma, levels = sigmas_10, labels = paste0(sigma_symbol_10, "=", sigmas_10))) %>%
  ggplot(aes(y = parameter)) +
  geom_vline(xintercept = 0, linetype = "dashed", col = "grey50") +
  geom_segment(aes(x = pct_low, xend = pct_high, yend = parameter), linewidth = 1, col = "grey70") +
  geom_point(aes(x = pct_low,  col = "Parameter decreased (-20%)"), size = 1.2, alpha = 0.6) +
  geom_point(aes(x = pct_high, col = "Parameter increased (+20%)"), size = 1.2, alpha = 0.6) +
  scale_colour_manual(values = perturbation_colours_10, name = "Perturbation") +
  guides(colour = "none") +
  coord_cartesian(xlim = c(-shared_xlim_10, shared_xlim_10)) +
  facet_grid(sigma ~ metric) +
  theme_classic() +
  theme(strip.background = element_blank()) +
  scale_x_continuous(n.breaks = 10) +
  labs(x = "% change from baseline", y = NULL)
fig_10a
ggsave(fig_10a, file = "figures/10a_sensitivity_counts.png", width = 7.29, height = 4.51)

fig_10b <- funnel_pct_10 %>%
  pivot_wider(names_from = direction, values_from = pct_change, names_prefix = "pct_") %>%
  mutate(parameter = factor(parameter, levels = param_order_10b, labels = param_labels_10[param_order_10b]),
         sigma = factor(sigma, levels = sigmas_10, labels = paste0(sigma_symbol_10, "=", sigmas_10))) %>%
  ggplot(aes(y = parameter)) +
  geom_vline(xintercept = 0, linetype = "dashed", col = "grey50") +
  geom_segment(aes(x = pct_low, xend = pct_high, yend = parameter), linewidth = 1, col = "grey70") +
  geom_point(aes(x = pct_low,  col = "Parameter decreased (-20%)"), size = 1.2, alpha = 0.6) +
  geom_point(aes(x = pct_high, col = "Parameter increased (+20%)"), size = 1.2, alpha = 0.6) +
  scale_colour_manual(values = perturbation_colours_10, name = "Perturbation") +
  guides(colour = "none") +
  coord_cartesian(xlim = c(-shared_xlim_10, shared_xlim_10)) +
  facet_grid(sigma ~ metric) +
  theme_classic() +
  theme(strip.background = element_blank()) +
  scale_x_continuous(n.breaks = 10) +
  labs(x = "% change from baseline", y = NULL)
fig_10b
ggsave(fig_10b, file = "figures/10b_sensitivity_funnel.png", width = 7.29, height = 4.51)

fig_10c <- sigma_ratio_pct_10 %>%
  pivot_wider(names_from = direction, values_from = pct_change, names_prefix = "pct_") %>%
  mutate(parameter = factor(parameter, levels = param_order_10c, labels = param_labels_10[param_order_10c])) %>%
  ggplot(aes(y = parameter)) +
  geom_vline(xintercept = 0, linetype = "dashed", col = "grey50") +
  geom_segment(aes(x = pct_low, xend = pct_high, yend = parameter), linewidth = 1, col = "grey70") +
  geom_point(aes(x = pct_low,  col = "Parameter decreased (-20%)"), size = 1.2, alpha = 0.6) +
  geom_point(aes(x = pct_high, col = "Parameter increased (+20%)"), size = 1.2, alpha = 0.6) +
  scale_colour_manual(values = perturbation_colours_10, name = "Perturbation") +
  guides(colour = "none") +
  coord_cartesian(xlim = c(-shared_xlim_10, shared_xlim_10)) +
  facet_grid(comparison ~ metric) +
  theme_classic() +
  theme(strip.background = element_blank()) +
  scale_x_continuous(n.breaks = 10) +
  labs(x = "% change from baseline", y = NULL)
fig_10c
ggsave(fig_10c, file = "figures/10c_sensitivity_sigma_ratio.png", width = 7.29, height = 4.51)
```
