---
title: "run_analysis"
format: html
---
This Quarto Markdown file outlines a workflow for running all steps of the analysis. It is based on the example workflow in `code/trialsim_rote.R`.

## 1. Setup

```{r}
#| label: setup

library(tidyverse)
library(readxl)
library(future.apply)
library(progressr)
library(countrycode)
library(zoo)
source('code/utils.R')
n_workers <- 8  # shared worker count for all plan(multisession, ...) calls below
plan(multisession, workers=n_workers)  # use multiple cores for speed

# Extract and pre-process data sets
unwpp <- read_excel("data/WPP2024_POP_F01_1_POPULATION_SINGLE_AGE_BOTH_SEXES.xlsx", skip = 16) %>%  # populations from UNWPP
  filter(Year == 2023 & Type == "Country/Area") %>% rename(country="Region, subregion, country or area *") %>%
  mutate(across(all_of(as.character(0:99)), ~ as.numeric(.x) * 1000)) %>% select(country, all_of(as.character(0:99))) %>% arrange(country)
global_TB_inc_report <- read.csv(file = "data/TB_burden_age_sex_2026-02-20.csv") %>%  # number of cases per year, 2024 from WHO
  filter(sex=="a" & risk_factor=="all") %>% select(country, year, age_group, best, lo, hi) %>% rename(cases=best, cases_lo=lo, cases_hi=hi) %>%
  filter(age_group %in% c("0-4","5-9","10-14","15-19","20-24","25-34","35-44","45-54","55-64","65plus")) %>%  # filter duplicate age groups
  mutate(pop = unlist(unname(mapply(get_pop, age_group, country, MoreArgs = list(unwpp = unwpp))))) %>%  # append population
  mutate(inc = cases/pop, inc_lo=cases_lo/pop, inc_hi=cases_hi/pop) %>%  # compute incidence
  select(country, year, age_group, inc, inc_lo, inc_hi) %>% numericize(age_group) %>% arrange(country, age_group)  # expand to single-year ages
progressor_type_by_age_studies <- read.csv(file="data/progressor-type-by-age-estimates-from-literature.csv") %>%
  numericize(age) %>% impute_probability_of_being_slow()

# Estimate reversion rate
Dagnew_reversion_data <- left_join(read.csv("data/Dagnew_2026_IGRA_status_at_day_1_table_s4.csv"), read.csv("data/Dagnew_2026_IGRA_reversion_conversion_table_s6.csv"), by = c("country", "site_no" = "site_number")) %>%  # reversion data from Dagnew et al.
  select(country, site_no, N_D1, n_positive_D1, N_M12, reversion_n) %>%
  group_by(country) %>% summarise(across(c(N_D1, n_positive_D1, N_M12, reversion_n), sum)) %>%  # summing across sites
  mutate(prob_of_reversion_once_infected = reversion_n / (n_positive_D1*N_M12/N_D1))  # probability of reverting once infected = no of reversions / approx no of initial positives who completed the study

# Infection prevalence by age, for fitting/benchmarking (used in chunks 6, 6a)
Dagnew_positivity_data <- read.csv("data/Dagnew_2026_IGRA_positivity_by_age_table_s5.csv") %>%
  select(country, site_no, age_group, pct_positive, ci_lo_positive, ci_hi_positive) %>%
  mutate(across(c(pct_positive, ci_lo_positive, ci_hi_positive), ~ .x / 100)) %>%  # convert % to proportion
  group_by(country, age_group) %>% summarise(min_positivity = min(ci_lo_positive), max_positivity = max(ci_hi_positive)) %>%
  ungroup()
```

## 2. Define age structure

```{r}
#| label: define_age_structure

age_structure <- "South Africa"  # works for "uniform" or any UN-recognised country, e.g. "South Africa"
agedist <- extract_age_distribution(unwpp, age_structure)  # population age distribution
```

## 3. Define parameter values
`pars_lit` takes best-known parameter values from the literature.

```{r}
#| label: define_params

# Edit here as desired
rho_lit <- make_foi(4,6,4,7,5)  # South Africa; best fit to Wood et al. 2010 IGRA prevalence-by-age curve among the 523 passing parameter_fit combinations
p_slow_lit <- extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-high")  # works for "uniform", "Vynnycky-1997", "Vynnycky-high"
mu_slow_lit <- define_mu_slow("0.003")  # works for "min", "base", "0.003", "max"
p_revert_lit <- Dagnew_reversion_data %>% filter(country==age_structure) %>% pull(prob_of_reversion_once_infected)

pars_lit <- list(
	minage=15, # taken from above
	maxage=49, # taken from above
	rho=rho_lit,  # from fitting
	p_slow=p_slow_lit,  # from lit
	mu_slow=mu_slow_lit,  # from lit
	mu_fast=1.5,  # for most fast progressors progressing within two years, assuming exponential dist
	p_revert=p_revert_lit,  # from lit
	mu_revert=0.75, # for most reverters reverting within two years, assuming exponential dist
	sigma=100,  # IGRA test is essentially lifelong
	trial_length=3) # taken from above
```

## 4. South Africa parameter fitting

Note: run code snippets 1-3 first.

```{r}
#| label: SA_parameter_fit
#| eval: FALSE

start.time <- Sys.time()
# define parameter search space
foi_grid_1 <- tibble(a0_4=1:10, a5_24=1:10, a25_34=1:10, a35_49=1:10, a50plus=1:10)  # initial uniform fits
foi_grid_2 <- expand.grid(a0_4=3:7, a5_24=3:7, a25_34=3:7, a35_49=3:7, a50plus=3:7)  # closer inspection of 3-7% as this looked promising from initial fits
foi_grid <- bind_rows(foi_grid_1, foi_grid_2) %>% distinct()
foi_structures <- make_foi(foi_grid)  # named list of 3125 vectors
progression_structures <- c("Vynnycky-1997", "Vynnycky-high")
slow_structures <- c("base", "min", "max", "0.003")
summary_table <- tibble()
reps <- 5

# pars_4: local copy of pars_lit for this fitting loop - pars_lit itself is left untouched
pars_4 <- pars_lit

# run sims
for (progression_structure in progression_structures) {
  # Redefine parameter which is looped
  prog <- extract_probability_of_being_slow(progressor_type_by_age_studies, progression_structure)  # prob of being slow
  pars_4$p_slow <- prog

  for (slow_structure in slow_structures) {
    # Redefine parameter which is looped
    mu_slow <- define_mu_slow(slow_structure)  # rate of progression to disease for slow progressors
    pars_4$mu_slow <- mu_slow

    for (foi_structure in names(foi_structures)) {
    # Redefine parameter which is looped
    foi <- foi_structures[[foi_structure]] # force of infection by age
    pars_4$rho <- foi

    # Simulate stochastic approach (sigma=80)
    with_progress({stochastic_df_lit <- sim_stoch_over_sigma(pars=pars_4, sigmavec=c(80), casetarget=50, agedist=agedist, reps=reps)})

    # Estimate case incidence per 100k, infection prevalence, and ARTI from model (sigma=80)
    from_model <- summarise_case_incidence_and_ARTI(stochastic_df_lit, pars=pars_4, reps=reps, sig=80)
    summary_table <- bind_rows(summary_table, tibble(progression_structure=progression_structure, slow_structure=slow_structure,
                                                     foi_structure=foi_structure, 
                                                     inf_prev_15to24=median(stochastic_df_lit$inf_prev_15to24),  # assuming sigmavec=c(80)
                                                     inf_prev_25to34=median(stochastic_df_lit$inf_prev_25to34),  # assuming sigmavec=c(80)
                                                     ARTI=median(from_model$ARTI), cases=median(from_model$cases)))
    }
  }
}

# Extract South Africa positivity bounds for fitting criteria (Dagnew_positivity_data loaded in setup chunk)
dagnew_age20_min <- Dagnew_positivity_data %>% filter(country=="South Africa" & age_group=="15-24") %>% pull(min_positivity)
dagnew_age20_max <- Dagnew_positivity_data %>% filter(country=="South Africa" & age_group=="15-24") %>% pull(max_positivity)
dagnew_age30_min <- Dagnew_positivity_data %>% filter(country=="South Africa" & age_group=="25-34") %>% pull(min_positivity)
dagnew_age30_max <- Dagnew_positivity_data %>% filter(country=="South Africa" & age_group=="25-34") %>% pull(max_positivity)

# compute summary table and save
summary_table <- summary_table %>% mutate(conditions_met = between(inf_prev_15to24, dagnew_age20_min, dagnew_age20_max) & between(inf_prev_25to34, dagnew_age30_min, dagnew_age30_max) & between(ARTI, 0.04, 0.06) & between(cases, 242, 571))
write.csv(summary_table, file="output/parameter_fit_results.csv", row.names=FALSE) 
end.time <- Sys.time()
```

```{r}
#| label: SA_parameter_fit_plot
#| eval: FALSE
# plot parameter fitting results
slow_labels <- c("min"   = "μ_s = 0.0001",
  "base"  = "μ_s = 0.001",
  "0.003" = "μ_s = 0.003",
  "max"   = "μ_s = 0.00527")

prog_labels <- c("Vynnycky-1997" = "4–14% age-varying",
  "Vynnycky-high" = "4–19% age-varying")

fig_4 <- summary_table %>%
  ggplot(aes(x=inf_prev_15to24, y=ARTI, shape=progression_structure, col=conditions_met)) +
  annotate("rect", xmin=dagnew_age20_min, xmax=dagnew_age20_max,
           ymin=0.04, ymax=0.06, alpha=0.1, fill="steelblue") +
  geom_vline(xintercept=c(dagnew_age20_min, dagnew_age20_max),
             linetype="dashed", col="steelblue", linewidth=0.4) +
  geom_hline(yintercept=c(0.04, 0.06),
             linetype="dashed", col="steelblue", linewidth=0.4) +
  geom_point(data=~filter(.x, !conditions_met), size=2, alpha=0.8) +
  geom_point(data=~filter(.x, conditions_met), size=2, alpha=0.8) +
  scale_colour_manual(values=c("FALSE"="grey80", "TRUE"="forestgreen")) +
  scale_shape_manual(values=c(16, 17), labels=prog_labels) +
  facet_wrap(~slow_structure, labeller=as_labeller(slow_labels)) +
  theme_classic() +
  theme(strip.background=element_blank()) +
  labs(x="Infection prevalence, age 15-24", y="ARTI",
       col="All conditions met", shape="p_f")

fig_4
ggsave(fig_6, file="figures/4_parameter_fit.png", width=7.29, height=4.51)

# summary table
library(flextable)
summary_table %>%
  filter(conditions_met) %>%
  select(foi_structure, progression_structure, slow_structure,
         inf_prev_15to24, inf_prev_25to34, ARTI, cases) %>%
  mutate(across(c(inf_prev_15to24, inf_prev_25to34), ~ round(.x, 2)),
         across(c(ARTI), ~ round(.x, 3)),
         across(c(cases), ~ round(.x, 0))) %>%
  arrange(slow_structure, progression_structure) %>%
  flextable() %>%
  autofit() %>%
  save_as_docx(path="output/parameter_fit_passing.docx")
```

## 5. South Africa literature simulation

```{r}
#| label: simulate_with_lit
#| eval: FALSE

# Simulate the stochastic approach with lit params, over the duration of positivity sigma OR pre-load saved csv file
with_progress({
  stochastic_df_lit <- sim_stoch_over_sigma(pars=pars_lit, sigmavec=c(0.5,1:80), casetarget=50, agedist=agedist, reps=25)
})

# Simulate the analytical approach with lit params, over the duration of positivity sigma
analytical_df_lit <- sim_analytic_over_sigma(pars=pars_lit, sigmavec=seq(from=0.5, to=80, by=0.2), casetarget=50, agedist=agedist)

# Plot all results (per 1)
fig_stochastic_analytic_lit <- plot_stochastic_analytic(stochastic_df_lit, analytical_df_lit, ylimit=1000)
fig_stochastic_analytic_lit
ggsave(fig_stochastic_analytic_lit, file=paste0("figures/stochastic_analytic_lit.png"), width=7.29, height=4.51)

fig_stochastic_analytic_lit_zoom <- plot_stochastic_analytic(stochastic_df_lit %>% filter(sigma <= 15), analytical_df_lit %>% filter(sigma <= 15))
fig_stochastic_analytic_lit_zoom
ggsave(fig_stochastic_analytic_lit_zoom, file=paste0("figures/stochastic_analytic_lit_zoom.png"), width=7.29, height=4.51)

# Optional: estimate case incidence per 100k, infection prevalence, and ARTI from model (sigma=80)
from_model <- summarise_case_incidence_and_ARTI(stochastic_df_lit, pars=pars_lit, reps=25, sig=80)
```

## 6. Scenarios (shared setup)

Note: run code snippets 1-3 first.

Shared setup for the country-scenario chunks below (6a-6c): country list, age distributions, p_revert by country, and the three p_slow structures used by 6a/6b. Run this once before 6a, 6b, or 6c.

```{r}
#| label: 6_scenarios_setup
#| eval: FALSE

countries_scenarios <- c("South Africa", "Kenya", "India")

# Pre-compute age distributions — keeps unwpp out of the future_lapply workers
agedists_scenarios <- setNames(lapply(countries_scenarios, function(c) extract_age_distribution(unwpp, c)), countries_scenarios)

p_revert_by_country <- list(
  "South Africa" = Dagnew_reversion_data %>% filter(country=="South Africa") %>% pull(prob_of_reversion_once_infected),
  "Kenya"        = Dagnew_reversion_data %>% filter(country=="Kenya")        %>% pull(prob_of_reversion_once_infected),
  "India"        = Dagnew_reversion_data %>% filter(country=="Bangladesh")   %>% pull(prob_of_reversion_once_infected))  # Bangladesh used as proxy for India

# Shared p_slow structures for 6a/6b (6c uses a single fixed p_slow per country instead)
p_slow_structures_scenarios <- list(
  "uniform_95"    = extract_probability_of_being_slow(progressor_type_by_age_studies, "uniform"),
  "Vynnycky-1997" = extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-1997"),
  "Vynnycky-high" = extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-high"))

# Shared benchmark thresholds by country, used for conditions_met checks in 6a (uniform sweep) and the
# Kenya/India age-varying parameter fitting
country_thresholds_scenarios <- tibble(
  country       = c("South Africa", "Kenya",   "India"),
  arti_lo       = c(0.04,           0.016,      0.00),
  arti_hi       = c(0.06,           0.036,      0.02),
  cases_lo      = c(242,            109,        160),
  cases_hi      = c(571,            339,        218)
)
```

## 6a. Varied vaccine trial sites (including foi parameter fit)

Full age-varying FOI model fitting for Kenya and India, mirroring the South Africa fitting in chunk 4. FOI search range for each country is informed by an initial uniform sweep (Kenya: 2-5%, India: 1-4%). Parameters held constant: minage, maxage, sigma range, trial_length, mu_fast, mu_slow (0.003). Age distribution, FOI, and p_slow vary by scenario.

```{r}
#| label: 6a_varied_sites_fit
#| eval: FALSE

## First find suitable foi values for Kenya and India
plan(multisession, workers=n_workers)  # reset worker pool in case of stale state from previous run

countries_6a      <- c("Kenya", "India")
p_slow_structures_6a <- c("Vynnycky-1997", "uniform")
slow_structures <- c("base", "max", "0.003")
reps <- 5

# Pre-compute age distributions — keeps unwpp out of the future_lapply workers
agedists_6a <- agedists_scenarios[countries_6a]

# Build base parameter list (shared across all scenarios)
pars_6a <- pars_lit
p_revert_6a <- p_revert_by_country

# FOI grid
foi_grid_1 <- tibble(a0_4=1:10, a5_24=1:10, a25_34=1:10, a35_49=1:10, a50plus=1:10)  # initial uniform fits (shared)
foi_grid_2_by_country <- list(
  "Kenya" = expand.grid(a0_4=2:5, a5_24=2:5, a25_34=2:5, a35_49=2:5, a50plus=2:5),  # closer inspection of 2-5%, informed by uniform sweep above
  "India" = expand.grid(a0_4=1:4, a5_24=1:4, a25_34=1:4, a35_49=1:4, a50plus=1:4))  # closer inspection of 1-4%, informed by uniform sweep above

summary_table_kenya_india <- tibble()

for (country in c("Kenya", "India")) {
  foi_grid <- bind_rows(foi_grid_1, foi_grid_2_by_country[[country]]) %>% distinct()
  foi_structures <- make_foi(foi_grid)  # named list of FOI vectors for this country

  # pars_country: local copy of pars_lit for this fitting loop - pars_lit itself is left untouched
  pars_country <- pars_lit
  pars_country$p_revert <- p_revert_by_country[[country]]
  agedist_country <- agedists_scenarios[[country]]

  for (progression_structure in p_slow_structures_6a) {
    prog <- extract_probability_of_being_slow(progressor_type_by_age_studies, progression_structure)
    pars_country$p_slow <- prog

    for (slow_structure in slow_structures) {
      mu_slow <- define_mu_slow(slow_structure)
      pars_country$mu_slow <- mu_slow

      for (foi_structure in names(foi_structures)) {
        foi <- foi_structures[[foi_structure]]
        pars_country$rho <- foi

        with_progress({stochastic_df_country <- sim_stoch_over_sigma(pars=pars_country, sigmavec=c(80), casetarget=50, agedist=agedist_country, reps=reps)})

        from_model <- summarise_case_incidence_and_ARTI(stochastic_df_country, pars=pars_country, reps=reps, sig=80)
        summary_table_kenya_india <- bind_rows(summary_table_kenya_india, tibble(
          country=country, progression_structure=progression_structure, slow_structure=slow_structure,
          foi_structure=foi_structure,
          inf_prev_15to24=median(stochastic_df_country$inf_prev_15to24),
          inf_prev_25to34=median(stochastic_df_country$inf_prev_25to34),
          ARTI=median(from_model$ARTI), cases=median(from_model$cases)))
      }
    }
  }
}

# Benchmark bounds by country (Dagnew_positivity_data loaded in setup chunk, country_thresholds_scenarios in 6_scenarios_setup)
dagnew_bounds_15to24_ki <- Dagnew_positivity_data %>%
  filter(country %in% c("Kenya","India"), age_group == "15-24") %>%
  select(country, min_positivity, max_positivity) %>%
  rename(min_15to24 = min_positivity, max_15to24 = max_positivity) %>%
  rows_update(tibble(country="India", min_15to24 = 0.098, max_15to24 = 0.158), by="country")  # india data from Selvaraju et al 2023

dagnew_bounds_25to34_ki <- Dagnew_positivity_data %>%
  filter(country %in% c("Kenya","India"), age_group == "25-34") %>%
  select(country, min_positivity, max_positivity) %>%
  rename(min_25to34 = min_positivity, max_25to34 = max_positivity) %>%
  rows_update(tibble(country="India", min_25to34 = 0.171, max_25to34 = 0.252), by="country")  # india data from Selvaraju et al 2023

summary_table_kenya_india <- summary_table_kenya_india %>%
  left_join(dagnew_bounds_15to24_ki, by="country") %>%
  left_join(dagnew_bounds_25to34_ki, by="country") %>%
  left_join(country_thresholds_scenarios, by="country") %>%
  mutate(conditions_met =
    between(inf_prev_15to24, min_15to24, max_15to24) &
    between(inf_prev_25to34, min_25to34, max_25to34) &
    between(ARTI, arti_lo, arti_hi) &
    between(cases, cases_lo, cases_hi))

write.csv(summary_table_kenya_india, file="output/kenya_india_parameter_fit_results.csv", row.names=FALSE)
```


```{r}
#| label: 6a_varied_site_results
#| eval: FALSE

# Flat grid over all combinations: country x FOI x sigma x rep
foi_by_country <- list(
  "South Africa" = make_foi(4,6,4,7,5),                # best fit from chunk 4
  "Kenya"        = define_foi_by_age("uniform_1"),      # replace with best foi from Kenya/India fitting above
  "India"        = define_foi_by_age("uniform_3"))      # replace with best foi from Kenya/India fitting above

# p_slow lookup (named list of actual p_slow vectors, keyed by structure name) - distinct from
# p_slow_structures_6a in the fitting chunk above, which is just the plain vector of structure names
p_slow_lookup_6a <- list(
  "Vynnycky-high" = extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-high"),
  "Vynnycky-1997" = extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-1997"),
  "uniform"       = extract_probability_of_being_slow(progressor_type_by_age_studies, "uniform"))

# South Africa's p_slow/mu_slow are already fixed (matching pars_lit's chosen fit); Kenya/India still
# compare all p_slow/mu_slow options since their fitting hasn't settled on a single best combination yet
sim_grid_6a <- bind_rows(
  tibble(country="South Africa") %>% crossing(p_slow="Vynnycky-high", mu_slow="0.003"),
  tibble(country=c("Kenya","India")) %>% crossing(p_slow=c("Vynnycky-1997","uniform"), mu_slow=slow_structures)
) %>%
  crossing(sigma = c(0.5, 1:10, seq(15, 80, by=5)), rep = 1:25)

# South Africa/Kenya/India all needed here (agedists_6a/countries_6a above only cover Kenya/India)
countries_6a_results <- c("South Africa", "Kenya", "India")
agedists_6a_results  <- agedists_scenarios

# Single flat future_lapply — avoids nested parallelism and memory spikes
with_progress({
  p <- progressr::progressor(steps=nrow(sim_grid_6a))
  stoch_list_6a <- future.apply::future_lapply(1:nrow(sim_grid_6a), function(i) {
    pars_i        <- pars_6a
    pars_i$rho    <- foi_by_country[[sim_grid_6a$country[i]]]
    pars_i$p_slow <- p_slow_lookup_6a[[sim_grid_6a$p_slow[i]]]
    pars_i$mu_slow <- define_mu_slow(sim_grid_6a$mu_slow[i])
    pars_i$p_revert <- p_revert_6a[[sim_grid_6a$country[i]]]
    pars_i$sigma  <- sim_grid_6a$sigma[i]
    agedist_i     <- agedists_6a_results[[sim_grid_6a$country[i]]]
    out           <- sim_stoch(pars_i, casetarget=50, agedist=agedist_i)
    p()
    tibble(country=sim_grid_6a$country[i], p_slow=sim_grid_6a$p_slow[i],
       mu_slow=sim_grid_6a$mu_slow[i], sigma=sim_grid_6a$sigma[i], rep=sim_grid_6a$rep[i],
       n_tested=out$n_tested, n_enrolled=out$n_enrolled, n_overall=out$n_overall,
       n_trial_cases=out$n_trial_cases, inf_prev_15to24=out$inf_prev_15to24, inf_prev_25to34=out$inf_prev_25to34)
  }, future.seed=TRUE)
})

stoch_df_6a <- bind_rows(stoch_list_6a)

#' 3x2 panel plot: rows = n_enrolled_1 / n_tested_1, columns = country, colour = p_slow, linetype = mu_slow
stoch_df_6a_long <- stoch_df_6a %>%
  mutate(country = factor(country, levels=countries_6a_results),
         n_enrolled_1 = n_enrolled / n_trial_cases,
         n_tested_1   = n_tested   / n_trial_cases) %>%
  select(country, p_slow, mu_slow, sigma, rep, n_enrolled_1, n_tested_1) %>%
  pivot_longer(cols=c(n_enrolled_1, n_tested_1), names_to="metric", values_to="value") %>%
  mutate(metric = case_when(metric=="n_enrolled_1"~"Enrolled", metric=="n_tested_1"~"Tested"),
         metric = factor(metric, levels=c("Enrolled","Tested")))
write.csv(stoch_df_6a_long, file="output/variedsite_results_stochoutput.csv", row.names=FALSE)

median_df_6a <- stoch_df_6a_long %>%
  group_by(country, p_slow, mu_slow, sigma, metric) %>%
  summarise(value = median(value), .groups="drop")
write.csv(median_df_6a, file="output/variedsite_results_medians.csv", row.names=FALSE)

p_slow_labels_6a  <- c("uniform"="5%","Vynnycky-1997"="4-14%","Vynnycky-high"="4-19%")
mu_slow_labels_6a <- c("base"="μ_s = 0.001","max"="μ_s = 0.00527","0.003"="μ_s = 0.003")

fig_6a <- ggplot(stoch_df_6a_long, aes(x=sigma, y=value, col=p_slow, linetype=mu_slow)) +
  geom_point(size=0.4, alpha=0.1) +
  geom_line(data=median_df_6a, linewidth=0.7) +
  facet_grid(metric ~ country, scales="free_y") +
  scale_colour_brewer(palette="Set1", labels=p_slow_labels_6a) +
  scale_linetype_manual(values=c("base"="solid","max"="dashed","0.003"="dotted"),
                      labels=mu_slow_labels_6a) +
  theme_classic() +
  theme(strip.background=element_blank()) +
  labs(x="Test span (years)", y="Number (for 1 case)", col="p_f", linetype="μ_s")
fig_6a
ggsave(fig_6a, file="figures/6a_varied_sites.png", width=7.29, height=4.51)

fig_6a_zoom <- ggplot(stoch_df_6a_long %>% filter(sigma <= 15),
                      aes(x=sigma, y=value, col=p_slow, linetype=mu_slow)) +
  geom_point(size=0.4, alpha=0.1) +
  geom_line(data=median_df_6a %>% filter(sigma <= 15), linewidth=0.7) +
  facet_grid(metric ~ country, scales="free_y") +
  scale_colour_brewer(palette="Set1", labels=p_slow_labels_6a) +
  scale_linetype_manual(values=c("base"="solid","max"="dashed","0.003"="dotted"),
                        labels=mu_slow_labels_6a) +
  theme_classic() +
  theme(strip.background=element_blank()) +
  labs(x="Test span (years)", y="Number (for 1 case)", col="p_f", linetype="μ_s")
fig_6a_zoom
ggsave(fig_6a_zoom, file="figures/6a_varied_sites_zoom.png", width=7.29, height=4.51)

#' Summary table: infection prevalence at ages 20/30, ARTI, case incidence
#' Computed from stochastic output at sigma=80 (infection prevs, ARTI, cases)
summary_table_6a <- stoch_df_6a %>%
  filter(sigma == 80) %>%
  mutate(inf_prev_all = (n_overall - n_tested + n_enrolled) / n_overall,
    meanage      = ((pars_6a$maxage - pars_6a$minage) / 2) + pars_6a$minage,
    ARTI         = 1 - (1 - inf_prev_all)^(1 / meanage),
    cases_per100k = n_trial_cases / (n_overall * pars_6a$trial_length) * 100000) %>%
  group_by(country, p_slow, mu_slow) %>%
  summarise(inf_prev_15to24 = median(inf_prev_15to24),
    inf_prev_25to34 = median(inf_prev_25to34),
    ARTI            = median(ARTI),
    cases_per100k   = median(cases_per100k),
    .groups = "drop")

write.csv(summary_table_6a, file="output/variedsite_results.csv", row.names=FALSE)
```

## 6b. No-test enrolment scenarios

Three scenarios using `sim_stoch_notest`: standard ages (15-49), younger ages (12-34), and household contacts (6-99, high instantaneous FOI if not already infected). No sigma dimension — one output per (scenario, country, FOI, rep).

```{r}
#| label: 6b_notest_scenarios
#| eval: FALSE

plan(multisession, workers=n_workers)

countries_6b      <- countries_scenarios
p_slow_structures_6b <- p_slow_structures_scenarios
p_revert_6b       <- p_revert_by_country
mu_slow_6b        <- define_mu_slow("0.003")
agedists_6b       <- agedists_scenarios

# Build base parameter list
pars_6b <- pars_lit
pars_6b$mu_slow <- mu_slow_6b

# Flat grid: scenario x country x FOI x rep
scenarios_6b <- tibble(scenario = c("no test standard", "no test young", "no test household"),
                       minage   = c(15, 12, 6),
                       maxage   = c(49, 34, 99))

sim_grid_6b <- crossing(
  bind_rows(tibble(country="South Africa", foi_structure="uniform_6", slow_structure="Vynnycky-high"),
    tibble(country="Kenya", foi_structure="uniform_3", slow_structure=c("uniform_95","Vynnycky-1997")),
    tibble(country="India", foi_structure="uniform_2", slow_structure=c("uniform_95","Vynnycky-1997"))),
  scenarios_6b,
  rep = 1:25)

with_progress({
  p <- progressr::progressor(steps=nrow(sim_grid_6b))
  notest_list_6b <- future.apply::future_lapply(1:nrow(sim_grid_6b), function(i) {
    pars_i        <- pars_6b
    pars_i$rho    <- define_foi_by_age(sim_grid_6b$foi_structure[i])
    pars_i$minage <- sim_grid_6b$minage[i]
    pars_i$maxage <- sim_grid_6b$maxage[i]
    pars_i$p_slow   <- p_slow_structures_6b[[sim_grid_6b$slow_structure[i]]]
    pars_i$p_revert <- p_revert_6b[[sim_grid_6b$country[i]]]
    agedist_i     <- agedists_6b[[sim_grid_6b$country[i]]]
    out           <- sim_stoch_notest(pars_i, casetarget=50, agedist=agedist_i, 
                                      households = (sim_grid_6b$scenario[i] == "no test household"))
    p()
    tibble(
      scenario      = sim_grid_6b$scenario[i],
      country       = sim_grid_6b$country[i],
      foi_structure = sim_grid_6b$foi_structure[i],
      slow_structure  = sim_grid_6b$slow_structure[i],
      rep           = sim_grid_6b$rep[i],
      n_enrolled   = out$n_enrolled,
      n_fast        = out$n_fast,
      n_trial_cases = out$n_trial_cases,
      n_overall     = out$n_overall,
      n_infected    = out$n_infected,
      inf_prev_15to24 = out$inf_prev_15to24,
      inf_prev_25to34 = out$inf_prev_25to34,
      minage = sim_grid_6b$minage[i],
      maxage = sim_grid_6b$maxage[i])
  }, future.seed=TRUE)
})

notest_df_6b <- bind_rows(notest_list_6b)

#' Summarise over reps: median + 10th/90th percentile
notest_summary_6b <- notest_df_6b %>%
  group_by(scenario, country, foi_structure, slow_structure) %>%
  summarise(
    n_enrolled_med = median(n_enrolled),
    n_enrolled_lo  = quantile(n_enrolled, 0.1),
    n_enrolled_hi  = quantile(n_enrolled, 0.9),
    n_overall_med   = median(n_overall),
    n_overall_lo    = quantile(n_overall, 0.1),
    n_overall_hi    = quantile(n_overall, 0.9),
    .groups = "drop"
  )
write.csv(notest_summary_6b, file="output/notest_results.csv", row.names=FALSE)

#' Plot: x = scenario, facet = country, line = p_f
fig_6b <- notest_df_6b %>%
  mutate(country       = factor(country, levels=countries_6b),
         scenario      = factor(scenario, levels=c("no test standard","no test young","no test household")),
         slow_structure = factor(slow_structure, levels=names(p_slow_structures_6b)),
         n_enrolled_1  = n_enrolled / n_trial_cases) %>%
  ggplot(aes(x=scenario, y=n_enrolled_1, fill=slow_structure)) +
  geom_boxplot(coef=Inf) +
  scale_fill_brewer(palette="Set1",
                    labels=c("uniform_95"="5%","Vynnycky-1997"="4-14%","Vynnycky-high"="4-19%")) +
  facet_wrap(~country, nrow=1) +
  theme_classic() +
  theme(strip.background=element_blank(), axis.text.x=element_text(angle=25, hjust=1)) +
  labs(x=NULL, y="Number enrolled (for 1 case)", fill="p_f")
fig_6b
ggsave(fig_6b, file="figures/6b_notest_scenarios.png", width=7.29, height=4.51)
```

## 6c. Main figure: test-based vs no-test strategies combined

Combines two test-based strategies (sigma = 2 years, ~lifetime) with the three `sim_stoch_notest` scenarios from 6b, one fixed FOI and one fixed p_slow structure per country (Vynnycky-high for South Africa, Vynnycky-1997 for Kenya and India), fill = enrolment strategy.

```{r}
#| label: 6c_main_combined
#| eval: FALSE

plan(multisession, workers=n_workers)

countries_6c <- countries_scenarios
p_slow_by_country_6c <- list(
  "South Africa" = extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-high"),
  "Kenya"        = extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-1997"),
  "India"        = extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-1997"))
p_revert_6c <- p_revert_by_country
foi_by_country_6c <- c("South Africa"="uniform_6", "Kenya"="uniform_3", "India"="uniform_2")
agedists_6c <- agedists_scenarios

# Build base parameter list
pars_6c <- pars_lit
pars_6c$mu_slow <- define_mu_slow("0.003")

# Strategy definitions: 3 test-based (varying sigma) + 3 no-test (varying age range/households)
strategies_6c <- tibble(
  strategy   = c("No test\nstandard", "No test\nyoung", "No test\nhousehold", "Test\nlifetime", "Test\n2 years"),
  type       = c("notest", "notest", "notest", "test", "test"),
  sigma      = c(NA, NA, NA, 80, 2),
  minage     = c(15, 12, 6, NA, NA),
  maxage     = c(49, 34, 99, NA, NA),
  households = c(FALSE, FALSE, TRUE, NA, NA))

# Flat grid: country x strategy x rep
sim_grid_6c <- crossing(country=countries_6c, strategy=strategies_6c$strategy, rep=1:25) %>%
  left_join(strategies_6c, by="strategy") %>%
  mutate(foi_structure = foi_by_country_6c[country])

with_progress({
  p <- progressr::progressor(steps=nrow(sim_grid_6c))
  stoch_list_6c <- future.apply::future_lapply(1:nrow(sim_grid_6c), function(i) {
    pars_i        <- pars_6c
    pars_i$rho    <- define_foi_by_age(sim_grid_6c$foi_structure[i])
    pars_i$p_slow <- p_slow_by_country_6c[[sim_grid_6c$country[i]]]
    pars_i$p_revert <- p_revert_6c[[sim_grid_6c$country[i]]]
    agedist_i     <- agedists_6c[[sim_grid_6c$country[i]]]

    if (sim_grid_6c$type[i] == "test") {
      pars_i$sigma <- sim_grid_6c$sigma[i]
      out <- sim_stoch(pars_i, casetarget=50, agedist=agedist_i)
    } else {
      pars_i$minage <- sim_grid_6c$minage[i]
      pars_i$maxage <- sim_grid_6c$maxage[i]
      out <- sim_stoch_notest(pars_i, casetarget=50, agedist=agedist_i,
                              households=sim_grid_6c$households[i])
    }
    p()
    tibble(country=sim_grid_6c$country[i], strategy=sim_grid_6c$strategy[i], type=sim_grid_6c$type[i],
      rep=sim_grid_6c$rep[i], n_enrolled=out$n_enrolled, n_trial_cases=out$n_trial_cases)
  }, future.seed=TRUE)
})

stoch_df_6c <- bind_rows(stoch_list_6c)

# Plot: x = strategy (grouped, test-based then no-test), 3 dodged boxes per group = country, fill = country
country_colours_6c <- c("South Africa"="#4DAF4A", "Kenya"="#377EB8", "India"="#E41A1C")
fig_6c <- stoch_df_6c %>%
  mutate(country  = factor(country, levels=countries_6c),
         strategy = factor(strategy, levels=strategies_6c$strategy),
         n_enrolled_1 = n_enrolled / n_trial_cases) %>%
  ggplot(aes(x=strategy, y=n_enrolled_1, fill=country)) +
  geom_boxplot(coef=Inf, position=position_dodge2(preserve="single")) +
  scale_fill_manual(values=country_colours_6c) +
  theme_classic() +
  theme(strip.background=element_blank(), axis.text.x=element_text(angle=25, hjust=1)) +
  labs(x=NULL, y="Number needed to enrol (for 1 case)", fill="Country")
fig_6c
ggsave(fig_6c, file="figures/6c_main_combined.png", width=8.5, height=4.51)
```

## 7. M72IIb emulation fitting

Rather than stopping at casetarget=50 and scaling up, `sim_stoch_trial` recruits until enrol_target is reached.
```{r}
#| label: simulate_with_m72IIb_fit
#| eval: FALSE

target_enrolled <- 3289
target_cases    <- 52

pars_m72IIb <- list(
	minage=18,  # from trial
	maxage=49,  # from trial (up to 50.0y)
	rho=make_foi(4,6,4,7,5),  # modelled value (South Africa; best fit to Wood et al. 2010, see chunk 2)
	p_slow=NA,  # modelled value
	mu_slow=NA,  # assumed, informed by lit
	mu_fast=1.5,  # from lit
	p_revert=p_revert_lit,  # from lit
	mu_revert=0.75, # from lit
	sigma=100,  # IGRA test is essentially lifelong
	trial_length=3)  # from trial
p_slow_m72IIb_vals     <- seq(0.5, 1.0, by=0.05)
slow_structures_m72IIb <- c("base", "min", "max", "0.003")
reps <- 25

# Build a flat grid of all parameter combinations x reps
uniform_grid <- expand.grid(
  slow_structure = slow_structures_m72IIb,
  p_slow_label   = paste0("uniform_", seq(0.5, 0.95, by=0.05)),
  rep            = 1:reps,
  stringsAsFactors = FALSE)
vynnycky_grid <- expand.grid(
  slow_structure = slow_structures_m72IIb,
  p_slow_label   = c("Vynnycky-1997", "Vynnycky-high"),
  rep            = 1:reps,
  stringsAsFactors = FALSE)
param_grid <- bind_rows(uniform_grid, vynnycky_grid)

with_progress({
  p <- progressr::progressor(steps=nrow(param_grid))
  trial_results_list <- future.apply::future_lapply(1:nrow(param_grid), function(i) {
    pars_fit         <- pars_m72IIb
    pars_fit$mu_slow <- define_mu_slow(param_grid$slow_structure[i])
    pars_fit$p_slow <- if (param_grid$p_slow_label[i] == "Vynnycky-1997") {
      extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-1997") 
      } else if (param_grid$p_slow_label[i] == "Vynnycky-high") {
        extract_probability_of_being_slow(progressor_type_by_age_studies, "Vynnycky-high")
      } else {
        val <- as.numeric(sub("uniform_", "", param_grid$p_slow_label[i]))
        setNames(rep(val, 100), 0:99)
      }
    out <- sim_stoch_trial(pars_fit, enrol_target=target_enrolled, agedist=agedist)
    p()
    tibble(p_slow_structure= param_grid$p_slow_label[i],
      mu_slow        = pars_fit$mu_slow,
      foi_structure  = param_grid$foi_structure[i],
      rep            = param_grid$rep[i],
      n_overall      = out$n_overall,
      n_tested       = out$n_tested,
      n_enrolled     = out$n_enrolled,
      n_trial_cases  = out$n_trial_cases)
  }, future.seed=TRUE)
})

trial_results <- bind_rows(trial_results_list)

#' Summarise over reps
m72IIb_fit_trial <- trial_results %>%
  group_by(p_slow_structure, mu_slow) %>%
  summarise(
    n_overall_med = round(median(n_overall)),
    n_enrolled_med = round(median(n_enrolled)),
    n_trial_cases_med = round(median(n_trial_cases), 1),
    n_trial_cases_lo  = round(quantile(n_trial_cases, 0.1), 1),
    n_trial_cases_hi  = round(quantile(n_trial_cases, 0.9), 1),
    .groups       = "drop"
  ) %>%
  mutate(case_target_met = between(n_trial_cases_med, target_cases * 0.8, target_cases * 1.2))

write.csv(m72IIb_fit_trial, file="output/m72IIb_fit_results.csv", row.names=FALSE)
```

## 8. Stochastic & analytic match
```{r}
#| label: match_approaches
#| eval: FALSE

# Set non-age-varying params TODO
pars_lit_uniform <- list(
	minage=15, # taken from above
	maxage=49, # taken from above
	rho=make_foi(6,6,6,6,6),
	p_slow=extract_probability_of_being_slow(progressor_type_by_age_studies, "uniform"),
	mu_slow=mu_slow_lit,  # from lit
	mu_fast=1.5,  # for most fast progressors progressing within two years, assuming exponential distribution
	p_revert=0,  # no reversion for analytic match
	mu_revert=0, # no reversion for analytic match
	sigma=100,  # IGRA test is essentially lifelong
	trial_length=3)

# Simulate the stochastic approach with lit params, over the duration of positivity sigma OR pre-load saved csv file
with_progress({
  stochastic_df_match <- sim_stoch_over_sigma(pars=pars_lit_uniform, sigmavec=c(0.5,1:80), casetarget=50, agedist=agedist, reps=25)
})

#' Simulate the analytical approach with lit params, over the duration of positivity sigma
analytical_df_match <- sim_analytic_over_sigma(pars=pars_lit_uniform, sigmavec=seq(from=0.5, to=80, by=0.1), casetarget=50, agedist=agedist)

#' Plot all results
fig_stochastic_analytic_match <- plot_stochastic_analytic(stochastic_df_match, analytical_df_match)
fig_stochastic_analytic_match
ggsave(fig_stochastic_analytic_match, file=paste0("figures/stochastic_analytic_match.png"), width=7.29, height=4.51)
```